---
title: "VR_K_correlation"
author: "Liam"
date: '2022-08-31'
output: html_document
---

# Pre-plotting

Load required packages

```{r pkg}
library(ggplot2)
library(hyenaR)
library(dplyr)
library(here)
```

Define which simulation type we're using

```{r}

#Model 2 (polynomial age and random effect of year nested within clan)
#Simulations have a variety of start points to reduce initialization bias
folder_name <- "model2_multistart_v036"
db.path     <- "../hyena_data/Fisidata_2022_08_08.sqlite"
start_year  <- 1997
```

# PLOT 1: Absolute change in K and N over time

Prep data

```{r}

## EXTRACT ESTIMATED K
years <- start_year:2020

pb_yr <- progress::progress_bar$new(total = length(years))

Kplot_data <- purrr::map_df(.x = years,
                            .f = function(year, folder_name){
                              
                              pb_yr$tick()
                              
                              txt_files <- list.files(here(paste0("./MS_preliminary_results/", folder_name, "/", year)),
                                                      pattern = ".txt", full.names = TRUE)
                              
                              allsims <- purrr::map_df(.x = txt_files,
                                                       .f = function(filepath){
                                                         
                                                         readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) %>%
                                                           dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=pop)[0-9]+"))
                                                         
                                                       })
                              
                              estK <- allsims %>% 
                                dplyr::group_by(.data$sim) %>% 
                                dplyr::mutate(start_pop = first(pop_size)) %>% 
                                dplyr::slice(ceiling(dplyr::n()/2):dplyr::n()) %>% 
                                dplyr::summarise(K = median(.data$pop_size),
                                                 start_size = first(start_pop))
                              
                              plot_data <- estK %>% 
                                dplyr::summarise(year = year,
                                                 globalK = median(.data$K),
                                                 lower = min(.data$K),
                                                 upper = max(.data$K),
                                                 points = list(data.frame(pop_size = .data$K,
                                                                          start_pop = .data$start_size)))
                              
                              return(plot_data)
                              
                            }, folder_name = folder_name)

```

Extract observed VRs from model frame data (should be more easily accessible...)

```{r}
## GENERATED IN STEP0_prepare_data/model_fit.Rmd
model_data <- readRDS(here::here("./MS_preliminary_results/results/data/model_data.RDS"))
```

```{r}

Fad_surv_yr <- model_data$F_surv_data %>% 
  filter(age >= 24) %>% 
  group_by(year) %>% 
  summarise(sum_surv = sum(surv),
            n = n()) %>% 
  mutate(binom::binom.wilson(x = sum_surv, n = n),
         VR = "Female adult surv")

Fcub_surv_yr <- model_data$F_surv_data %>% 
  filter(age < 24) %>% 
  group_by(year) %>% 
  summarise(sum_surv = sum(surv),
            n = n()) %>% 
  mutate(binom::binom.wilson(x = sum_surv, n = n),
         VR = "Female cub surv")

M_predisp_surv_yr <- model_data$PreM_surv_data %>% 
  group_by(year) %>% 
  summarise(sum_surv = sum(surv),
            n = n()) %>% 
  mutate(binom::binom.wilson(x = sum_surv, n = n),
         VR = "Male predisp surv")

M_postdisp_surv_yr <- model_data$PostM_surv_data %>% 
  group_by(year) %>% 
  summarise(sum_surv = sum(surv),
            n = n()) %>% 
  mutate(binom::binom.wilson(x = sum_surv, n = n),
         VR = "Male postdisp surv")

twinning_yr <- model_data$F_twin_data %>% 
  group_by(year) %>% 
  summarise(sum_twin = sum(twin),
            n = n()) %>% 
  mutate(binom::binom.wilson(x = sum_twin, n = n),
         VR = "Twinning")

primi_repro_yr <- model_data$F_repro_primi %>% 
  group_by(year) %>% 
  summarise(sum_repro = sum(repro),
            n = n()) %>% 
  mutate(binom::binom.wilson(x = sum_repro, n = n),
         VR = "Primiparous repro")

nonprimi_repro_yr <- model_data$F_repro_nonprimi %>% 
  group_by(year) %>% 
  summarise(sum_repro = sum(repro),
            n = n()) %>% 
  mutate(binom::binom.wilson(x = sum_repro, n = n),
         VR = "Non-primiparous repro")

df_life <- list(Fad_surv_yr, Fcub_surv_yr, M_predisp_surv_yr, M_postdisp_surv_yr, twinning_yr, primi_repro_yr, nonprimi_repro_yr)

```

Estimate time varying cor for each

```{r}

library(timevarcorr)

purrr::imap(df_life, .f = ~{
  
  cor_data <- left_join(..1, select(Kplot_data, year, globalK), by = "year")
  
  with(cor_data, tcor(x = globalK, y = mean, t = year, kernel = "box", CI = TRUE)) %>% 
    mutate(VR = cor_data$VR[1])
  
}) %>% 
  dplyr::bind_rows() -> timevarcorr_all

#Group female and male together
plot_data <- timevarcorr_all %>% 
  mutate(facet = case_when(stringr::str_detect(VR, "repro$") ~ "Reproduction",
                           VR == "Twinning" ~ "Litter size",
                           stringr::str_detect(VR, "^Female") ~ "Female",
                           stringr::str_detect(VR, "^Male") ~ "Male"),
         name = case_when(stringr::str_detect(VR, "repro$") ~ stringr::str_remove(VR, " repro"),
                          stringr::str_detect(VR, "^Female") ~ stringr::str_extract(VR, "(?<=Female )[a-z]*"),
                          stringr::str_detect(VR, "^Male") ~ stringr::str_extract(VR, "(?<=Male )[a-z]*"),
                          TRUE ~ VR)) %>% 
  mutate(facet = forcats::fct_relevel(facet, "Female", "Male", "Reproduction","Litter size"))

ggplot() +
  geom_hline(yintercept = 0, size = 0.5, colour = "black") +
  geom_ribbon(data = plot_data, aes(x = t, ymin = lwr, ymax = upr, group = name, fill = name),
              alpha = 0.5) +
  geom_line(data = plot_data, aes(x = t, y = r, group = name, colour = name)) +
  geom_segment(data = data.frame(x = seq(1995, 2020, 5), xend = seq(1995, 2020, 5),
                                 y = 0, yend = -0.05, facet = "Reproduction"),
               aes(x = x, xend = xend, y = y, yend = yend), size = 0.5, lineend = "round") +
  scale_fill_manual(values   = c("grey10", "grey70", "grey10", "grey70", "grey10", "grey70", "grey10")) +
  scale_colour_manual(values = c("grey10", "grey70", "grey10", "grey70", "grey10", "grey70", "grey10")) +
  scale_x_continuous(breaks = seq(1995, 2020, 5)) +
  coord_cartesian(ylim = c(0, NA),
                  xlim = c(1995, 2021),
                  expand = FALSE, clip = "off") +
  facet_wrap(facets = ~facet) +
  labs(y = "Correlation") +
  theme_classic() +
  theme(legend.position = "none",
        axis.ticks.y = element_line(colour = "black"),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.text = element_text(colour = "black"),
        axis.text.x = element_text(margin = margin(t = 5)),
        axis.line.x = element_blank())

```

Separate female survival into top and low ranking individuals...

```{r}
Fad_surv_yr_low <- model_data$F_surv_data %>% 
  filter(age >= 24 & rank_category == "lower.ranking") %>% 
  group_by(year) %>% 
  summarise(sum_surv = sum(surv),
            n = n()) %>% 
  mutate(binom::binom.wilson(x = sum_surv, n = n),
         VR = "Female low rank adult surv")

Fad_surv_yr_high <- model_data$F_surv_data %>% 
  filter(age >= 24 & rank_category == "top5") %>% 
  group_by(year) %>% 
  summarise(sum_surv = sum(surv),
            n = n()) %>% 
  mutate(binom::binom.wilson(x = sum_surv, n = n),
         VR = "Female high rank adult surv")

df_life_rank <- list(Fad_surv_yr_low, Fad_surv_yr_high)

```s

Estimate time varying cor for each

```{r}

library(timevarcorr)

purrr::imap(df_life_rank, .f = ~{
  
  cor_data <- left_join(..1, select(Kplot_data, year, globalK), by = "year")
  
  with(cor_data, tcor(x = globalK, y = mean, t = year, kernel = "box", CI = TRUE)) %>% 
    mutate(VR = cor_data$VR[1])
  
}) %>% 
  dplyr::bind_rows() -> timevarcorr_all

#Group female and male together
plot_data <- timevarcorr_all %>% 
  mutate(facet = VR,
         name = VR)

ggplot() +
  geom_hline(yintercept = 0, size = 0.5, colour = "black") +
  geom_ribbon(data = plot_data, aes(x = t, ymin = lwr, ymax = upr, group = name, fill = name),
              alpha = 0.5) +
  geom_line(data = plot_data, aes(x = t, y = r, group = name, colour = name)) +
  # geom_segment(data = data.frame(x = seq(1995, 2020, 5), xend = seq(1995, 2020, 5),
  #                  y = 0, yend = -0.05, facet = "Reproduction"),
  #              aes(x = x, xend = xend, y = y, yend = yend), size = 0.5, lineend = "round") +
  scale_fill_manual(values   = c("grey10", "grey70", "grey10", "grey70", "grey10", "grey70", "grey10")) +
  scale_colour_manual(values = c("grey10", "grey70", "grey10", "grey70", "grey10", "grey70", "grey10")) +
  scale_x_continuous(breaks = seq(1995, 2020, 5)) +
  coord_cartesian(ylim = c(0, NA),
                  xlim = c(1995, 2021),
                  expand = FALSE, clip = "off") +
  facet_wrap(facets = ~facet) +
  labs(y = "Correlation") +
  theme_classic() +
  theme(legend.position = "none",
        axis.ticks.y = element_line(colour = "black"),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.text = element_text(colour = "black"),
        axis.text.x = element_text(margin = margin(t = 5)),
        axis.line.x = element_blank())

```

Estimate carrying capacity for each sex separately...

```{r}
library(lay)
## EXTRACT ESTIMATED K
years <- start_year:2020

pb_yr <- progress::progress_bar$new(total = length(years))

K_data_sex <- purrr::map_df(.x = years,
                            .f = function(year, folder_name){
                              
                              pb_yr$tick()
                              
                              txt_files <- list.files(here(paste0("./MS_preliminary_results/", folder_name, "/", year)),
                                                      pattern = ".txt", full.names = TRUE)
                              
                              allsims <- purrr::map_df(.x = txt_files,
                                                       .f = function(filepath){
                                                         
                                                         readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) %>%
                                                           dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=pop)[0-9]+"))
                                                         
                                                       })
                              
                              estK <- allsims %>% 
                                #Remove dead cols
                                dplyr::select(!contains("dead")) %>% 
                                #Use lay to determine rowwise sums
                                dplyr::mutate(fem_sum = lay(across(contains("fem")), .fn = ~sum(., na.rm = TRUE)),
                                              male_sum = lay(across(contains("male")), .fn = ~sum(., na.rm = TRUE)),
                                              bothsex_sum = fem_sum + male_sum) %>% 
                                dplyr::group_by(.data$sim) %>% 
                                dplyr::mutate(start_pop = first(pop_size)) %>% 
                                dplyr::slice(ceiling(dplyr::n()/2):dplyr::n()) %>% 
                                dplyr::summarise(Kfem = median(.data$fem_sum),
                                                 Kmal = median(.data$male_sum),
                                                 Ktotal = median(.data$pop_size),
                                                 start_size = first(start_pop),
                                                 year = year)
                              
                              return(estK)
                              
                            }, folder_name = folder_name)

```

```{r}
plot_data_sex <- K_data_sex %>% 
  group_by(year) %>% 
  summarise(medianKmale = median(Kmal),
            medianKfem  = median(Kfem)) %>% 
  mutate(startdate = lubridate::ymd(paste(year, "01", "01", sep = "-")),
         enddate = lubridate::ymd(paste(year + 1, "01", "01", sep = "-"))) %>% 
  tidyr::pivot_longer(startdate:enddate,
                      names_to = "dategrp", values_to = "date") %>% 
  tidyr::pivot_longer(cols = medianKmale:medianKfem,
                      names_to = "sex",
                      values_to = "medianK")

ggplot() +
  geom_line(data = plot_data_sex,
            aes(x = date, y = medianK, colour = sex)) +
  scale_y_continuous(limits = c(0, NA)) +
  theme_classic()
```

Relative

```{r}
plot_data_sex_rel <- plot_data_sex %>% 
  group_by(sex) %>% 
  mutate(medianK_zscore = (medianK - mean(medianK))/sd(medianK))

ggplot() +
  geom_line(data = plot_data_sex_rel,
            aes(x = date, y = medianK_zscore, colour = sex)) +
  # scale_y_continuous(limits = c(0, NA)) +
  theme_classic()
```
