---
title: "Model selection"
output:
  html_document: default
  pdf_document: default
date: "2025-04-19"
---

Fit vital rate models used inside the simulation.

## Setup workspace

### Load packages

```{r}
library(dplyr)
library(ggplot2)
library(hyenaR)
```

### Define parallel processing variables

```{r}
cores_used <- 8
```

### Define years where we will calculate K

We exclude 1996 because we only have half a year of data. We exclude 2023 to have data where we can test predictive accuracy. 2024 is not used because we don't have enough observations (i.e. >1y) to accurately determine vital rates.

```{r}
## Set a starting year. Filter out everything before this
start_yr <- 1997 # We ignore 1996 because majority are left censored individuals
end_yr   <- 2022 # Technically we can use data from early 2023, but not enough samples for year RE
```

## Extract model data

Extract vital rate observations to fit models. 2023 is excluded to use to test predictive accuracy.

```{r}
#Generate data to start simulation (at first observation)
if (file.exists(here::here("./data/model_data.RDS"))) {
  model_data <- readRDS(here::here("./data/model_data.RDS"))
} else {
  
  db.path <- here::here("./hyena_data/Fisidata_2025_04_18.sqlite")
  
  model_data_raw <- SHIM::generate_model_data(db = db.path)
  
  ## Save data as anonymised df (remove IDs)
  model_data <- list(
    ## Save all data that we can use to extract other data (e.g. 2023 for predictive accuracy)
    all = model_data_raw$raw_data |> 
      mutate(rank_category2 = case_when(nat_rank_std >= 1/3 ~ "top",
                                        nat_rank_std <= -1/3 ~ "bottom",
                                        TRUE ~ "middle")),
    ## Save data for all other models
    F_surv_data = model_data_raw$F_surv_data |> 
      ## Filter just to include focal years
      filter(year <= end_yr) |> 
      mutate(rank_category2 = case_when(nat_rank_std >= 1/3 ~ "top",
                                        nat_rank_std <= -1/3 ~ "bottom",
                                        TRUE ~ "middle")) |> 
      select(surv, year, rank_category2, age, clan_size, start_clan),
    PreM_surv_data = model_data_raw$PreM_surv_data |> 
      ## Filter just to include focal years
      filter(year <= end_yr) |> 
      mutate(rank_category2 = case_when(nat_rank_std >= 1/3 ~ "top",
                                        nat_rank_std <= -1/3 ~ "bottom",
                                        TRUE ~ "middle")) |> 
      select(surv, year, rank_category2, age, clan_size, start_clan),
    PostM_surv_data = model_data_raw$PostM_surv_data |> 
      ## Filter just to include focal years
      filter(year <= end_yr) |> 
      select(surv, year, age, clan_size, start_clan, post_dispersal_status),
    F_twin_data = model_data_raw$F_twin_data |> 
      mutate(rank_category2 = case_when(nat_rank_std >= 1/3 ~ "top",
                                        nat_rank_std <= -1/3 ~ "bottom",
                                        TRUE ~ "middle")) |> 
      select(twin, year, rank_category2, age, clan_size, start_clan, after1y_effort_all),
    F_repro_primi = model_data_raw$F_repro_primi |> 
      ## Filter just to include focal years
      filter(year <= end_yr) |> 
      mutate(rank_category2 = case_when(nat_rank_std >= 1/3 ~ "top",
                                        nat_rank_std <= -1/3 ~ "bottom",
                                        TRUE ~ "middle")) |> 
      select(repro, year, rank_category2, clan_size, start_clan, after1y_effort_all, months),
    F_repro_nonprimi = model_data_raw$F_repro_nonprimi |> 
      ## Filter just to include focal years
      filter(year <= end_yr) |> 
      mutate(rank_category2 = case_when(nat_rank_std >= 1/3 ~ "top",
                                        nat_rank_std <= -1/3 ~ "bottom",
                                        TRUE ~ "middle")) |> 
      select(repro, year, rank_category2, clan_size, start_clan, after1y_effort_all, months, age),
    M_second_disp_data = model_data_raw$M_second_disp_data |> 
      ## Filter just to include focal years
      filter(year <= end_yr) |> 
      select(second_disp, age, is_philo, year))
  
  saveRDS(model_data, here::here("./data/model_data.RDS"))
  
}
```

## Create utility fn

This function is used to compare models with different link functions using AIC.

```{r}
## Can add "cloglog" and "cauchit" to linkfn if you want, but this can struggle to converge
compare_linkfn <- function(formula, ..., linkfn = c("logit", "probit")) {
  
  all_mods <- lapply(linkfn, FUN = \(link){
    spaMM::fitme(formula, ..., family = binomial(link = link))
  })
  names(all_mods) <- linkfn
  
  AICs <- data.frame(linkfn = linkfn,
                     AIC = sapply(all_mods, FUN = \(mod){
                       AIC(mod, verbose = FALSE)[1]
                     })) %>% 
    dplyr::arrange(AIC)
  
  print(AICs)
  return(all_mods)
}
```

Fit models with different exponents on clan size...

```{r}
fit_exp <- function(x, model, data, verbose){
  
  data$old_clan_size <- data$clan_size
  data$clan_size     <- data$clan_size^x
  
  if (verbose) {
    mod <- update(model, data = data, family = family(model))
  } else {
    mod <- suppressMessages(update(model, data = data, family = family(model))) 
  }
  return(mod)
}
```

Function to calculate Brier scores. This can be used as an alternative to optimising on log likelihood.

```{r}
## NOTE: Data expects to be already filtered with our output (e.g. surv) in a column called 'event'
## Also see DescTools::BrierScore
## Alternative, Metrics::logLoss
calc_brierScore <- function(data, model){
  
  ## Predict outcomes...
  data$predict <- as.numeric(spaMM::predict.HLfit(object = model, newdata = data))
  ## Convert observed outcomes (TRUE/FALSE) to integer
  data$event <- as.numeric(data$event)
  
  ## Calculate Brier score
  Brier_score <- (1/nrow(data))*sum((data$predict - data$event)^2)
  
  return(Brier_score)
  
}
```

Extract model log likelihood for different exponents

```{r}
exp_estimation <- function(x, data, model, pb, verbose = TRUE, metric = "logLik", test_data){
  
  if (!missing(pb)) {
    pb$tick() 
  }
  
  mod <- fit_exp(x = x, data = data, model = model, verbose = verbose)
  
  if (metric == "logLik"){
    mod_loglik <- logLik(mod)[[1]]
    
    if (verbose) {
      print(paste("exponent:", x, ", loglik:", mod_loglik)) 
    }
    
    return(mod_loglik) 
  } else if (metric == "Brier"){
    
    ## Round to 4dp
    mod_Brier <- calc_brierScore(data = test_data, model = mod)
    
    if (verbose) {
      print(paste("exponent:", x, ", Brier score:", mod_Brier)) 
    }
    
    return(mod_Brier)
    
  } else {
    stop("'metric' should be logLik or Brier")
  }
  
}
```

Carry out likelihood profiling with different exponent values

```{r}
exp_profiling <- function(exp, data, model, optimize = TRUE, metric = "logLik", test_data, ...){
  
  if (metric == "logLik"){
    pb <- progress::progress_bar$new(total = length(exp))
    manual_loglik_opt <- sapply(exp, FUN = exp_estimation, data = data, model = model, pb = pb, verbose = FALSE)
    plot_data <- data.frame(exp = exp,
                            loglik = manual_loglik_opt)
    
    ## Include this if model struggles to optimize
    if (optimize) {
      algo_loglik_optim <- optimize(exp_estimation, lower = min(exp), upper = max(exp), data = data, model = model, verbose = FALSE,
                                    maximum = TRUE, ...) 
    } else {
      algo_loglik_optim <- list()
      algo_loglik_optim$objective <- max(plot_data$loglik)
      algo_loglik_optim$maximum <- plot_data$exp[plot_data$loglik == max(plot_data$loglik)]
    }
    
    loglik_1    <- exp_estimation(x = 1, data = data, model = model, verbose = FALSE)
    loglik_best <- exp_estimation(x = algo_loglik_optim$maximum, data = data, model = model, verbose = FALSE)
    
    pval <- pchisq(-2 * (loglik_1 - loglik_best), df = 1, lower.tail = FALSE)
    
    return(list(optim = algo_loglik_optim,
                data = plot_data,
                plot = ggplot(data = plot_data) +
                  geom_hline(yintercept = algo_loglik_optim$objective - qchisq(p = 0.95, df = 1)/2,
                             lty = 2) +
                  geom_line(aes(x = exp, y = loglik)) +
                  geom_point(aes(x = exp, y = loglik)) +
                  geom_point(aes(x = algo_loglik_optim$maximum, y = loglik_best),
                             size = 3, colour = "red") +
                  scale_x_continuous(limits = c(min(exp), max(exp)),
                                     breaks = seq(min(exp), max(exp), 1)) +
                  labs(title = paste("P-value difference between exp=1 and best exponent", round(algo_loglik_optim$maximum, 2), ":\n", round(pval, digits = 2), sep = " ")) +
                  theme_bw()))
    
  } else if(metric == "Brier"){
    
    pb <- progress::progress_bar$new(total = length(exp))
    manual_Brier_opt <- sapply(exp, FUN = exp_estimation, data = data, model = model, pb = pb, verbose = FALSE, metric = "Brier", test_data = test_data)
    plot_data <- data.frame(exp = exp,
                            Brier = manual_Brier_opt)
    
    ## Include this if model struggles to optimize
    if (optimize) {
      algo_Brier_optim <- optimize(exp_estimation, lower = min(exp), upper = max(exp), data = data, model = model, verbose = FALSE,
                                   metric = "Brier", test_data = test_data,
                                   maximum = FALSE, ...) 
    } else {
      algo_Brier_optim <- list()
      algo_Brier_optim$objective <- min(plot_data$Brier)
      ## Because we round our Brier scores, we can get multiple matches
      algo_Brier_optim$minimise <- plot_data$exp[plot_data$Brier == min(plot_data$Brier)]
    }
    
    Brier_best <- exp_estimation(x = algo_Brier_optim$minimise, data = data, model = model, verbose = FALSE, metric = "Brier", test_data = test_data)
    
    return(list(optim = algo_Brier_optim, 
                data = plot_data,
                plot = ggplot(data = plot_data) +
                  # geom_hline(yintercept = algo_loglik_optim$objective - qchisq(p = 0.95, df = 1)/2,
                  #            lty = 2) +
                  geom_line(aes(x = exp, y = Brier)) +
                  geom_point(aes(x = exp, y = Brier)) +
                  geom_point(aes(x = algo_Brier_optim$minimise, y = Brier_best),
                             size = 3, colour = "red") +
                  scale_x_continuous(limits = c(min(exp), max(exp)),
                                     breaks = seq(min(exp), max(exp), 1)) +
                  theme_bw()))
    
  }
  
}
```

## Fit models

### Female survival

```{r}
train_data <- model_data$all |>
  dplyr::filter(year <= end_yr) |> 
  dplyr::filter(!is.na(.data$rank_category) & .data$sex == "female" & !is.na(.data$age)) %>%
  #Filter out the (very few) cases where a female has changed status during a month
  dplyr::filter(!(.data$status_start != .data$status_end & stringr::str_detect(.data$status_end, "selector|disperser|immigrant|transient")))

test_data <- model_data$all |> 
  dplyr::filter(year > end_yr) |> 
  dplyr::filter(!is.na(.data$rank_category) & .data$sex == "female" & !is.na(.data$age)) %>%
  #Filter out the (very few) cases where a female has changed status during a month
  dplyr::filter(!(.data$status_start != .data$status_end & stringr::str_detect(.data$status_end, "selector|disperser|immigrant|transient"))) |> 
  rename(event = surv)
```


```{r}
F_surv_mod_yr <- compare_linkfn(surv ~ poly(age, 2)*rank_category2 +
                                  clan_size +
                                  ## Based on reviewer comments we may also want to add ID but
                                  ## this takes ages to converge on my Mac (need on server I guess)
                                  ## leaving out for now
                                  clan_size:rank_category2 + start_clan + (1|start_clan:year),
                                data = train_data,
                                method = "PQL/L")
```

Logit is the best using AIC. What about with Brier score? Does it affect our predictive power?

```{r}
for(model in names(F_surv_mod_yr)){
  score <- round(calc_brierScore(data = test_data, model = F_surv_mod_yr[[model]]), 4)
  print(paste0(model, " Brier score: ", score))
}
```

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(exp = seq(0, 3, 0.25),
                        data = train_data,
                        model = F_surv_mod_yr$logit)
output$plot
```

```{r}
output$optim
```

*No significant difference from 1 exponent*. Best is `r output$optim$maximum`

Compare exponents using Brier score

```{r}
output_Brier <- exp_profiling(exp = seq(-1, 3, 0.1),
                              data = train_data, model = F_surv_mod_yr$logit,
                              test_data = test_data, metric = "Brier", optimize = FALSE)
output_Brier$plot
```
```{r}
output_Brier$optim
```

Based on Brier score, best option is `r output_Brier$optim$minimise`

#### Plot

Plot a) Model with no exp (i.e. x = 1); b) model with best exponent from logLik; c) best exponent from Brier score

```{r}
best_logLik  <- fit_exp(x = output$optim$maximum,
                        model = F_surv_mod_yr$logit, data = train_data, verbose = FALSE)
best_Brier  <- fit_exp(x = output_Brier$optim$minimise,
                       model = F_surv_mod_yr$logit, data = train_data, verbose = FALSE)
noexp  <- fit_exp(x = 1, model = F_surv_mod_yr$logit, data = train_data, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         rank_category2 = c("top", "middle", "bottom"), age = 120, months = 12) %>% 
  mutate(`Optimal (log likelihood)` = as.numeric(predict(best_logLik, newdata = ., type = "response", re.form = NA)),
         `Optimal (Brier)` = as.numeric(predict(best_Brier, newdata = ., type = "response", re.form = NA)),
         `No exponent` = as.numeric(predict(noexp, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(c(starts_with("Opt"), `No exponent`))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = rank_category2)) +
  facet_wrap(facets = ~name, scales = "free_y")
```

For simplicity, we stick with no exponent (i.e. x = 1).

### Male pre-dispersal survival

```{r}
train_data <- model_data$all |>
  dplyr::filter(year <= end_yr) |> 
  dplyr::filter(!is.na(.data$rank_category) & .data$sex == "male" & !is.na(.data$age) &
                    .data$dispersal_status == "pre_dispersal")

test_data <- model_data$all |> 
  dplyr::filter(year > end_yr) |> 
  dplyr::filter(!is.na(.data$rank_category) & .data$sex == "male" & !is.na(.data$age) &
                    .data$dispersal_status == "pre_dispersal") |> 
  rename(event = surv)
```

```{r}
PreM_surv_mod_yr <- compare_linkfn(surv ~ poly(age, 2)*rank_category2 +
                                     clan_size +
                                     clan_size:rank_category2 + start_clan + (1|start_clan:year),
                                   data = train_data,
                                   method = "PQL/L")
```

logit is equally good.

```{r}
for(model in names(PreM_surv_mod_yr)){
  score <- round(calc_brierScore(data = test_data, model = PreM_surv_mod_yr[[model]]), 4)
  print(paste0(model, " Brier score: ", score))
}
```

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(exp = c(seq(-1, -0.25, 0.25),
                                seq(0.25, 2, 0.25),
                                3, 4, 5, 6),
                        data = train_data,
                        model = PreM_surv_mod_yr$logit,
                        ## Struggling to optimise alogrithmically
                        optimize = FALSE)
output$plot
```

No sig difference. -0.25 is best.

```{r}
output$optim
```

Compare exponents using Brier score

```{r}
output_Brier <- exp_profiling(exp = seq(-1, 6, 0.25),
                              model = PreM_surv_mod_yr$logit,
                              data = train_data,
                              test_data = test_data, metric = "Brier", optimize = FALSE)
output_Brier$plot
```

```{r}
output_Brier$optim
```

#### Plot

Plot a) Model with no exp (i.e. x = 1); b) model with best exponent from logLik; c) best exponent from Brier score

```{r}
best_logLik  <- fit_exp(x = output$optim$maximum,
                        model = PreM_surv_mod_yr$logit, data = train_data, verbose = FALSE)
best_Brier  <- fit_exp(x = output_Brier$optim$minimise,
                       model = PreM_surv_mod_yr$logit, data = train_data, verbose = FALSE)
noexp  <- fit_exp(x = 1, model = PreM_surv_mod_yr$logit, data = train_data, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         rank_category2 = c("top", "middle", "bottom"), age = 120, months = 12) %>% 
  mutate(`Optimal (log likelihood)` = as.numeric(predict(best_logLik, newdata = ., type = "response", re.form = NA)),
         `Optimal (Brier)` = as.numeric(predict(best_Brier, newdata = ., type = "response", re.form = NA)),
         `No exponent` = as.numeric(predict(noexp, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(c(starts_with("Opt"), `No exponent`))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = rank_category2)) +
  facet_wrap(facets = ~name, scales = "free_y")
```

### Male post-dispersal survival

```{r}
train_data <- model_data$all |>
  dplyr::filter(year <= end_yr) |> 
  dplyr::filter(.data$sex == "male" & !is.na(.data$age) &
                    .data$dispersal_status == "post_dispersal") %>%
    dplyr::mutate(post_dispersal_status = as.factor(.data$post_dispersal_status)) %>%
    #In this case, we need to exclude the month of dispersal (not clear how long they were pre-disperser or post-disperser here)
    #Also exclude the month changing from natal to philo.
    #We don't do this for females because they are still within the same model and status is not included as a model term
    dplyr::filter(!(.data$status_start != .data$status_end & stringr::str_detect(.data$status_end,
                                                                                 "selector|disperser|immigrant|transient|philopatric")))

test_data <- model_data$all |> 
  dplyr::filter(year > end_yr) |> 
  dplyr::filter(.data$sex == "male" & !is.na(.data$age) &
                    .data$dispersal_status == "post_dispersal") %>%
    dplyr::mutate(post_dispersal_status = as.factor(.data$post_dispersal_status)) %>%
    #In this case, we need to exclude the month of dispersal (not clear how long they were pre-disperser or post-disperser here)
    #Also exclude the month changing from natal to philo.
    #We don't do this for females because they are still within the same model and status is not included as a model term
    dplyr::filter(!(.data$status_start != .data$status_end & stringr::str_detect(.data$status_end,
                                                                                 "selector|disperser|immigrant|transient|philopatric"))) |> 
  rename(event = surv)
```

```{r}
PostM_surv_mod_yr <- compare_linkfn(surv ~ poly(age, 2)*post_dispersal_status +
                                      clan_size +
                                      start_clan + (1|start_clan:year),
                                    data = train_data,
                                    method = "PQL/L")
```

logit is comparable (a bit worse than probit and cloglog but kept for easy comparison)

```{r}
for(model in names(PostM_surv_mod_yr)){
  score <- round(calc_brierScore(data = test_data, model = PostM_surv_mod_yr[[model]]), 4)
  print(paste0(model, " Brier score: ", score))
}
```

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(c(-2, -1, -0.5, -0.1, 0.1, 0.5, 1, 2, 3, 4, 5, 6, 7), data = train_data,
                        model = PostM_surv_mod_yr$logit)
output$plot
```

Not significantly different to 1. Best is 1

Compare exponents using Brier score

```{r}
output_Brier <- exp_profiling(exp = seq(-2, 7, 0.5), data = train_data, model = PostM_surv_mod_yr$logit,
                              test_data = test_data, metric = "Brier", optimize = FALSE)
output_Brier$plot
```

```{r}
output_Brier$optim
```

#### Plot

```{r}
best_logLik  <- fit_exp(x = output$optim$maximum,
                        model = PostM_surv_mod_yr$logit, data = train_data, verbose = FALSE)
best_Brier  <- fit_exp(x = output_Brier$optim$minimise,
                       model = PostM_surv_mod_yr$logit, data = train_data, verbose = FALSE)
noexp  <- fit_exp(x = 1, model = PostM_surv_mod_yr$logit, data = train_data, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         rank_category2 = c("top", "middle", "bottom"), age = 120, months = 12) %>% 
  mutate(`Optimal (log likelihood)` = as.numeric(predict(best_logLik, newdata = ., type = "response", re.form = NA)),
         `Optimal (Brier)` = as.numeric(predict(best_Brier, newdata = ., type = "response", re.form = NA)),
         `No exponent` = as.numeric(predict(noexp, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(c(starts_with("Opt"), `No exponent`))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = rank_category2)) +
  facet_wrap(facets = ~name, scales = "free_y")
```

logit with no exponent.

### Primiparous reproduction

```{r}
F_repro_primi_mod_yr <- compare_linkfn(repro ~ log(months+0.01)*rank_category2 +
                                         rank_category2*clan_size +
                                         after1y_effort_all + start_clan + (1|start_clan:year),
                                       data = model_data$F_repro_primi,
                                       method = "PQL/L")
```

Probit is much better, but sticking with logit now for consistency.

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(c(-2, -1, -0.5, -0.1, 0.1, 0.5, 1, 2), data = model_data$F_repro_primi, model = F_repro_primi_mod_yr$logit)
output
```

No significant different. Best is -0.71

#### Plot

```{r}
best1y  <- fit_exp(x = -0.71, model = F_repro_primi_mod_yr$logit, data = model_data$F_repro_primi, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         rank_category2 = c("top", "middle", "bottom"), age = 120, months = 12) %>% 
  mutate(pred1y = as.numeric(predict(F_repro_primi_mod_yr$logit, newdata = ., type = "response", re.form = NA)),
         pred1y_best = as.numeric(predict(best1y, newdata = ., type = "response", re.form = NA)),
         pred1y_probit = as.numeric(predict(F_repro_primi_mod_yr$probit, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(starts_with("pred"))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = rank_category2)) +
  facet_wrap(facets = ~name, scales = "free_y")
```

Logit with no exponent is best.

### Multiparous reproduction

```{r}
F_repro_nonprimi_mod_yr <- compare_linkfn(repro ~ log(months+0.01)*rank_category2 + log(months+0.01)*age +
                                            clan_size*rank_category2 + after1y_effort_all + start_clan + (1|start_clan:year),
                                          data = model_data$F_repro_nonprimi,
                                          method = "PQL/L")
```

Logit is best.

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(c(-2, -1.5, -1, -0.5, -0.1, 0.1, 0.5, 1, 2, 3, 4, 5, 6, 7), data = model_data$F_repro_nonprimi, model = F_repro_nonprimi_mod_yr$logit)
output
```

No significant difference. Best is 0.39

#### Plot

```{r}
best1y  <- fit_exp(x = 0.39, model = F_repro_nonprimi_mod_yr$logit, data = model_data$F_repro_nonprimi, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         rank_category2 = c("top", "middle", "bottom"), age = 120, months = 12) %>% 
  mutate(pred1y = as.numeric(predict(F_repro_nonprimi_mod_yr$logit, newdata = ., type = "response", re.form = NA)),
         pred1y_best = as.numeric(predict(best1y, newdata = ., type = "response", re.form = NA)),
         pred1y_probit = as.numeric(predict(F_repro_nonprimi_mod_yr$probit, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(starts_with("pred"))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = rank_category2)) +
  facet_wrap(facets = ~name, scales = "free_y")
```

Logit with no exponent.

### Twinning

```{r}
twin_mod_yr <- compare_linkfn(twin ~ poly(age, 2)*rank_category2 +
                                after1y_effort_all +
                                clan_size*rank_category2 +
                                start_clan + (1|start_clan:year),
                              data = model_data$F_twin_data,
                              method = "PQL/L")
```

Probit/logit are identical...stick with logit.

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(c(-3, -2.5, -2, -1.5, -1, -0.5, -0.1, 0.1, 0.5, 1, 2, 3, 4, 5, 6, 7), data = model_data$F_twin_data, model = twin_mod_yr$logit)
output
```

No significant difference. Best is -0.33

#### Plot

```{r}

best1y  <- fit_exp(x = -0.33, model = twin_mod_yr$logit, data = model_data$F_twin_data, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         rank_category2 = c("top", "middle", "bottom"), age = 120, months = 12) %>% 
  mutate(pred1y = as.numeric(predict(twin_mod_yr$logit, newdata = ., type = "response", re.form = NA)),
         pred1y_best = as.numeric(predict(best1y, newdata = ., type = "response", re.form = NA)),
         pred1y_probit = as.numeric(predict(twin_mod_yr$probit, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(starts_with("pred"))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = rank_category2)) +
  facet_wrap(facets = ~name)
```

Stick with logit with no exponent...
