---
title: "02_demographic_data"
author: "Liam D. Bailey"
date: "2025-04-26"
output: html_document
---

## EXTRACT DEMOGRAPHIC DATA:

```{r}
## Prepare workspace
library(hyenaR)
library(tidyr)
library(dplyr)
library(SHIM)
library(here)
library(ggplot2)
library(lay)
```

```{r}
## Define number of cores for parallel processing
cores_used <- 8
```

```{r}
## This was extract in April 2025, last sighting was Feb 2025.
db.path     <- here::here("./hyena_data/Fisidata_2025_04_18.sqlite")
start_year  <- 1997 ## First year to estimate K
end_year    <- 2023 ## Last year to estimate K
```

## Absolute population size

We extract number of individuals, separated by sex and lifestage (i.e. adult v. non-adult). NOTE: This will be very slightly different if we just extracted all individuals because some are missed if their lifestage or sex is unknown. This is a small number and not relevant for plotting.

We extract data at monthly and yearly level. Currently, only annual data is used in plots to match the scale of our estimate of Kt.

### Population level

Calculate number of individuals in the whole population (main clans). NOTE: This might not match exactly to the sum of all clan sizes within a time period because individuals may be double counted when moving between clans.

```{r}
if (!file.exists(here::here("./data/Nplot_data_separate_year.RDS"))) {
  
  hyenaR::load_package_database.full(db.path)
  
  ## We include all data with at least 1y observations afterwards. Exclude Jan/Feb 2022 just to make it easier to describe!
  real_pop_separate <- dplyr::tibble(date = seq(as.Date("1996-01-01"), as.Date("2023-01-01"), by = "1 year")) %>%
    dplyr::mutate(from = date, to = lead(date)) |>
    dplyr::filter(!is.na(to))
  
  ## Only start half way in 1996 (we don't monitor the whole year)
  real_pop_separate$date[1] <- as.Date("1996-05-01")
  
  real_pop_separate <- real_pop_separate |> 
    dplyr::mutate(young = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$from, to = .data$to,
                                                   CPUcores = cores_used, .parallel.min = 50,
                                                   lifestage = "!adult"),
                  ad_male = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$from, to = .data$to,
                                                     CPUcores = cores_used, .parallel.min = 50,
                                                     lifestage = "adult", sex = "male"),
                  ad_fem = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$from, to = .data$to,
                                                    CPUcores = cores_used, .parallel.min = 50,
                                                    lifestage = "adult", sex = "female")
    )
  
  saveRDS(real_pop_separate, file = here::here("./data/Nplot_data_separate_year.RDS"))
}
```

```{r}
## Calculate monthly output (if not already saved)
if (!file.exists(here::here("./data/Nplot_data_separate_1month.RDS"))) {
  
  hyenaR::load_package_database.full(db.path)
  
  ## Exclude first few months of 2024 just to make it easier to describe breaks
  ## Extract ALL data here, but not all is used to fit models
  real_pop_separate <- dplyr::tibble(date = seq(as.Date("1996-05-01"), as.Date("2024-01-01"), by = "1 month")) %>%
    dplyr::mutate(young = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$date, to = lead(.data$date),
                                                   CPUcores = cores_used, .parallel.min = 50,
                                                   lifestage = "!adult"),
                  ad_male = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$date, to = lead(.data$date),
                                                     CPUcores = cores_used, .parallel.min = 50,
                                                     lifestage = "adult", sex = "male"),
                  ad_fem = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$date, to = lead(.data$date),
                                                    CPUcores = cores_used, .parallel.min = 50,
                                                    lifestage = "adult", sex = "female")
    )
  
  saveRDS(real_pop_separate, file = here::here("./data/Nplot_data_separate_1month.RDS"))
}
```

### Clan level

Do the same thing, but for each of the main clans individually. NOTE: This might not match exactly to the total population size calculated above due to double counting during dispersal.

```{r}
if (!file.exists(here::here("./data/NClanplot_data_separate_year.RDS"))) {
  
  hyenaR::load_package_database.full(db.path)
  
  ## We include all data with at least 1y observations afterwards. Exclude Jan/Feb 2022 just to make it easier to describe!
  real_clan_separate <- dplyr::tibble(date = seq(as.Date("1996-01-01"), as.Date("2023-01-01"), by = "1 year")) %>%
    dplyr::mutate(from = date, to = lead(date)) |>
    dplyr::filter(!is.na(to))
  
  ## Only start half way in 1996 (we don't monitor the whole year)
  real_clan_separate$date[1] <- as.Date("1996-05-01")
  
  real_clan_separate <- real_clan_separate |> 
    dplyr::mutate(clan = list(hyenaR::find_clan_name.all())) |>
    tidyr::unnest(cols = clan) |>
    dplyr::mutate(young = hyenaR::fetch_clan_number(clan = clan, from = .data$from, to = .data$to,
                                                    CPUcores = cores_used, .parallel.min = 50,
                                                    lifestage = "!adult"),
                  ad_male = hyenaR::fetch_clan_number(clan = clan, from = .data$from, to = .data$to,
                                                      CPUcores = cores_used, .parallel.min = 50,
                                                      lifestage = "adult", sex = "male"),
                  ad_fem = hyenaR::fetch_clan_number(clan = clan, from = .data$from, to = .data$to,
                                                     CPUcores = cores_used, .parallel.min = 50,
                                                     lifestage = "adult", sex = "female")
    )
  
  saveRDS(real_clan_separate, file = here::here("./data/NClanplot_data_separate_year.RDS"))
}
```

```{r}
if (!file.exists(here::here("./data/NClanplot_data_separate_1month.RDS"))) {
  
  hyenaR::load_package_database.full(db.path)

  ## We include all data with at least 1y observations afterwards. Exclude Jan/Feb 2022 just to make it easier to describe!
  real_clan_separate <- dplyr::tibble(date = seq(as.Date("1996-05-01"), as.Date("2023-01-01"), by = "1 month")) %>%
    dplyr::mutate(clan = list(hyenaR::find_clan_name.all())) |>
    tidyr::unnest(cols = clan) |>
    dplyr::mutate(young = hyenaR::fetch_clan_number(clan = clan, from = .data$date, to = lead(.data$date),
                                                   CPUcores = cores_used, .parallel.min = 50,
                                                   lifestage = "!adult"),
                  ad_male = hyenaR::fetch_clan_number(clan = clan, from = .data$date, to = lead(.data$date),
                                                     CPUcores = cores_used, .parallel.min = 50,
                                                     lifestage = "adult", sex = "male"),
                  ad_fem = hyenaR::fetch_clan_number(clan = clan, from = .data$date, to = lead(.data$date),
                                                    CPUcores = cores_used, .parallel.min = 50,
                                                    lifestage = "adult", sex = "female")
    )

  saveRDS(real_clan_separate, file = here::here("./data/NClanplot_data_separate_1month.RDS"))
}
```

## Compare data to understand difference in calculation methods

Calculate absolute population size for comparison (no distinction for lifestage/sex).

```{r}
if (!file.exists(here::here("./data/Nplot_data_year.RDS"))) {
  
  hyenaR::load_package_database.full(db.path)

  real_pop <- dplyr::tibble(date = seq(as.Date("1996-01-01"), as.Date("2023-01-01"), by = "1 year")) %>%
    dplyr::mutate(from = date, to = lead(date)) |>
    dplyr::filter(!is.na(to))

  ## In first year, just consider the
  real_pop$from[1] <- "1996-05-01"

  real_pop <- real_pop |>
    dplyr::mutate(pop_size = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$from, to = .data$to,
                                                      CPUcores = cores_used, .parallel.min = 285),
                  adult_pop_size = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$from, to = .data$to, lifestage = "adult",
                                                            CPUcores = cores_used, .parallel.min = 285))
  
  saveRDS(real_pop, here::here("./data/Nplot_data_year.RDS"))
  
}
```

```{r}
whole_pop_combined <- readRDS(here::here("./data/Nplot_data_year.RDS"))
whole_pop_separate <- readRDS(here::here("./data/Nplot_data_separate_year.RDS")) |> 
  mutate(pop_sum = lay::lay(pick(young:ad_fem), sum))
clan_pop_separate  <- readRDS(here::here("./data/NClanplot_data_separate_year.RDS")) |> 
  mutate(pop_sum = lay::lay(pick(young:ad_fem), sum)) |> 
  group_by(date) |> 
  summarise(pop_sum_clan = sum(pop_sum))
```

```{r}
plot_data <- whole_pop_combined |> 
  dplyr::select(from, allindv = pop_size) |> 
  dplyr::left_join(whole_pop_separate |> 
                     select(from = date, knownsex = pop_sum)) |> 
  dplyr::left_join(clan_pop_separate |> 
                     select(from = date, perclan = pop_sum_clan)) |> 
  tidyr::pivot_longer(cols = allindv:perclan)

ggplot() +
  geom_point(data = plot_data,
             aes(x = from, y = value, colour = name))
```


