---
title: "02_demographic_data"
author: "Liam D. Bailey"
date: "2025-04-26"
output: html_document
---

```{r}
## Prepare workspace
library(hyenaR)
library(tidyr)
library(dplyr)
library(SHIM)
library(here)
library(ggplot2)
library(lay)
```

```{r}
## Define number of cores for parallel processing
cores_used <- 8
```

```{r}
## This was extract in April 2025, last sighting was Feb 2025.
db.path     <- here::here("./hyena_data/Fisidata_2025_04_18.sqlite")
start_year  <- 1997 ## First year to estimate K
end_year    <- 2023 ## Last year to estimate K
```

```{r}
hyenaR::load_package_database.full(db.path)
```

## Extracting demographic information

We have a challenge when estimating demographic data. For our analysis, it is most useful to consider an annual scale so that we can compare to estimates of Kt. However, if we just consider unique individuals in a year we risk overestimating the population size because not all those individuals will have been present at the same time. This issue is even worse at clan level!

Instead, it is more appropriate to estimate demographic data at the scale of month (i.e. number of unique individuals). Within a month, changes in lifestage/clan occur less frequently so issues of double counting is minimised. If we want annual estimates, we can then consider the maximum monthly value observed within a year.

### Maximum population size

We estimate number of adults and total number of individuals in the population in each month. We then take the MAXIMUM monthly population size for comparison to Kt.

```{r}
if (!file.exists(here::here("./data/Nplot_data_1month.RDS"))) {
  
  real_pop <- dplyr::tibble(date = seq(as.Date("1996-05-01"), as.Date("2025-01-01"), by = "1 month")) %>%
    dplyr::mutate(from = date, to = lead(date)) |>
    dplyr::filter(!is.na(to))
  
  real_pop <- real_pop |>
    dplyr::mutate(pop_size = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$from, to = .data$to,
                                                      CPUcores = cores_used, .parallel.min = 285),
                  adult_pop_size = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$from, to = .data$to, lifestage = "adult",
                                                            CPUcores = cores_used, .parallel.min = 285))
  
  saveRDS(real_pop, here::here("./data/Nplot_data_1month.RDS"))
  
}
```

```{r}
if (!file.exists(here::here("./data/Nplot_data_year.RDS"))) {
  
  ## Monthly data
  pop_size_month <- readRDS(here::here("./data/Nplot_data_1month.RDS"))
  
  ## Find max pop
  pop_size_year <- pop_size_month |>
    dplyr::mutate(year = lubridate::year(date)) |> 
    dplyr::group_by(year) |> 
    summarise(from = min(from), to = max(to),
              max_pop_size = max(pop_size),
              max_adult_pop_size = max(adult_pop_size), .groups = "drop")
  
  saveRDS(pop_size_year, here::here("./data/Nplot_data_year.RDS"))
  
}
```

### Maximum clan size

We also want to extract clan size data; however, we are faced with major issue of double counting due to dispersal. Instead, we calculate data within each month and then take the MAXIMUM clan size for each clan within a year. This also involves double counting, but it is more informative of the actual realised size that clans can reach.

```{r}
if (!file.exists(here::here("./data/NClanplot_data_1month.RDS"))) {
  
  ## We include all data with at least 1y observations afterwards. Exclude Jan/Feb 2022 just to make it easier to describe!
  real_clan_separate <- dplyr::tibble(date = seq(as.Date("1996-05-01"), as.Date("2025-01-01"), by = "1 month")) %>%
    dplyr::mutate(clan = list(hyenaR::find_clan_name.all())) |>
    tidyr::unnest(cols = clan) |>
    group_by(clan) |> 
    dplyr::mutate(clan_size = hyenaR::fetch_clan_number(clan = clan, from = .data$date, to = lead(.data$date),
                                                       CPUcores = cores_used, .parallel.min = 285),
                  adult_clan_size = hyenaR::fetch_clan_number(clan = clan, from = .data$date, to = lead(.data$date),
                                                             lifestage = "adult",
                                                             CPUcores = cores_used, .parallel.min = 285))
  
  saveRDS(real_clan_separate, file = here::here("./data/NClanplot_data_1month.RDS"))
  
}
```

```{r}
if (!file.exists(here::here("./data/NClanplot_data_year.RDS"))) {
  
  clan_size_month <- readRDS(here::here("./data/NClanplot_data_1month.RDS"))
  
  clan_size_year <- clan_size_month |>
    ## Filter last rows where we have no following data
    dplyr::filter(clan_size != 0) |> 
    dplyr::mutate(year = lubridate::year(date)) |> 
    dplyr::group_by(clan, year) |> 
    summarise(max_clan_size = max(clan_size),
              max_adult_clan_size = max(adult_clan_size), .groups = "drop")
  
  saveRDS(clan_size_year, file = here::here("./data/NClanplot_data_year.RDS"))
  
}
```

### Age and (adult) sex ratio

Calculate number of individuals in each of three groups: adult female, adult male, juvenile. This is for supplementary data and doesn't need to be aggregated up to annual value. We calculate a snapshot every 6mo.

```{r}
## Calculate monthly output (if not already saved)
if (!file.exists(here::here("./data/Nplot_data_separate_6month.RDS"))) {
  
  hyenaR::load_package_database.full(db.path)
  
  ## Exclude first few months of 2024 just to make it easier to describe breaks
  ## Extract ALL data here, but not all is used to fit models
  real_pop_separate <- dplyr::tibble(date = seq(as.Date("1996-07-01"), as.Date("2025-01-01"), by = "6 month")) %>%
    dplyr::mutate(young = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$date, to = lead(.data$date),
                                                   CPUcores = cores_used, .parallel.min = 50,
                                                   lifestage = "!adult"),
                  ad_male = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$date, to = lead(.data$date),
                                                     CPUcores = cores_used, .parallel.min = 50,
                                                     lifestage = "adult", sex = "male"),
                  ad_fem = hyenaR::fetch_pop_number(main.clans = TRUE, from = .data$date, to = lead(.data$date),
                                                    CPUcores = cores_used, .parallel.min = 50,
                                                    lifestage = "adult", sex = "female")
    )
  
  saveRDS(real_pop_separate, file = here::here("./data/Nplot_data_separate_6month.RDS"))
}
```
