---
title: "extract_mechanistic_data"
output: html_document
date: "2024-04-08"
---

## Prepare

Load required packages

```{r pkg}
library(ggplot2)
library(hyenaR)
library(dplyr)
library(here)
library(lay)
library(lubridate)
library(doSNOW)
library(patchwork)
library(spaMM)
library(DHARMa)
library(ggtext)
library(SHIM)
```

Define which simulation type we're using

```{r}
db.path     <- here("../hyena_data/Fisidata_20_04_2024.sqlite")
start_year  <- 1997
end_year    <- 2022
```

Load database

```{r}
load_package_database.full(db.path)
```


## Analysis for whole population

### Prey data

```{r}
prey_plot_datapop <- extract_database_table("sightings") %>% 
  filter(!is.na(prey) & clanID %in% find_clan_name.all(main.clans = TRUE)) %>% 
  mutate(year = lubridate::year(date_time)) %>% 
  select(year, prey, clan = clanID) %>% 
  group_by(year, clan) %>% 
  summarise(avgprey = mean(prey),
            se = sd(prey)/sqrt(n()),
            .groups = "drop") |> 
  filter(year >= start_year & year <= end_year)
```

```{r}
ggplot(data = prey_plot_datapop) +
  geom_ribbon(aes(x = year, ymin = avgprey - se, ymax = avgprey + se),
              alpha = 0.5) +
  geom_line(aes(x = year, y = avgprey)) +
  labs(title = "Prey categories") +
  theme_classic() +
  facet_wrap(facets = ~clan)
```

### Lion data

Here we need to have the clan homeranges (pre and post 2012) so that we can determine lion density.

```{r, message=FALSE}
homeranges <- tibble(clan = find_clan_name.all(),
                     merge_val = 1) %>% 
  left_join(tibble(from = c(paste0(start_year, "-01-01"),
                            "2012-01-01"),
                   to = c("2011-12-31",
                          paste0(end_year, "-12-31")),
                   merge_val = 1), by = "merge_val", multiple = "all") %>% 
  mutate(homerangepoly = hyenaR::fetch_clan_homerange(clan = clan, lifestage = "adult", sex = "female",
                                                      from = from, to = to, hr.args = list(levels = 0.95)))

plot_homerange_data <- homeranges %>% 
  sf::st_as_sf()

ggplot() +
  geom_sf(data = hyenaR::sf_hyenaR$rim_polygon) +
  geom_sf(data = plot_homerange_data, aes(fill = clan),
          alpha = 0.5) +
  facet_wrap(facets = ~from) +
  theme_void()
```

Extract lion data

```{r}
all_lions <- extract_database_table("carnivores") %>% 
  filter(species == "li" & !is.na(longitude) & !is.na(latitude)) %>% 
  #When there are >1 record with same date_time & lat-long just take the first (these are duplicates which are already recorded in group size)
  group_by(date_time, latitude, longitude) %>% 
  slice(1) %>% 
  ungroup() %>% 
  mutate(year = year(date_time)) %>% 
  sf::st_as_sf(coords = c("longitude", "latitude")) %>% 
  select(year, groupsize) %>% 
  sf::st_set_crs("EPSG:4326") %>% 
  sf::st_transform(sf::st_crs(plot_homerange_data))
```

Join with homerange depending on overlap

```{r}
lion_homerange_overlap <- plot_homerange_data %>% 
  sf::st_join(all_lions)
```

For each clan/year determine the number of lions/m2

```{r}
lion_density <- lion_homerange_overlap %>% 
  group_by(clan, year) %>% 
  summarise(total_lions = sum(groupsize),
            total_sightings = n(),
            .groups = "drop") %>% 
  #Area in km2 (returns m2 by default)
  mutate(homerangearea = as.numeric(sf::st_area(.))*1e-6) %>% 
  mutate(lion_density = total_lions/homerangearea,
         sighting_density = total_sightings/homerangearea)
```

Plot density

```{r}
ggplot(data = lion_density) +
  geom_line(aes(x = year, y = lion_density, colour = clan)) +
  facet_wrap(facets = ~clan) +
  theme_classic()
```

Plot sightings

```{r}
ggplot(data = lion_density) +
  geom_line(aes(x = year, y = sighting_density, colour = clan)) +
  facet_wrap(facets = ~clan) +
  theme_classic()
```

Join with existing data

```{r}
mod_data_all <- prey_plot_datapop |> 
  left_join(lion_density |> 
              sf::st_drop_geometry(),
            by = c("clan", "year"))
```

### Disease

```{r}
disease_raw <- extract_database_table("injuries") %>% 
  filter(grepl(tolower(cause), pattern = "strep|disease") & !grepl(ID, pattern = "cub")) %>% 
  mutate(year = year(date_time),
         clan = fetch_id_clan.current(ID = ID, at = date_time)) %>% 
  group_by(year, clan) %>% 
  summarise(clan_disease = n(),
            .groups = "drop")
```

```{r}
mod_data_alldisease <- mod_data_all %>% 
  left_join(disease_raw, by = c("year", "clan")) %>% 
  mutate(total_disease = tidyr::replace_na(clan_disease, 0),
         from = lubridate::ymd(paste(year, "01", "01", sep = "-")),
         to = lubridate::ymd(paste(year + 1, "01", "01")) - lubridate::days(1)) %>% 
  mutate(clan_size = fetch_clan_number(clan = clan, from = from, to = to)) %>% 
  mutate(total_disease_percap = total_disease/clan_size)
```

### Add conservation actions

Road use change occurred during 2006.
Grazing ban occurred during 2016.

```{r}
mod_data_alldisease_consv <- mod_data_alldisease %>% 
  dplyr::mutate(roaduse = ifelse(year > 2006, "active", "inactive"),
                grazing = ifelse(year %in% 1996:2016 & clan %in% c("A", "F"), "present", "abscent")) %>% 
  arrange(clan, year)
```

### Standardise variables

For our analysis it would be useful to use scaled Z-scores to compare different variables.

```{r}
mod_data_alldisease_consv$total_disease_percap_scale <- scale(mod_data_alldisease_consv$total_disease_percap)[,1]
mod_data_alldisease_consv$lion_density_scale <- scale(mod_data_alldisease_consv$lion_density)[,1]
mod_data_alldisease_consv$avgprey_scale <- scale(mod_data_alldisease_consv$avgprey)[,1]
```

### Save output data

```{r}
final_output <- mod_data_alldisease_consv |> 
  select(lion_density, lion_density_scale, avgprey, avgprey_scale, total_disease_percap, total_disease_percap_scale, roaduse, grazing, clan, year)

readr::write_excel_csv(final_output,
                       here("./data/mechanistic_model_data.csv"))

```
