---
title: "Model selection"
output:
  html_document: default
  pdf_document: default
date: "2023-01-23"
---

Identify best models used for the simulation. This will involve fitting different density dependent relationships.

We will fit models using random intercept of year.

## Packages

```{r}
library(dplyr)
library(ggplot2)
library(hyenaR)
```

```{r}
## Set a starting year. Filter out everything before this
start_yr <- 1997 # We ignore 1996 because majority are left censored individuals
end_yr   <- 2022 # Technically we can use data from early 2023, but not enough samples for year RE
```

## Extract model data

Extract data that has already been loaded.

```{r}
#Generate data to start simulation (at first observation)
## Generate model data from this
if (file.exists(here::here("./data/model_data.RDS"))) {
  model_data <- readRDS(here::here("./data/model_data.RDS"))
} else {
  
  #This data is up until 2024
  ## (so that means that individual deaths should be detectable in 2022)
  db.path <- "~/data/hyena_data/Fisidata_20_04_2024.sqlite"
  
  model_data <- SHIM::generate_model_data(db = db.path)
  
  ## Save data as (anonymised) df
  model_data <- list(F_surv_data = model_data$F_surv_data |> 
                       mutate(rank_category2 = case_when(nat_rank_std >= 1/3 ~ "top",
                                                         nat_rank_std <= -1/3 ~ "bottom",
                                                         TRUE ~ "middle")) |> 
                       select(surv, year, rank_category2, age, clan_size, start_clan),
                     PreM_surv_data = model_data$PreM_surv_data |> 
                       mutate(rank_category2 = case_when(nat_rank_std >= 1/3 ~ "top",
                                                         nat_rank_std <= -1/3 ~ "bottom",
                                                         TRUE ~ "middle")) |> 
                       select(surv, year, rank_category2, age, clan_size, start_clan),
                     PostM_surv_data = model_data$PostM_surv_data |> 
                       select(surv, year, age, clan_size, start_clan, post_dispersal_status),
                     F_twin_data = model_data$F_twin_data |> 
                       mutate(rank_category2 = case_when(nat_rank_std >= 1/3 ~ "top",
                                                         nat_rank_std <= -1/3 ~ "bottom",
                                                         TRUE ~ "middle")) |> 
                       select(twin, year, rank_category2, age, clan_size, start_clan, after1y_effort_all),
                     F_repro_primi = model_data$F_repro_primi |> 
                       mutate(rank_category2 = case_when(nat_rank_std >= 1/3 ~ "top",
                                                         nat_rank_std <= -1/3 ~ "bottom",
                                                         TRUE ~ "middle")) |> 
                       select(repro, year, rank_category2, clan_size, start_clan, after1y_effort_all, months),
                     F_repro_nonprimi = model_data$F_repro_nonprimi |> 
                       mutate(rank_category2 = case_when(nat_rank_std >= 1/3 ~ "top",
                                                         nat_rank_std <= -1/3 ~ "bottom",
                                                         TRUE ~ "middle")) |> 
                       select(repro, year, rank_category2, clan_size, start_clan, after1y_effort_all, months, age),
                     M_second_disp_data = model_data$M_second_disp_data |> 
                       select(second_disp, age, is_philo, year))
  
  saveRDS(model_data, here::here("./data/model_data.RDS"))
  
}
```

## Create utility fn

```{r}
compare_linkfn <- function(formula, ..., linkfn = c("logit", "probit", "cauchit", "cloglog")) {
  
  all_mods <- lapply(linkfn, FUN = \(link){
    spaMM::fitme(formula, ..., family = binomial(link = link))
  })
  names(all_mods) <- linkfn
  
  AICs <- data.frame(linkfn = linkfn,
                     AIC = sapply(all_mods, FUN = \(mod){
                       AIC(mod, verbose = FALSE)[1]
                     })) %>% 
    dplyr::arrange(AIC)
  
  print(AICs)
  return(all_mods)
}
```

```{r}
fit_exp <- function(x, model, data, verbose){
  
  data$old_clan_size <- data$clan_size
  data$clan_size     <- data$clan_size^x
  
  if (verbose) {
    mod <- update(model, data = data, family = family(model))
  } else {
    mod <- suppressMessages(update(model, data = data, family = family(model))) 
  }
  return(mod)
}
```

```{r}
exp_estimation <- function(x, data, model, pb, verbose = TRUE){
  
  if (!missing(pb)) {
    pb$tick() 
  }
  
  mod <- fit_exp(x = x, data = data, model = model, verbose = verbose)
  
  mod_loglik <- logLik(mod)[[1]]
  
  if (verbose) {
    print(paste("exponent:", x, ", loglik:", mod_loglik)) 
  }
  
  return(mod_loglik)
  
}
```

```{r}
exp_profiling <- function(exp, data, model, optimize = TRUE, ...){
  
  pb <- progress::progress_bar$new(total = length(exp))
  manual_loglik_opt <- sapply(exp, FUN = exp_estimation, data = data, model = model, pb = pb, verbose = FALSE)
  plot_data <- data.frame(exp = exp,
                          loglik = manual_loglik_opt)
  
  ## Include this if model struggles to optimize
  if (optimize) {
     algo_loglik_optim <- optimize(exp_estimation, lower = min(exp), upper = max(exp), data = data, model = model, verbose = FALSE,
                                maximum = TRUE, ...) 
  } else {
    algo_loglik_optim <- list()
    algo_loglik_optim$objective <- max(plot_data$loglik)
    algo_loglik_optim$maximum <- plot_data$exp[plot_data$loglik == max(plot_data$loglik)]
  }
  
  loglik_1    <- exp_estimation(x = 1, data = data, model = model, verbose = FALSE)
  loglik_best <- exp_estimation(x = algo_loglik_optim$maximum, data = data, model = model, verbose = FALSE)
  
  pval <- pchisq(-2 * (loglik_1 - loglik_best), df = 1, lower.tail = FALSE)
  
  return(ggplot(data = plot_data) +
           geom_hline(yintercept = algo_loglik_optim$objective - qchisq(p = 0.95, df = 1)/2,
                      lty = 2) +
           geom_line(aes(x = exp, y = loglik)) +
           geom_point(aes(x = exp, y = loglik)) +
           geom_point(aes(x = algo_loglik_optim$maximum, y = loglik_best),
                      size = 3, colour = "red") +
           scale_x_continuous(limits = c(min(exp), max(exp)),
                              breaks = seq(min(exp), max(exp), 1)) +
           labs(title = paste("P-value difference between exp=1 and best exponent", round(algo_loglik_optim$maximum, 2), ":\n", round(pval, digits = 2), sep = " ")) +
           theme_bw())
  
}
```

## Fit models

### Female survival

```{r}
F_surv_mod_yr <- compare_linkfn(surv ~ poly(age, 2)*rank_category2 +
                                  clan_size +
                                  clan_size:rank_category2 + start_clan + (1|start_clan:year),
                                data = model_data$F_surv_data,
                                method = "PQL/L")
```

Logit is the best.

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(exp = c(-1, -0.5, -0.1, 0.1, 0.5, 1, 2, 3), data = model_data$F_surv_data, model = F_surv_mod_yr$logit)
output
```

*No significant difference from 0 exponent* Best is 0.86

#### Plot

```{r}
best1y  <- fit_exp(x = 0.86, model = F_surv_mod_yr$logit, data = model_data$F_surv_data, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         rank_category2 = c("top", "middle", "bottom"), age = 120, months = 12) %>% 
  mutate(pred1y = as.numeric(predict(F_surv_mod_yr$logit, newdata = ., type = "response", re.form = NA)),
         pred1y_best = as.numeric(predict(best1y, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(starts_with("pred"))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = rank_category2)) +
  facet_wrap(facets = ~name, scales = "free_y")
```

Logit with exp 1.

### Male pre-dispersal survival

```{r}
PreM_surv_mod_yr <- compare_linkfn(surv ~ poly(age, 2)*rank_category2 +
                                     clan_size +
                                     clan_size:rank_category2 + start_clan + (1|start_clan:year),
                                   data = model_data$PreM_surv_data,
                                   method = "PQL/L")
```

logit is equally good.

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(exp = c(seq(-1, -0.25, 0.25),
                                seq(0.25, 2, 0.25),
                                3, 4, 5, 6), data = model_data$PreM_surv_data,
                        model = PreM_surv_mod_yr$logit,
                        ## Struggling to optimise alogrithmically
                        optimize = FALSE)
output
```
No sig difference. -0.25 is best.

#### Plot

```{r}
best1y  <- fit_exp(x = -0.25, model = PreM_surv_mod_yr$logit, data = model_data$PreM_surv_data, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         rank_category2 = c("top", "middle", "bottom"), age = 12, months = 12) %>% 
  mutate(pred1y = as.numeric(predict(PreM_surv_mod_yr$logit, newdata = ., type = "response", re.form = NA)),
         pred1y_best = as.numeric(predict(best1y, newdata = ., type = "response", re.form = NA)),
         pred1y_logit = as.numeric(predict(PreM_surv_mod_yr$logit, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(starts_with("pred"))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = rank_category2)) +
  facet_wrap(facets = ~name)
```

logit exp 1 is best.

### Male post-dispersal survival

```{r}
PostM_surv_mod_yr <- compare_linkfn(surv ~ poly(age, 2)*post_dispersal_status +
                                      clan_size +
                                      start_clan + (1|start_clan:year),
                                    data = model_data$PostM_surv_data,
                                    method = "PQL/L")
```

logit is comparable (a bit worse than probit and cloglog but kept for easy comparison)

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(c(-2, -1, -0.5, -0.1, 0.1, 0.5, 1, 2, 3, 4, 5, 6, 7), data = model_data$PostM_surv_data,
                        model = PostM_surv_mod_yr$logit)
output
```

Not significantly different to 1. Best is 1

#### Plot

```{r}
best1y  <- fit_exp(x = 1, model = PostM_surv_mod_yr$logit, data = model_data$PostM_surv_data, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         post_dispersal_status = c("philo", "disp"), age = 120, months = 12) %>% 
  mutate(pred1y = as.numeric(predict(PostM_surv_mod_yr$logit, newdata = ., type = "response", re.form = NA)),
         pred1y_best = as.numeric(predict(best1y, newdata = ., type = "response", re.form = NA)),
         pred1y_cloglog = as.numeric(predict(PostM_surv_mod_yr$cloglog, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(starts_with("pred"))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = post_dispersal_status)) +
  facet_wrap(facets = ~name, scales = "free_y")
```

logit with no exponent.

### Primiparous reproduction

```{r}
F_repro_primi_mod_yr <- compare_linkfn(repro ~ log(months+0.01)*rank_category2 +
                                         rank_category2*clan_size +
                                         after1y_effort_all + start_clan + (1|start_clan:year),
                                       data = model_data$F_repro_primi,
                                       method = "PQL/L")
```

Probit is much better, but sticking with logit now for consistency.

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(c(-2, -1, -0.5, -0.1, 0.1, 0.5, 1, 2), data = model_data$F_repro_primi, model = F_repro_primi_mod_yr$logit)
output
```

No significant different. Best is -0.71

#### Plot

```{r}
best1y  <- fit_exp(x = -0.71, model = F_repro_primi_mod_yr$logit, data = model_data$F_repro_primi, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         rank_category2 = c("top", "middle", "bottom"), age = 120, months = 12) %>% 
  mutate(pred1y = as.numeric(predict(F_repro_primi_mod_yr$logit, newdata = ., type = "response", re.form = NA)),
         pred1y_best = as.numeric(predict(best1y, newdata = ., type = "response", re.form = NA)),
         pred1y_probit = as.numeric(predict(F_repro_primi_mod_yr$probit, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(starts_with("pred"))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = rank_category2)) +
  facet_wrap(facets = ~name, scales = "free_y")
```

Logit with no exponent is best.

### Multiparous reproduction

```{r}
F_repro_nonprimi_mod_yr <- compare_linkfn(repro ~ log(months+0.01)*rank_category2 + log(months+0.01)*age +
                                                    clan_size*rank_category2 + after1y_effort_all + start_clan + (1|start_clan:year),
                                          data = model_data$F_repro_nonprimi,
                                          method = "PQL/L")
```

Logit is best.

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(c(-2, -1.5, -1, -0.5, -0.1, 0.1, 0.5, 1, 2, 3, 4, 5, 6, 7), data = model_data$F_repro_nonprimi, model = F_repro_nonprimi_mod_yr$logit)
output
```

No significant difference. Best is 0.39

#### Plot

```{r}
best1y  <- fit_exp(x = 0.39, model = F_repro_nonprimi_mod_yr$logit, data = model_data$F_repro_nonprimi, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         rank_category2 = c("top", "middle", "bottom"), age = 120, months = 12) %>% 
  mutate(pred1y = as.numeric(predict(F_repro_nonprimi_mod_yr$logit, newdata = ., type = "response", re.form = NA)),
         pred1y_best = as.numeric(predict(best1y, newdata = ., type = "response", re.form = NA)),
         pred1y_probit = as.numeric(predict(F_repro_nonprimi_mod_yr$probit, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(starts_with("pred"))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = rank_category2)) +
  facet_wrap(facets = ~name, scales = "free_y")
```

Logit with no exponent.

### Twinning

```{r}
twin_mod_yr <- compare_linkfn(twin ~ poly(age, 2)*rank_category2 +
                                           after1y_effort_all +
                                           clan_size*rank_category2 +
                                           start_clan + (1|start_clan:year),
                              data = model_data$F_twin_data,
                              method = "PQL/L")
```

Probit/logit are identical...stick with logit.

Use likelihood profiling to pick best exponent value.

```{r}
output <- exp_profiling(c(-3, -2.5, -2, -1.5, -1, -0.5, -0.1, 0.1, 0.5, 1, 2, 3, 4, 5, 6, 7), data = model_data$F_twin_data, model = twin_mod_yr$logit)
output
```

No significant difference. Best is -0.33

#### Plot

```{r}

best1y  <- fit_exp(x = -0.33, model = twin_mod_yr$logit, data = model_data$F_twin_data, verbose = FALSE)

plot_data <- expand.grid(start_clan = "A", clan_size = 0:200, after1y_effort_all = 1,
                         rank_category2 = c("top", "middle", "bottom"), age = 120, months = 12) %>% 
  mutate(pred1y = as.numeric(predict(twin_mod_yr$logit, newdata = ., type = "response", re.form = NA)),
         pred1y_best = as.numeric(predict(best1y, newdata = ., type = "response", re.form = NA)),
         pred1y_probit = as.numeric(predict(twin_mod_yr$probit, newdata = ., type = "response", re.form = NA))) %>% 
  tidyr::pivot_longer(starts_with("pred"))

ggplot(data = plot_data)+
  geom_line(aes(x = clan_size, y = value, colour = rank_category2)) +
  facet_wrap(facets = ~name)
```

Stick with logit with no exponent...
