---
title: "EstimateK"
author: "Liam D. Bailey"
date: "2025-05-04"
output: html_document
---

Once we've run simulations, how do we define a simulation as stable and define K?

## Setup workspace

### Load packages

```{r}
library(dplyr)
library(ggplot2)
```

### Define years where we will calculate K

We exclude 1996 because we only have half a year of data. We exclude 2023 to have data where we can test predictive accuracy. 2024 is not used because we don't have enough observations (i.e. >1y) to accurately determine vital rates.

```{r}
## Set a starting year. Filter out everything before this
start_yr <- 1997 # We ignore 1996 because majority are left censored individuals
end_yr <- 2022 ## We want to also run for 2023, but hasn't been done yet
# end_yr   <- 2023 # We also have data from early 2024, but not enough samples for year RE
```

## Estimate K

### Extract model data

```{r}
all_data <- purrr::map_df(.x = start_yr:end_yr, .f = function(sim_year, folder_name){
  
  txt_files <- list.files(here::here(paste0("./STEP1_estimateK/", sim_year)),
                          pattern = ".txt", full.names = TRUE)
  
  allsims <- purrr::map_df(.x = txt_files,
                           .f = function(filepath){
                             
                             readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) |> 
                               dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=_)[0-9]+(?=.txt)"))
                             
                           }) |> 
    mutate(sim_year = sim_year)
  
  allsims
  
})

all_data_select <- all_data |> 
  select(sim_year, date, pop_size, sim)
```

### Calculate variance removing time steps

Remove data until we reach a variance below X (X is arbitrary...)

```{r}
## Try and example for sim 1
burnin_allyrs <- purrr::map_df(.x = start_yr:end_yr, .f = \(focal_year){
  
  allsims <- all_data_select |> 
    filter(sim_year == focal_year)
  
  purrr::map_df(.x = 1:10, \(sim_nr){
    
    simN <- allsims |> 
      filter(sim == sim_nr)
    
    ## Loop through removing 1 month at a time
    simN_var <- purrr::map_dfr(.x = 1:(nrow(simN) - 1), \(x){
      
      data.frame(sim = sim_nr, x = x,
                 var = var(simN$pop_size[x:nrow(simN)]))
      
    }) |> 
      mutate(sim_year = focal_year)
    
    ## Also calculate slope
    simN_var$slope <- c(purrr::map_dbl(.x = 1:(nrow(simN_var) - 1), \(i){
      
      diff(simN_var$var[i:(i+1)])
      
    }), NA)
    
    simN_var$pop_slope <- c(purrr::map_dbl(.x = 1:(nrow(simN_var) - 1), \(i){
      
      diff(simN$pop_size[i:(i+1)])
      
    }), NA)
    
    return(simN_var)
    
  })
  
})
```

```{r}
ggplot() +
  geom_line(data = burnin_allyrs,
            aes(x = x, y = var, group = sim), linewidth = 0.1) +
  facet_wrap(facets = ~sim_year)
```

```{r}
ggplot() +
  geom_line(data = burnin_allyrs,
            aes(x = x, y = slope, group = sim), linewidth = 0.1) +
  facet_wrap(facets = ~sim_year)
```

Our approach:

- In all simulations, population size increased from starting population (equivalent to status in 1997)
- We removed steps from each simulation to reduce variance in population size
- Each simulation was considered 'stable' once removing steps no longer decreased variance AND absolute variance was below 750.

Apply our approach below:

```{r}
stable_sims <- burnin_allyrs |> 
  group_by(sim, sim_year) |> 
  filter(x >= min(which(slope > 0)) & x >= min(which(var <= 750))) |> 
  slice(1) |> 
  ungroup() |> 
  arrange(sim_year, sim)

stable_sims
```

```{r}
range(stable_sims$x)
```

How quickly did sims converge?

```{r}
plot_data <- stable_sims |> 
  mutate(years_converge = x/12)

converge_hist <- ggplot() +
  geom_histogram(data = plot_data,
                 aes(x = years_converge), binwidth = 1,
                 colour = "black", fill = "grey80") +
  geom_vline(xintercept = median(plot_data$years_converge), lty = 2) +
  geom_text(aes(x = median(plot_data$years_converge) + 1,
                y = 55, label = paste0("Median: ", median(plot_data$years_converge), " years")),
            hjust = 0) +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(0, 70, by = 2),
           xend = seq(0, 70, by = 2),
           y = -0.5, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(0, 70, by = 10),
           xend = seq(0, 70, by = 10),
           y = -1, yend = 0,
           lineend = "round", linejoin = "round") +
  scale_x_continuous(breaks = seq(0, 100, 10),
                     name = "Time until equilibrium (years)")  +
  scale_y_continuous(name = "Number of simulations")  +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 60),
                  xlim = c(0, 70)) +
  theme_classic() +
  theme(legend.position = "right",
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 10),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(colour = "black", size = 10, margin = margin(r = 5)),
        axis.title = element_text(colour = "black", size = 12, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10),
        strip.text = element_text(size = 20, colour = "black"),
        strip.background = element_rect(colour = "grey80"))

ggplot2::ggsave(plot = converge_hist, here::here("./plots/sim_outputs/convergence_histogram.png"),
                height = 7, width = 8, dpi = 300)
```

How many years of data does this give us? In all but 3 sims, we end up with >67 years of data. Do we want to run these other sims longer?

```{r}
plot_data <- stable_sims |> 
  mutate(years_data = (1200-x)/12)

ggplot() +
  geom_histogram(data = plot_data,
                 aes(x = years_data), binwidth = 1) +
  scale_x_continuous(breaks = seq(30, 100, 10))
```

What does Kt look like using this method?

```{r}
stable_data <- all_data_select |> 
  group_by(sim, sim_year) |> 
  mutate(x = 1:n(), sim = as.integer(sim)) |> 
  select(sim, sim_year, x, pop_size) |> 
  ungroup() |> 
  left_join(stable_sims |> 
              select(sim, sim_year, burnin = x),
            by = c("sim", "sim_year")) |> 
  filter(x >= burnin)

KtN_calc <- stable_data |> 
  group_by(sim, sim_year) |> 
  summarise(KtN = median(pop_size), .groups = "drop")

Kt_calc <- KtN_calc |> 
  group_by(sim_year) |> 
  summarise(globalK = median(KtN),
            lower = min(KtN),
            upper = max(KtN),
            points = list(data.frame(pop_size = KtN))) |> 
  rename(year = sim_year)

saveRDS(Kt_calc, here::here("./data/Kplot_data.RDS"))
```

Compare to our previous hard cut-off method

```{r}
## Old data
Kplot_data <- readRDS(here::here("./data/Kplot_data_old.RDS"))

ggplot() +
  geom_errorbar(data = Kplot_data,
                aes(x = year, ymin = lower, ymax = upper),
                width = 0) +
  geom_point(data = Kplot_data,
             aes(x = year, y = globalK)) +
  geom_errorbar(data = Kt_calc,
                aes(x = year + 0.25, ymin = lower, ymax = upper),
                width = 0, colour = "blue") +
  geom_point(data = Kt_calc,
             aes(x = year + 0.25, y = globalK),
             colour = "blue")
```

When we have defined something as 'at equilibrium' how much do time steps vary from this Kt value?

```{r}
divergence <- stable_data |> 
  left_join(KtN_calc, by = c("sim", "sim_year")) |> 
  mutate(diff = pop_size - KtN,
         abs_diff = abs(diff)) |> 
  ## What % are within 30 individuals?
  summarise(in30 = sum(abs_diff <= 30),
            perc_in30 = in30/n())

divergence
```
