---
title: "dN_correlates"
output: html_document
date: '2022-10-25'
---

# Prepare workspace

Load required packages

```{r pkg}
library(ggplot2)
library(hyenaR)
library(dplyr)
library(here)
library(spaMM)
spaMM.options(nb_cores=10) ## CHECK WITH htop BEFORE USING TOO MANY
library(doSNOW)
library(DHARMa)
library(ggrepel)
library(ggtext)
```

Define which simulation type we're using

```{r params}
#Model 2 (polynomial age and random effect of year nested within clan)
#Simulations have a variety of start points to reduce initialization bias
start_year  <- 1997
end_year    <- 2022
scale       <- "year" ## For this plot, stick with annual change to make it easier to compare
```

# Extract data

Extract estimated K

```{r k_data}
if (!file.exists(here::here("./data/Kplot_data.RDS"))) {
  ## EXTRACT ESTIMATED K
  years <- start_year:end_year
  
  pb_yr <- progress::progress_bar$new(total = length(years))
  
  Kplot_data <- purrr::map_df(.x = years,
                              .f = function(year){
                                
                                pb_yr$tick()
                                
                                txt_files <- list.files(here(paste0("./STEP1_estimate_K/", year)),
                                                        pattern = ".txt", full.names = TRUE)
                                
                                allsims <- purrr::map_df(.x = txt_files,
                                                         .f = function(filepath){
                                                           
                                                           readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) %>%
                                                             dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=_)[0-9]+(?=.txt)"))
                                                           
                                                         })
                                
                                print(year)
                                
                                estK <- allsims %>% 
                                  dplyr::group_by(.data$sim) %>% 
                                  dplyr::mutate(start_pop = first(pop_size)) %>% 
                                  dplyr::slice(ceiling(dplyr::n()/2):dplyr::n()) %>% 
                                  dplyr::summarise(K = median(.data$pop_size),
                                                   start_size = first(start_pop))
                                
                                plot_data <- estK %>% 
                                  dplyr::summarise(year = year,
                                                   globalK = median(.data$K),
                                                   lower = min(.data$K),
                                                   upper = max(.data$K),
                                                   points = list(data.frame(pop_size = .data$K,
                                                                            start_pop = .data$start_size)))
                                
                                return(plot_data)
                                
                              })
  
  saveRDS(Kplot_data, here::here("./data/Kplot_data.RDS"))
} else {
  Kplot_data <- readRDS(here::here("./data/Kplot_data.RDS"))
}
```

Extract real pop data over time

```{r N_data}
### GENERATED IN STEP0_prepare_data/demographic_data.R
if (scale == "month") {
  real_pop <- readRDS(here::here("./data/Nplot_data_month.RDS"))
} else if (scale == "year") {
  real_pop <- readRDS(here::here("./data/Nplot_data_year.RDS"))
}

```

Prep data. We want to calculate different values of dK by comparing all estimates of K with all others in the next time step.

```{r}

Kplot_data_raw <- Kplot_data %>% 
  tidyr::unnest(cols = points)

```

Now that we have all the K data, we can estimate the change in K from 1 year to another. To include uncertainty, we compare all possible combos of K estimates from t and t + 1.

```{r}

#Only go to 1 year before end year, because we can't get a change in K in the last year
years <- start_year:(end_year - 1)
combos <- expand.grid(index1 = 1:12, index2 = 1:12)

dK_data <- purrr::map_df(years, .f = function(year){
  
  t_data <- Kplot_data_raw %>% 
    filter(year == {{year}})
  
  t1_data <- Kplot_data_raw %>% 
    filter(year == {{year}} + 1)
  
  dK_vector <- purrr::map_dbl(1:nrow(combos), .f = function(row){
    
    current_combo <- combos[row, ]
    
    Kt  <- t_data$pop_size[current_combo$index1]
    Kt1 <- t1_data$pop_size[current_combo$index2]
    
    Kt1/Kt
    
  })
  
  tibble(year = year, dK = dK_vector)
  
})

#For every year determine the median, lower and upper values of dK
dK_data_error <- dK_data %>% 
  group_by(year) %>% 
  summarise(value = median(dK, na.rm = TRUE),
            lower = min(dK, na.rm = TRUE),
            upper = max(dK, na.rm = TRUE),
            df = "K")

```

If we are scale of month, do the same thing for N. We pick every possible starting month from Jan - Dec (assume a 1year difference). Otherwise, we just have one value for each year.

```{r}

if (scale == "month") {
  month_combos <- 1:12
} else if (scale == "year") {
  month_combos <- 7
}

#Only go to 1 before end year, because we can't get a change in K in the last year
years <- start_year:(end_year - 1)

real_pop <- real_pop %>% 
  mutate(year = lubridate::year(date))

dN_data <- purrr::map_df(years, .f = function(year){
  
  t_data <- real_pop %>% 
    filter(year == {{year}})
  
  t1_data <- real_pop %>% 
    filter(year == {{year}} + 1)
  
  if (year == 1996) {
    
    input_combos <- month_combos[month_combos >= 5]
    
  } else {
    
    input_combos <- month_combos
    
  }
  
  dN_vector <- purrr::map_dbl(input_combos, .f = function(month){
    
    Nt  <- t_data %>% 
      filter(lubridate::month(date) == month) %>% 
      pull(pop_size)
    Nt1 <- t1_data %>% 
      filter(lubridate::month(date) == month) %>% 
      pull(pop_size)
    
    Nt1/Nt
    
  })
  
  tibble(year = year, dN = dN_vector)
  
})


#For every year determine the median, lower and upper values of dK
dN_data_error <- dN_data %>% 
  group_by(year) %>% 
  summarise(value = median(dN, na.rm = TRUE),
            lower = min(dN, na.rm = TRUE),
            upper = max(dN, na.rm = TRUE),
            df = "N")

```

```{r}

plot_data3 <- bind_rows(dK_data_error, dN_data_error) %>% 
  select(-upper, -lower) %>% 
  tidyr::pivot_wider(names_from = df, values_from = value, names_prefix = "lambda")

dK_data_errorbar <- dK_data_error %>% 
  left_join(select(dN_data_error, year, dN = value), by = "year")

dN_data_errorbar <- dN_data_error %>% 
  left_join(select(dK_data_error, year, dK = value), by = "year")

```

# Correlation test

Pearson and Spearman correlation vals

```{r}
#Pearson's
cor.test(dN_data_errorbar$value, dN_data_errorbar$dK, method = "pearson")
```

```{r}
#Spearman
cor.test(dN_data_errorbar$value, dN_data_errorbar$dK, method = "spearman")
```
# Distance between N and K

```{r}
distance_data <- Kplot_data |> 
  left_join(real_pop, by = "year") |> 
  #Distance between median K and monthly N
  mutate(diff = globalK - pop_size) |> 
  #Summary stats
  group_by(year) |> 
  summarise(min = min(diff), max = max(diff), mean = mean(diff))

distance_data
```

# Identify cases in each quadrant

### Identify cases of K growth and decline

Only consider changes >10%

```{r}
plot_data3 <- plot_data3 |> 
  mutate(Kgrowth = case_when(lambdaK >= 1.05 ~ "growth",
                             lambdaK <= 0.95 ~ "decline",
                             TRUE ~ "stable"),
         Ngrowth = case_when(lambdaN >= 1.05 ~ "growth",
                             lambdaN <= 0.95 ~ "decline",
                             TRUE ~ "stable"))

table(plot_data3$Kgrowth, plot_data3$Ngrowth)
```

```{r}
plot_data3 |> 
  arrange(Kgrowth, Ngrowth) |> 
  print(n = Inf)
```

```{r}
plot_data3 |> 
  filter(!(Kgrowth == "growth" & Ngrowth == "growth") & !(Kgrowth == "decline" & Ngrowth == "growth") & !(Kgrowth == "stable" & Ngrowth == "growth") & !year %in% c(2018, 2019)) |> 
  arrange(Kgrowth, Ngrowth) |> 
  print(n = Inf)
```

### When K grew but N didn't

```{r}
filter(plot_data3, lambdaK > 1 & lambdaN < 1)
```

### When K shrank but N grew

```{r}
filter(plot_data3, lambdaK < 1 & lambdaN > 1)
```

### Both grew

```{r}
filter(plot_data3, lambdaK > 1 & lambdaN > 1)
```

### Both decline

```{r}
filter(plot_data3, lambdaK < 1 & lambdaN < 1)
```

# PLOT: dN v dK with quadrants

Plot

```{r}

#WITHOUT YEAR LABELS

#Limit the size of the errorbar for 2019 to reach 2 (just to keep axis even)
dK_data_errorbar <- dK_data_errorbar %>% 
  mutate(upper_trunc = case_when(upper > 2 ~ 2,
                                 TRUE ~ upper))

(dN_dK_nolabel <- ggplot() +
    geom_hline(yintercept = 1, lty = 2) +
    geom_vline(xintercept = 1, lty = 2) +
    # geom_segment(aes(x = 1.05, xend = 1.05, y = 1.25, yend = 1.5),
    #              colour = "black", size = 1,
    #              arrow = arrow(length = unit(0.03, "npc"))) +
    #Add horizontal error bar
    geom_errorbarh(data = dK_data_errorbar, aes(y = dN, xmin = lower, xmax = upper)) +
    #Manually add segment showing that error for 2019 extends beyond 2
    # geom_segment(data = filter(dK_data_errorbar, year %in% c(2018, 2019)),
    #              aes(y = dN, yend = dN, x = lower, xend = upper_trunc), arrow = arrow(length = unit(0.1, "inches"))) +
    # geom_text(data = filter(dK_data_errorbar, year %in% c(2018, 2019)),
    #           aes(y = dN - 0.05, x = upper_trunc, label = signif(upper, 2)),
    #           size = 3) +
    #Add vertical error bar
    geom_errorbar(data = dN_data_errorbar, aes(x = dK, ymin = lower, ymax = upper)) +
    geom_point(data = plot_data3, aes(x = lambdaK, y = lambdaN),
               shape = 21, colour = "black", fill = "grey50") +
    geom_point(data = plot_data3 %>% filter(year %in% c(2018, 2019, 2006, 2001)), aes(x = lambdaK, y = lambdaN),
               shape = 21, colour = "black", fill = "red", size = 2) +
    #Add year text
    geom_text(data = plot_data3 %>% filter(year %in% c(2018, 2019, 2006, 2001)),
              aes(x = lambdaK + c(-0.075, 0.075, -0.075, 0.075),
                  y = lambdaN + c(0.04, 0.04, -0.04, -0.04), label = paste(year, year + 1, sep = "-")),
              force = 7, size = 2.5, max.overlaps = 14) +
    # geom_text(aes(x = c(0.35, 0.35, 1.6, 1.6, 1.15),
    #               y = c(0.5, 1.5, 0.5, 1.5, 1.375),
    #               label = c("Fig2C (end)", "Fig2C (start)", "Allee effect?", "Fig2A", "Fig2B"))) +
    scale_x_continuous(breaks = seq(0, 2, 0.25)) +
    labs(x = "\U03BB<sub>K</sub>",
         y = "\U03BB<sub>N</sub>") +
    annotate(x = 0.625, y = 0.425, label = "\U2190 Environment<br>degrading   ", geom = "richtext", label.colour = NA,
             hjust = 1, lineheight = 0, size = 3.5) +
    annotate(x = 1.375, y = 0.425, label = "Environment \U2192<br>improving  ", geom = "richtext", label.colour = NA,
             hjust = 0, lineheight = 0, size = 3.5) +
    annotate(x = -0.055, y = 0.85, label = "\U2190 Population<br>decreasing", geom = "richtext", label.colour = NA,
             hjust = 1, angle = 90, lineheight = 0, size = 3.5) +
    annotate(x = -0.055, y = 1.15, label = "Population \U2192<br>increasing", geom = "richtext", label.colour = NA,
             hjust = 0, angle = 90, lineheight = 0, size = 3.5) +
    coord_equal(clip = "off",
                ylim = c(0.6, 1.4),
                xlim = c(0.2, 1.8)) +
    theme_classic() +
    theme(axis.text = element_text(colour = "black", size = 9),
          plot.margin = margin(b = 15, l = 15, t = 15),
          axis.title.y = element_markdown(margin = margin(r = 10)),
          axis.title.x = element_markdown(margin = margin(t = 10))))

ggsave(here::here("./plots/dN_dK_plot.png"), dpi = 600,
       width = 6.75,
       height = 3.75)

```

```{r}

#WITH YEAR LABELS
library(ggrepel)

(dN_dK_label <- ggplot() +
    geom_hline(yintercept = 1, lty = 2) +
    geom_vline(xintercept = 1, lty = 2) +
    # geom_segment(aes(x = 1.05, xend = 1.05, y = 1.25, yend = 1.5),
    #              colour = "black", size = 1,
    #              arrow = arrow(length = unit(0.03, "npc"))) +
    #Add horizontal error bar
    geom_errorbarh(data = dK_data_errorbar, aes(y = dN, xmin = lower, xmax = upper)) +
    #Manually add segment showing that error for 2019 extends beyond 2
    # geom_segment(data = filter(dK_data_errorbar, year %in% c(2018, 2019)),
    #              aes(y = dN, yend = dN, x = lower, xend = upper_trunc), arrow = arrow(length = unit(0.1, "inches"))) +
    # geom_text(data = filter(dK_data_errorbar, year %in% c(2018, 2019)),
    #           aes(y = dN - 0.05, x = upper_trunc, label = signif(upper, 2)),
    #           size = 3) +
    #Add vertical error bar
    geom_errorbar(data = dN_data_errorbar, aes(x = dK, ymin = lower, ymax = upper)) +
    geom_point(data = plot_data3, aes(x = lambdaK, y = lambdaN),
               shape = 21, colour = "black", fill = "grey50") +
    geom_point(data = plot_data3 %>% filter(year %in% c(2018, 2019, 2001, 2006)), aes(x = lambdaK, y = lambdaN),
               shape = 21, colour = "black", fill = "red", size = 2) +
    #Add year text
    geom_text_repel(data = plot_data3, aes(x = lambdaK, y = lambdaN, label = year),
                    force = 7, size = 2.5, max.overlaps = 14) +
    # geom_text(aes(x = c(0.35, 0.35, 1.6, 1.6, 1.15),
    #               y = c(0.5, 1.5, 0.5, 1.5, 1.375),
    #               label = c("Fig2C (end)", "Fig2C (start)", "Allee effect?", "Fig2A", "Fig2B"))) +
    scale_x_continuous(breaks = seq(0, 2, 0.25)) +
    labs(x = "\U03BB<sub>K</sub>",
         y = "\U03BB<sub>N</sub>") +
    annotate(x = 0.625, y = 0.425, label = "\U2190 Environment<br>degrading   ", geom = "richtext", label.colour = NA,
             hjust = 1, lineheight = 0, size = 3.5) +
    annotate(x = 1.375, y = 0.425, label = "Environment \U2192<br>improving  ", geom = "richtext", label.colour = NA,
             hjust = 0, lineheight = 0, size = 3.5) +
    annotate(x = -0.055, y = 0.85, label = "\U2190 Population<br>decreasing", geom = "richtext", label.colour = NA,
             hjust = 1, angle = 90, lineheight = 0, size = 3.5) +
    annotate(x = -0.055, y = 1.15, label = "Population \U2192<br>increasing", geom = "richtext", label.colour = NA,
             hjust = 0, angle = 90, lineheight = 0, size = 3.5) +
    coord_equal(clip = "off",
                ylim = c(0.6, 1.4),
                xlim = c(0.2, 1.8)) +
    theme_classic() +
    theme(axis.text = element_text(colour = "black", size = 9),
          plot.margin = margin(b = 15, l = 15, t = 15),
          axis.title.y = element_markdown(margin = margin(r = 10)),
          axis.title.x = element_markdown(margin = margin(t = 10))))

ggsave(here::here("./plots/dN_dK_plot_labelled.png"), dpi = 600,
       width = 6.75,
       height = 3.75)

```

### Plot with K-N

As an alternative to plotting change in K and N over time we can look at effect of K-N.

```{r}

## calculate K-N for all values of K and N and take the median
years <- start_year:(end_year - 1)

real_pop <- real_pop %>% 
  mutate(year = lubridate::year(date))

KN_data <- purrr::map_df(years, .f = function(year){
  
  K_data <- Kplot_data_raw %>% 
    filter(year == {{year}})
  
  N_data <- real_pop %>% 
    filter(year == {{year}})
  
  combos <- expand.grid(Kindex = 1:nrow(K_data),
                        Nindex = 1:nrow(N_data))
  
  KN_vector <- purrr::map_dbl(1:nrow(combos), .f = function(row){
    
    K <- K_data$pop_size[combos$Kindex[row]]
    N <- N_data$pop_size[combos$Nindex[row]]
    
    N - K
    
  })
  
  tibble(year = year, diff = KN_vector)
  
})

#We can now include a median, upper and lower value
plot_data4a <- KN_data %>% 
  group_by(year) %>% 
  summarise(median = median(diff),
            lower = min(diff),
            upper = max(diff)) %>% 
  left_join(select(dN_data_error, year, lambdaN = value), by = "year") %>% 
  left_join(select(Kplot_data, year, K = globalK), by = "year") %>% 
  filter(!is.na(lambdaN))

```

Prep data

```{r}

#Update to include K-N errorbars
plot_data4b <- KN_data %>% 
  group_by(year) %>% 
  summarise(median = median(diff),
            lower = min(diff),
            upper = max(diff)) %>% 
  left_join(select(dN_data_error, year, lambdaN = value), by = "year") %>% 
  left_join(select(Kplot_data, year, K = globalK), by = "year") %>% 
  filter(!is.na(lambdaN))

dN_data_errorbar2 <- dN_data_errorbar %>% 
  left_join(select(plot_data4b, year, median), by = "year")

```

## Correlation test

Pearson and Spearman correlation vals

```{r}
#Pearson's
cor.test(plot_data4b$median, plot_data4b$lambdaN, method = "pearson")
```

```{r}
#Spearman
cor.test(plot_data4b$median, plot_data4b$lambdaN, method = "spearman")
```

Plot

```{r}

#WITHOUT YEAR LABELS
(dN_KN_nolabel <- ggplot() +
   geom_hline(yintercept = 1, lty = 2) +
   geom_vline(xintercept = 0, lty = 2) +
   geom_errorbarh(data = plot_data4b, aes(y = lambdaN, xmin = lower, xmax = upper), height = 0) +
   geom_errorbar(data = dN_data_errorbar2, aes(x = median, ymin = lower, ymax = upper), width = 0) +
   geom_point(data = plot_data4b, aes(x = median, y = lambdaN),
              shape = 21, fill = "grey50", colour = "black") + 
   geom_point(data = plot_data4b %>% filter(year %in% c(2018, 2019, 2001, 2006)), aes(x = median, y = lambdaN),
              shape = 21, colour = "black", fill = "red", size = 2) +
   #Add year text
   geom_text(data = plot_data4b %>% filter(year %in% c(2018, 2019, 2001, 2006)),
                   aes(x = median + c(50, 50, 50, 50),
                       y = lambdaN + c(-0.03, 0.03, 0.03, 0.03),
                       label = paste(year, year + 1, sep = "-")),
             size = 2.5) +
   # x = lambdaK + c(-0.075, 0.075, -0.075, 0.075),
   #                y = lambdaN + c(0.04, 0.04, -0.04, -0.04)
   labs(
     # title = "Relationship between K-N and \U03BBN",
     # subtitle = "Errorbars show range of possible values using all estimates of K\nand N in 1st of each month",
     x = "N<sub>t</sub> - K<sub>t</sub>",
     y = "\U03BB<sub>N</sub>") +
   coord_equal(ratio = 250/0.5,
               clip = "off",
               ylim = c(0.6, 1.4),
               xlim = c(-500, 500)) +
   annotate(x = -150, y = 0.325, label = "Population below<br>carrying capacity", geom = "richtext",
            label.colour = NA,
            hjust = 1, lineheight = 0, size = 3.5) +
   annotate(x = 150, y = 0.325, label = "Population above<br>carrying capacity", geom = "richtext",
            label.colour = NA,
            hjust = 0, lineheight = 0, size = 3.5) +
   annotate(x = -635, y = 0.85, label = "\U2190 Population<br>decreasing", geom = "richtext", label.colour = NA,
            hjust = 1, angle = 90, lineheight = 0, size = 3.5) +
   annotate(x = -635, y = 1.15, label = "Population \U2192<br>increasing", geom = "richtext", label.colour = NA,
            hjust = 0, angle = 90, lineheight = 0, size = 3.5) +
   theme_classic() +
   theme(axis.text = element_text(colour = "black", size = 9),
         plot.margin = margin(b = 15, l = 15, t = 15),
         axis.title.y = element_markdown(margin = margin(r = 10)),
         axis.title.x = element_markdown(margin = margin(t = 10))))

ggsave(here::here("./plots/dN_KN_plot.png"), dpi = 600,
       width = 6.75,
       height = 3.75)

```

```{r}

#WITH YEAR LABELS
(dN_KN_label <- ggplot() +
   geom_hline(yintercept = 1, lty = 2) +
   geom_vline(xintercept = 0, lty = 2) +
   geom_errorbarh(data = plot_data4b, aes(y = lambdaN, xmin = lower, xmax = upper), height = 0) +
   geom_errorbar(data = dN_data_errorbar2, aes(x = median, ymin = lower, ymax = upper), width = 0) +
   geom_point(data = plot_data4b, aes(x = median, y = lambdaN),
              shape = 21, fill = "grey50", colour = "black") + 
   geom_point(data = plot_data4b %>% filter(year %in% c(2018, 2019, 2001, 2006)), aes(x = median, y = lambdaN),
              shape = 21, colour = "black", fill = "red", size = 2) +
   #Add year text
   geom_text_repel(data = plot_data4b,
                   aes(x = median, y = lambdaN, label = year),
                   force = 7, size = 2.5, max.overlaps = 14) +
   labs(
     # title = "Relationship between K-N and \U03BBN",
     # subtitle = "Errorbars show range of possible values using all estimates of K\nand N in 1st of each month",
     x = "N - K",
     y = "\U03BB<sub>N</sub>") +
   coord_equal(ratio = 250/0.5,
               clip = "off",
               ylim = c(0.6, 1.4),
               xlim = c(-500, 500)) +
   annotate(x = -150, y = 0.325, label = "Population below<br>carrying capacity", geom = "richtext",
            label.colour = NA,
            hjust = 1, lineheight = 0, size = 3.5) +
   annotate(x = 150, y = 0.325, label = "Population above<br>carrying capacity", geom = "richtext",
            label.colour = NA,
            hjust = 0, lineheight = 0, size = 3.5) +
   annotate(x = -635, y = 0.85, label = "\U2190 Population<br>decreasing", geom = "richtext", label.colour = NA,
            hjust = 1, angle = 90, lineheight = 0, size = 3.5) +
   annotate(x = -635, y = 1.15, label = "Population \U2192<br>increasing", geom = "richtext", label.colour = NA,
            hjust = 0, angle = 90, lineheight = 0, size = 3.5) +
   theme_classic() +
   theme(axis.text = element_text(colour = "black", size = 9),
         plot.margin = margin(b = 15, l = 15, t = 15),
         axis.title.y = element_markdown(margin = margin(r = 10)),
         axis.title.x = element_markdown(margin = margin(t = 10))))

ggsave(here::here("./plots/dN_KN_plot_labelled.png"), dpi = 600,
       width = 6.75,
       height = 3.75)

```

Combine plots

```{r}
library(patchwork)
dN_dK_nolabel + dN_KN_nolabel + patchwork::plot_layout(ncol = 1, nrow = 2) + patchwork::plot_annotation(tag_levels = "a", tag_suffix = ")")  &
    theme(plot.tag.position = c(0.125, 0.975), plot.tag = element_text(size = 17))

ggsave(here::here("./plots/dN_combo_plot.png"), dpi = 600,
       width = 6.75,
       height = 7.5)
```

```{r}
library(patchwork)
dN_dK_label + dN_KN_label + patchwork::plot_layout(ncol = 1, nrow = 2) + patchwork::plot_annotation(tag_levels = "a", tag_suffix = ")")  &
    theme(plot.tag.position = c(0.125, 0.975), plot.tag = element_text(size = 17))

ggsave(here::here("./plots/dN_combo_plot_labelled.png"), dpi = 600,
       width = 6.75,
       height = 7.5)
```
