---
title: "Mechanistic_analysis"
author: "Liam"
date: '2022-09-02'
output: html_document
---

## Prepare

Load required packages

```{r pkg}
library(ggplot2)
library(dplyr)
library(here)
library(lay)
library(lubridate)
library(doSNOW)
library(patchwork)
library(spaMM)
library(DHARMa)
library(ggtext)
```

```{r}
start_year  <- 1997
end_year    <- 2022
```

Load environmental data

```{r}
## GENERATED IN STEP0_prepare_data/mechanistic_data.Rmd
mechanistic_data <- read.csv(here::here("./data/mechanistic_model_data.csv"))
```

Extract K data

```{r k_data_clan}
if (file.exists(here::here("./data/Kplot_clan_data.RDS"))) {
  Kplot_data <- readRDS(here::here("./data/Kplot_clan_data.RDS"))
} else {
  
  ## EXTRACT ESTIMATED K
  years <- start_year:end_year
  
  pb_yr <- progress::progress_bar$new(total = length(years))
  
  Kplot_data <- purrr::map_df(.x = years,
                              .f = function(year){
                                
                                pb_yr$tick()
                                
                                txt_files <- list.files(here(paste0("./STEP1_estimate_K/", year)),
                                                        pattern = ".txt", full.names = TRUE)
                                
                                allsims <- purrr::map_df(.x = txt_files,
                                                         .f = function(filepath){
                                                           
                                                           readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) %>%
                                                             dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=_)[0-9]+(?=.txt)"))
                                                           
                                                         })
                                
                                #Remove deaths, mothers, father
                                allsims_sub <- allsims %>% 
                                  select(-contains("dead"), -contains("father"), -contains("mother")) %>% 
                                  tidyr::pivot_longer(cols = A_cubfem:T_dispmale) %>% 
                                  tidyr::separate(col = name, sep = "_", into = c("clan", "group")) %>% 
                                  group_by(clan, date, sim) %>% 
                                  summarise(pop_size = first(pop_size),
                                            clan_size = sum(value), .groups = "drop") %>% 
                                  tidyr::pivot_wider(names_from = clan, values_from = clan_size)
                                
                                estK <- allsims_sub %>% 
                                  dplyr::group_by(.data$sim) %>% 
                                  dplyr::mutate(start_pop = first(pop_size)) %>%
                                  dplyr::slice(ceiling(dplyr::n()/2):dplyr::n()) %>% 
                                  dplyr::summarise(across(.cols = pop_size:T, .fns = function(N) replace(median(N, na.rm = TRUE),
                                                                                                         is.na(median(N, na.rm = TRUE)), 0)),
                                                   start_size = first(start_pop),
                                                   year = year)
                                
                                return(estK)
                                
                              })
  
  saveRDS(Kplot_data, file = here("./data/Kplot_clan_data.RDS"))
}

```

```{r}
clanK <- Kplot_data %>% 
  tidyr::pivot_longer(cols = pop_size:T, names_to = "clan") %>% 
  group_by(year, clan) %>% 
  dplyr::summarise(globalK = median(.data$value),
                   lower = min(.data$value),
                   upper = max(.data$value), .groups = "drop") %>% 
  filter(clan != "pop_size") |> 
  ## Force values to integer for analyses w/ Poisson or Negbin
  mutate(across(globalK:upper, as.integer))
```

Combined environmental data with K estimates

```{r}
mod_data_alldisease_consv <- clanK |> 
  left_join(mechanistic_data, by = c("year", "clan")) |> 
  filter(!is.na(avgprey))
```

Plot data to investigate

```{r}
ggplot() +
  geom_point(data = mod_data_alldisease_consv, aes(x = avgprey, y = globalK)) +
  geom_smooth(data = mod_data_alldisease_consv, aes(x = avgprey, y = globalK), method = "lm", se = FALSE) +
  labs(title = "Prey category") +
  theme_classic()
```

Join with other data (determine avg density across all clans in a year)

```{r}
ggplot() +
  geom_point(data = mod_data_alldisease_consv, aes(x = lion_density, y = globalK)) +
  geom_smooth(data = mod_data_alldisease_consv, aes(x = lion_density, y = globalK), method = "lm", se = FALSE) +
  theme_classic()
```
```{r}
ggplot() +
  geom_point(data = mod_data_alldisease_consv, aes(x = total_disease_percap, y = globalK)) +
  geom_smooth(data = mod_data_alldisease_consv, aes(x = total_disease_percap, y = globalK), method = "lm", se = FALSE) +
  theme_classic()
```

### Model (categorical prey)

#### Negbin

Some issues with temporal auto-correlation. Fit with AR1.

AR1 mod

```{r}
mod2 <- fitme(globalK ~ lion_density_scale + avgprey_scale + total_disease_percap_scale + roaduse + grazing + clan + AR1(1|year),
              data = mod_data_alldisease_consv,
              family = spaMM::negbin2(link = "log"))
```

Make sure this didn't mess up any of the other assumptions.

```{r}
simresid_mod2 <- simulateResiduals(mod2, n = 1000, seed = 124)

testUniformity(simresid_mod2)
```

```{r}
testQuantiles(simresid_mod2)
```

```{r}
testQuantiles(simresid_mod2, predictor = mod_data_alldisease_consv$avgprey_scale)
```

Looks like a non-linear effect of prey might be more appropriate.

```{r}
testQuantiles(simresid_mod2, predictor = mod_data_alldisease_consv$lion_density_scale)
```

```{r}
testQuantiles(simresid_mod2, predictor = mod_data_alldisease_consv$total_disease_percap_scale)
```

```{r}
testDispersion(simresid_mod2)
```

#### Gaussian

Try Gaussian. This requires us to remove year random intercept to get convergence, although in mod2 it explains very little variance so not a major issue.

```{r}
mod3 <- fitme(globalK ~ lion_density_scale + avgprey_scale + total_disease_percap_scale + roaduse + grazing + clan + AR1(1|year),
              data = mod_data_alldisease_consv,
              family = gaussian(link = "identity"))
```

Using Gaussian identical. This would be easier to describe (and comparable to models of temporal trends).

```{r}
AIC(mod2, verbose = TRUE)
AIC(mod3, verbose = TRUE)
```

```{r}
simresid_mod3 <- simulateResiduals(mod3, n = 1000, seed = 124)

testUniformity(simresid_mod3)
```

```{r}
testQuantiles(simresid_mod3)
```

```{r}
testQuantiles(simresid_mod3, predictor = mod_data_alldisease_consv$avgprey_scale)
```

Looks like a non-linear effect of prey might be more appropriate.

```{r}
testQuantiles(simresid_mod3, predictor = mod_data_alldisease_consv$lion_density_scale)
```

```{r}
testQuantiles(simresid_mod3, predictor = mod_data_alldisease_consv$total_disease_percap_scale)
```

```{r}
testDispersion(simresid_mod3)
```

#### Significance

##### Gaussian

Compare to null (significant!)

```{r}
## NOTE: Need to specify intercept for this to work otherwise LRT fails
null_mod <- fitme(globalK ~ 1 + AR1(1|year),
                  data = mod_data_alldisease_consv,
                  family = gaussian(link = "identity"))
## USE ASYMPTOTIC LRT P-VAL RATHER THAN BOOTSTRAP.
## THIS ALLOWS US TO BE CONSISTENT IN ALL RESULTS
LRT(mod3, null_mod)
# global_LRT_mod3 <- LRT(mod3, null_mod, boot.repl = 999, nb_cores = 10, seed = 124)
# data.frame(basic = global_LRT_mod3$basicLRT$p_value, bartlett = global_LRT_mod3$BartBootLRT$p_value, bootstrap = global_LRT_mod3$rawBootLRT$p_value)
```

```{r}
summary(mod3)
```

```{r}
nolion <- fitme(globalK ~ 1 + avgprey_scale + total_disease_percap_scale + roaduse + grazing + clan + AR1(1|year),
                data = mod_data_alldisease_consv,
                family = gaussian(link = "identity"))
noprey <- fitme(globalK ~ lion_density_scale + total_disease_percap_scale + roaduse + grazing + clan + AR1(1|year),
                data = mod_data_alldisease_consv,
                family = gaussian(link = "identity"))
nodisease <- fitme(globalK ~ lion_density_scale + avgprey_scale + roaduse + grazing + clan + AR1(1|year),
                   data = mod_data_alldisease_consv,
                   family = gaussian(link = "identity"))
noroaduse <- fitme(globalK ~ lion_density_scale + avgprey_scale + total_disease_percap_scale + grazing + clan + AR1(1|year),
                   data = mod_data_alldisease_consv,
                   family = gaussian(link = "identity"))
nograzingban <- fitme(globalK ~ lion_density_scale + avgprey_scale + roaduse + total_disease_percap_scale + clan + AR1(1|year),
                      data = mod_data_alldisease_consv,
                      family = gaussian(link = "identity"))
```

```{r}
## USE ASYMPTOTIC LRT P-VAL RATHER THAN BOOTSTRAP.
## THIS ALLOWS US TO BE CONSISTENT IN ALL RESULTS
LRT(mod3, nolion)
# lionLRT_mod3 <- LRT(mod3, nolion, boot.repl = 999, nb_cores = 10, seed = 124)
# data.frame(basic = lionLRT_mod3$basicLRT$p_value, bartlett = lionLRT_mod3$BartBootLRT$p_value, bootstrap = lionLRT_mod3$rawBootLRT$p_value)
```

```{r}
lionCI_mod3 <- confint(mod3, parm = "lion_density_scale", verbose = FALSE, boot_args = list(nsim = 999, nb_cores = 10, seed = 124))
lionCI_mod3
```

```{r}
## USE ASYMPTOTIC LRT P-VAL RATHER THAN BOOTSTRAP.
## THIS ALLOWS US TO BE CONSISTENT IN ALL RESULTS
LRT(mod3, noprey)
# preyLRT_mod3<- LRT(mod3, noprey, boot.repl = 999, nb_cores = 10, seed = 124)
# data.frame(basic = preyLRT_mod3$basicLRT$p_value, bartlett = preyLRT_mod3$BartBootLRT$p_value, bootstrap = preyLRT_mod3$rawBootLRT$p_value)
```

```{r}
preyCI_mod3 <- confint(mod3, parm = "avgprey_scale", verbose = FALSE, boot_args = list(nsim = 999, nb_cores = 10, seed = 124))
preyCI_mod3
```

```{r}
## USE ASYMPTOTIC LRT P-VAL RATHER THAN BOOTSTRAP.
## THIS ALLOWS US TO BE CONSISTENT IN ALL RESULTS
LRT(mod3, nodisease)
# diseaseLRT_mod3 <- LRT(mod3, nodisease, boot.repl = 999, nb_cores = 10, seed = 124)
# data.frame(basic = diseaseLRT_mod3$basicLRT$p_value, bartlett = diseaseLRT_mod3$BartBootLRT$p_value, bootstrap = diseaseLRT_mod3$rawBootLRT$p_value)
```

```{r}
diseaseCI_mod3  <- confint(mod3, parm = "total_disease_percap_scale", verbose = FALSE, boot_args = list(nsim = 999, nb_cores = 10, seed = 124))
diseaseCI_mod3 
```

```{r}
## USE ASYMPTOTIC LRT P-VAL RATHER THAN BOOTSTRAP.
## THIS ALLOWS US TO BE CONSISTENT IN ALL RESULTS
LRT(mod3, noroaduse)
# roaduseLRT_mod3 <- LRT(mod3, noroaduse, boot.repl = 999, nb_cores = 10, seed = 124)
# data.frame(basic = roaduseLRT_mod3$basicLRT$p_value, bartlett = roaduseLRT_mod3$BartBootLRT$p_value, bootstrap = roaduseLRT_mod3$rawBootLRT$p_value)
```

```{r}
roaduseCI_mod3 <- confint(mod3, parm = "roaduseinactive", verbose = FALSE, boot_args = list(nsim = 999, nb_cores = 10, seed = 124))
roaduseCI_mod3
```

```{r}
## USE ASYMPTOTIC LRT P-VAL RATHER THAN BOOTSTRAP.
## THIS ALLOWS US TO BE CONSISTENT IN ALL RESULTS
LRT(mod3, nograzingban)
# grazingbanLRT <- LRT(mod3, nograzingban, boot.repl = 999, nb_cores = 10, seed = 124)
# data.frame(basic = grazingbanLRT$basicLRT$p_value, bartlett = grazingbanLRT$BartBootLRT$p_value, bootstrap = grazingbanLRT$rawBootLRT$p_value)
```

```{r}
grazingbanCI <- confint(mod3, parm = "grazingpresent", verbose = FALSE, boot_args = list(nsim = 999, nb_cores = 10, seed = 124))
grazingbanCI
```
### Plots

#### Conditional predictions for disease

```{r}

plot_data_cond <- mod_data_alldisease_consv |> 
  select(lion_density_scale, avgprey_scale, roaduse, grazing, clan, year) |> 
  mutate(total_disease_percap_scale = list(seq(min(mod_data_alldisease_consv$total_disease_percap_scale),
                                               max(mod_data_alldisease_consv$total_disease_percap_scale),
                                               length.out = 50))) |> 
  tidyr::unnest(total_disease_percap_scale)

plot_data_cond$pred <- as.numeric(predict(mod3, newdata = as_tibble(plot_data_cond), type = "response"))

plot_data_cond <- plot_data_cond |> 
  ## Unscale values
  mutate(total_disease_percap = total_disease_percap_scale*sd(mod_data_alldisease_consv$total_disease_percap) + mean(mod_data_alldisease_consv$total_disease_percap)) |> 
  group_by(total_disease_percap) |> 
  summarise(mean_Ktc = mean(pred),
            SE_Ktc = sd(pred)/sqrt(n()),
            lower = mean_Ktc - (qnorm(0.975)*SE_Ktc),
            upper = mean_Ktc + (qnorm(0.975)*SE_Ktc))

plot_disease_cond <- ggplot() +
  geom_ribbon(data = plot_data_cond, aes(x = total_disease_percap, ymin = lower, ymax = upper),
              fill = "grey75", alpha = 0.6) +
  geom_line(data = plot_data_cond, aes(x = total_disease_percap, y = mean_Ktc)) +
  geom_point(data = mod_data_alldisease_consv, aes(x = total_disease_percap, y = globalK),
             alpha = 0.5, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 2, shape = 21, fill = "grey10", colour = "white") +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  labs(x = "Proportion of the clan observed\nwith clinical signs of infection",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black", size = 12),
        axis.title = element_markdown(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

```

#### Marginal predictions for disease

```{r}

plot_data_marginal <- data.frame(lion_density_scale = mean(mod_data_alldisease_consv$lion_density_scale),
                                 total_disease_percap_scale = seq(min(mod_data_alldisease_consv$total_disease_percap_scale),
                                                                  max(mod_data_alldisease_consv$total_disease_percap_scale),
                                                                  length.out = 50),
                                 roaduse = "active",
                                 grazing = "abscent",
                                 clan = "L",
                                 avgprey_scale = mean(mod_data_alldisease_consv$avgprey_scale),
                                 year = "1998")

preds <- predict(mod3, newdata = as_tibble(plot_data_marginal), type = "response", re.form = NA, intervals = "predVar")
plot_data_marginal$pred <- as.numeric(preds)
plot_data_marginal <- plot_data_marginal |> bind_cols(attr(preds, "interval"))

plot_data_marginal <- plot_data_marginal |>
  ## Unscale values
  mutate(total_disease_percap = total_disease_percap_scale*sd(mod_data_alldisease_consv$total_disease_percap) + mean(mod_data_alldisease_consv$total_disease_percap))

plot_disease_marg <- ggplot() +
  geom_ribbon(data = plot_data_marginal, aes(x = total_disease_percap, ymin = predVar_0.025, ymax = predVar_0.975),
              fill = "grey75", alpha = 0.6) +
  geom_line(data = plot_data_marginal, aes(x = total_disease_percap, y = pred)) +
  geom_point(data = mod_data_alldisease_consv, aes(x = total_disease_percap, y = globalK),
             alpha = 0.75, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 2, shape = 21, fill = "grey10", colour = "white") +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  labs(x = "Proportion of the clan observed\nwith clinical signs of infection",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black", size = 12),
        axis.title = element_text(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

```

#### Conditional predictions for prey

```{r}

plot_data_cond <- mod_data_alldisease_consv |> 
  select(lion_density_scale, total_disease_percap_scale, roaduse, grazing, clan, year) |> 
  mutate(avgprey_scale = list(seq(min(mod_data_alldisease_consv$avgprey_scale),
                                  max(mod_data_alldisease_consv$avgprey_scale),
                                  length.out = 50))) |> 
  tidyr::unnest(avgprey_scale)

plot_data_cond$pred <- as.numeric(predict(mod3, newdata = as_tibble(plot_data_cond), type = "response"))

plot_data_cond <- plot_data_cond |>
  ## Unscale values
  mutate(avgprey = avgprey_scale*sd(mod_data_alldisease_consv$avgprey) + mean(mod_data_alldisease_consv$avgprey)) |> 
  group_by(avgprey) |> 
  summarise(mean_Ktc = mean(pred),
            SE_Ktc = sd(pred)/sqrt(n()),
            lower = mean_Ktc - (qnorm(0.975)*SE_Ktc),
            upper = mean_Ktc + (qnorm(0.975)*SE_Ktc))

plot_avgprey_cond <- ggplot() +
  geom_ribbon(data = plot_data_cond, aes(x = avgprey, ymin = lower, ymax = upper),
              fill = "grey75", alpha = 0.6) +
  geom_line(data = plot_data_cond, aes(x = avgprey, y = mean_Ktc)) +
  geom_point(data = mod_data_alldisease_consv, aes(x = avgprey, y = globalK),
             alpha = 0.75, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 2, shape = 21, fill = "grey10", colour = "white") +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  labs(x = "Average prey abundance ranking",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black", size = 12),
        axis.title = element_text(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

```

#### Marginal predictions for prey

```{r}

plot_data_marginal <- data.frame(lion_density_scale = mean(mod_data_alldisease_consv$lion_density_scale),
                                 total_disease_percap_scale = mean(mod_data_alldisease_consv$total_disease_percap_scale),
                                 roaduse = "active",
                                 grazing = "abscent",
                                 clan = "L",
                                 avgprey_scale = seq(min(mod_data_alldisease_consv$avgprey_scale),
                                                     max(mod_data_alldisease_consv$avgprey_scale),
                                                     length.out = 50),
                                 year = "1998")

preds <- predict(mod3, newdata = as_tibble(plot_data_marginal), type = "response", re.form = NA, intervals = "predVar")
plot_data_marginal$pred <- as.numeric(preds)
plot_data_marginal <- plot_data_marginal |> bind_cols(attr(preds, "interval"))

plot_data_marginal <- plot_data_marginal |>
  ## Unscale values
  mutate(avgprey = avgprey_scale*sd(mod_data_alldisease_consv$avgprey) + mean(mod_data_alldisease_consv$avgprey))

plot_avgprey_marg <- ggplot() +
  geom_ribbon(data = plot_data_marginal, aes(x = avgprey, ymin = predVar_0.025, ymax = predVar_0.975),
              fill = "grey75", alpha = 0.6) +
  geom_line(data = plot_data_marginal, aes(x = avgprey, y = pred)) +
  geom_point(data = mod_data_alldisease_consv, aes(x = avgprey, y = globalK),
             alpha = 0.75, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 2, shape = 21, fill = "grey10", colour = "white") +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  labs(x = "Average prey abundance ranking",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black", size = 12),
        axis.title = element_text(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

```

#### Marginal predictions for lion

```{r}

plot_data_marginal <- data.frame(lion_density_scale = seq(min(mod_data_alldisease_consv$lion_density_scale),
                                                          max(mod_data_alldisease_consv$lion_density_scale),
                                                          length.out = 50),
                                 total_disease_percap_scale = mean(mod_data_alldisease_consv$total_disease_percap_scale),
                                 roaduse = "active",
                                 grazing = "abscent",
                                 clan = "L",
                                 avgprey_scale = mean(mod_data_alldisease_consv$avgprey_scale),
                                 year = "1998")

preds <- predict(mod3, newdata = as_tibble(plot_data_marginal), type = "response", re.form = NA, intervals = "predVar")
plot_data_marginal$pred <- as.numeric(preds)
plot_data_marginal <- plot_data_marginal |> bind_cols(attr(preds, "interval"))

plot_data_marginal <- plot_data_marginal |>
  ## Unscale values
  mutate(lion_density = lion_density_scale*sd(mod_data_alldisease_consv$lion_density) + mean(mod_data_alldisease_consv$lion_density))

plot_lion_marg <- ggplot() +
  geom_ribbon(data = plot_data_marginal, aes(x = lion_density, ymin = predVar_0.025, ymax = predVar_0.975),
              fill = "grey75", alpha = 0.6) +
  geom_line(data = plot_data_marginal, aes(x = lion_density, y = pred)) +
  geom_point(data = mod_data_alldisease_consv, aes(x = lion_density, y = globalK),
             alpha = 0.75, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 2, shape = 21, fill = "grey10", colour = "white") +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  labs(x = "Lion density (number sighted/km<sup>2</sup>)",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black", size = 12),
        axis.title.x = element_markdown(colour = "black", size = 15),
        axis.title.y = element_text(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

plot_lion_marg

```

### Final plot

```{r}
plot_avgprey_marg + plot_disease_marg + plot_lion_marg + patchwork::plot_layout(nrow = 1) +
  patchwork::plot_annotation(tag_levels = "a", tag_suffix = ")")  &
  theme(plot.tag.position = c(0.175, 0.975), plot.tag = element_text(size = 17))

ggsave(filename = here::here("./plots/mechanistic_results.png"), dpi = 600,
       width = 15, height = 5)
```

### Supplementary fig

#### Marginal predictions for road use

```{r}

plot_data_marginal <- data.frame(lion_density_scale = mean(mod_data_alldisease_consv$lion_density_scale),
                                 total_disease_percap_scale = mean(mod_data_alldisease_consv$total_disease_percap_scale),
                                 roaduse = c("active", "inactive"),
                                 grazing = "abscent",
                                 clan = "L",
                                 avgprey_scale = mean(mod_data_alldisease_consv$avgprey_scale),
                                 year = "1998")

preds <- predict(mod3, newdata = as_tibble(plot_data_marginal), type = "response", re.form = NA, intervals = "predVar")
plot_data_marginal$pred <- as.numeric(preds)
plot_data_marginal <- plot_data_marginal |> bind_cols(attr(preds, "interval"))

plot_road_marg <- ggplot() +
  geom_point(data = mod_data_alldisease_consv, aes(x = roaduse, y = globalK),
             alpha = 0.75, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 1.5, shape = 21, fill = "grey10", colour = "white") +
  geom_violin(data = mod_data_alldisease_consv, aes(x = roaduse, y = globalK),
              alpha = 0.5, fill = "grey50") +
  geom_errorbar(data = plot_data_marginal, aes(x = roaduse, ymin = predVar_0.025, ymax = predVar_0.975), width = 0.1) +
  geom_point(data = plot_data_marginal, aes(x = roaduse, y = pred), size = 3) +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  scale_x_discrete(labels = c("Road use restrictions \n active", "Road use restrictions \n inactive")) +
  labs(x = "",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text.y = element_text(colour = "black", size = 12),
        axis.text.x = element_text(colour = "black", size = 13),
        axis.title = element_text(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

plot_road_marg

```

#### Marginal predictions for grazing

```{r}

plot_data_marginal <- data.frame(lion_density_scale = mean(mod_data_alldisease_consv$lion_density_scale),
                                 total_disease_percap_scale = mean(mod_data_alldisease_consv$total_disease_percap_scale),
                                 roaduse = "active",
                                 grazing = c("abscent", "present"),
                                 clan = "L",
                                 avgprey_scale = mean(mod_data_alldisease_consv$avgprey_scale),
                                 year = "1998")

preds <- predict(mod3, newdata = as_tibble(plot_data_marginal), type = "response", re.form = NA, intervals = "predVar")
plot_data_marginal$pred <- as.numeric(preds)
plot_data_marginal <- plot_data_marginal |> bind_cols(attr(preds, "interval"))

plot_grazing_marg <- ggplot() +
  geom_point(data = mod_data_alldisease_consv, aes(x = grazing, y = globalK),
             alpha = 0.75, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 1.5, shape = 21, fill = "grey10", colour = "white") +
  geom_violin(data = mod_data_alldisease_consv, aes(x = grazing, y = globalK),
              alpha = 0.5, fill = "grey50") +
  geom_errorbar(data = plot_data_marginal, aes(x = grazing, ymin = predVar_0.025, ymax = predVar_0.975), width = 0.1) +
  geom_point(data = plot_data_marginal, aes(x = grazing, y = pred), size = 3) +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  scale_x_discrete(labels = c("Grazing restrictions \n active", "Grazing restrictions \n inactive")) +
  labs(x = "",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text.y = element_text(colour = "black", size = 12),
        axis.text.x = element_text(colour = "black", size = 13),
        axis.title = element_text(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

plot_grazing_marg

```

#### Save output

```{r}
plot_avgprey_marg + plot_disease_marg + plot_lion_marg + plot_road_marg + plot_grazing_marg +
  patchwork::plot_layout(nrow = 2, ncol = 3) + patchwork::plot_annotation(tag_levels = "a", tag_suffix = ")") &
  theme(plot.tag.position = c(0.175, 0.975), plot.tag = element_text(size = 20))

ggsave(filename = here::here("./plots/supp_mechanistic_results.png"), dpi = 600,
       width = 15, height = 10)
```

### Partial dependence effects

```{r}

plot_data_pdep <- pdep_effects(mod3, focal_var = "lion_density_scale", length.out = 200) |>
  ## Unscale values
  mutate(lion_density = focal_var*sd(mod_data_alldisease_consv$lion_density) + mean(mod_data_alldisease_consv$lion_density))

plot_lion_pdep <- ggplot() +
  geom_ribbon(data = plot_data_pdep, aes(x = lion_density, ymin = low, ymax = up),
              fill = "grey75", alpha = 0.6) +
  geom_line(data = plot_data_pdep, aes(x = lion_density, y = pointp)) +
  geom_point(data = mod_data_alldisease_consv, aes(x = lion_density, y = globalK),
             alpha = 0.75, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 2, shape = 21, fill = "grey10", colour = "white") +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  labs(x = "Lion density (number sighted/km<sup>2</sup>)",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black", size = 12),
        axis.title.x = element_markdown(colour = "black", size = 15),
        axis.title.y = element_text(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

plot_lion_pdep

```

```{r}

plot_data_pdep <- pdep_effects(mod3, focal_var = "total_disease_percap_scale", length.out = 200) |>
  ## Unscale values
  mutate(total_disease_percap = focal_var*sd(mod_data_alldisease_consv$total_disease_percap) + mean(mod_data_alldisease_consv$total_disease_percap))

plot_disease_pdep <- ggplot() +
  geom_ribbon(data = plot_data_pdep, aes(x = total_disease_percap, ymin = low, ymax = up),
              fill = "grey75", alpha = 0.6) +
  geom_line(data = plot_data_pdep, aes(x = total_disease_percap, y = pointp)) +
  geom_point(data = mod_data_alldisease_consv, aes(x = total_disease_percap, y = globalK),
             alpha = 0.75, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 2, shape = 21, fill = "grey10", colour = "white") +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  labs(x = "Proportion of the clan observed\nwith clinical signs of infection",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black", size = 12),
        axis.title = element_text(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

plot_disease_pdep

```

```{r}

plot_data_pdep <- pdep_effects(mod3, focal_var = "avgprey_scale", length.out = 200) |>
  ## Unscale values
  mutate(avgprey = focal_var*sd(mod_data_alldisease_consv$avgprey) + mean(mod_data_alldisease_consv$avgprey))

plot_prey_pdep <- ggplot() +
  geom_ribbon(data = plot_data_pdep, aes(x = avgprey, ymin = low, ymax = up),
              fill = "grey75", alpha = 0.6) +
  geom_line(data = plot_data_pdep, aes(x = avgprey, y = pointp)) +
  geom_point(data = mod_data_alldisease_consv, aes(x = avgprey, y = globalK),
             alpha = 0.75, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 2, shape = 21, fill = "grey10", colour = "white") +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  labs(x = "Average prey abundance ranking",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black", size = 12),
        axis.title = element_text(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

plot_prey_pdep

```

```{r}

plot_data_pdep <- pdep_effects(mod3, focal_var = "roaduse")

plot_road_pdep <- ggplot() +
  geom_point(data = mod_data_alldisease_consv, aes(x = roaduse, y = globalK),
             alpha = 0.75, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 1.5, shape = 21, fill = "grey10", colour = "white") +
  geom_violin(data = mod_data_alldisease_consv, aes(x = roaduse, y = globalK),
              alpha = 0.5, fill = "grey50") +
  geom_errorbar(data = plot_data_pdep, aes(x = focal_var, ymin = low, ymax = up), width = 0.1) +
  geom_point(data = plot_data_pdep, aes(x = focal_var, y = pointp), size = 3) +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  scale_x_discrete(labels = c("Road use restrictions \n active", "Road use restrictions \n inactive")) +
  labs(x = "",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text.y = element_text(colour = "black", size = 12),
        axis.text.x = element_text(colour = "black", size = 13),
        axis.title = element_text(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

plot_road_pdep

```

```{r}

plot_data_pdep <- pdep_effects(mod3, focal_var = "grazing")

plot_grazing_pdep <- ggplot() +
  geom_point(data = mod_data_alldisease_consv, aes(x = grazing, y = globalK),
             alpha = 0.75, position = position_jitter(width = 0.002, height = 0, seed = 124),
             size = 1.5, shape = 21, fill = "grey10", colour = "white") +
  geom_violin(data = mod_data_alldisease_consv, aes(x = grazing, y = globalK),
              alpha = 0.5, fill = "grey50") +
  geom_errorbar(data = plot_data_pdep, aes(x = focal_var, ymin = low, ymax = up), width = 0.1) +
  geom_point(data = plot_data_pdep, aes(x = focal_var, y = pointp), size = 3) +
  scale_y_continuous(limits = c(-5, 175),
                     breaks = seq(0, 175, 25), expand = c(0, 0)) +
  scale_x_discrete(labels = c("Grazing restrictions \n active", "Grazing restrictions \n inactive")) +
  labs(x = "",
       y = "Clan carrying capacity") +
  theme_classic() +
  theme(axis.text.y = element_text(colour = "black", size = 12),
        axis.text.x = element_text(colour = "black", size = 13),
        axis.title = element_text(colour = "black", size = 15),
        legend.position = c(0.425, 0.4),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.text = element_text(size = 8))

plot_grazing_pdep

```

```{r}
plot_prey_pdep + plot_disease_pdep + plot_lion_pdep + patchwork::plot_layout(nrow = 1) +
  patchwork::plot_annotation(tag_levels = "a", tag_suffix = ")")  &
  theme(plot.tag.position = c(0.175, 0.975), plot.tag = element_text(size = 17))

ggsave(filename = here::here("./plots/mechanistic_results_pdep.png"), dpi = 600,
       width = 15, height = 5)
```

```{r}
plot_prey_pdep + plot_disease_pdep + plot_lion_pdep + plot_road_pdep + plot_grazing_pdep +
  patchwork::plot_layout(nrow = 2, ncol = 3) + patchwork::plot_annotation(tag_levels = "a", tag_suffix = ")") &
  theme(plot.tag.position = c(0.175, 0.975), plot.tag = element_text(size = 20))

ggsave(filename = here::here("./plots/supp_mechanistic_results_pdep.png"), dpi = 600,
       width = 15, height = 10)
```
