---
title: "response_to_reviewer"
format: html
---

All these plots are create in response to reviewer comments. In long term, could be worth separating them into individual sections.

## Prepare workspace

```{r}
library(ggplot2)
library(dplyr)
```

## PLOT 1: Clans

Many comments from reviewers focus on clan numbers. We need to show how clan size varies over time, how clan size and trends in clan size differ between clans.

```{r}
### GENERATED IN STEP0_prepare_data/demographic_data.R
plot_data <- readRDS(here::here("./data/NClanplot_data_separate_year.RDS")) |> 
  mutate(pop = lay::lay(pick(young:ad_fem), sum),
         to = date + lubridate::years(1))
```

General stats:

**Max and min**

```{r}
## Max & min clan size
## What's up with Triangle in 2022?! Remove this for now
plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  summarise(across(young:pop, max, .names = "{.col}_max"),
            across(young:pop, min, .names = "{.col}_min")) 
```

```{r}
plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  filter(pop == min(pop))
```


**Difference in clan size**

```{r}
## Range clan size
## What's up with Triangle in 2022?! Remove this for now
plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  mutate(year = lubridate::year(date)) |> 
  group_by(year) |> 
  summarise(across(young:pop, .fns = \(x) abs(diff(range(x))), .names = "{.col}")) |> 
  filter(pop == max(pop))
```

```{r}
plot_data |> 
  filter(lubridate::year(date) == 2017)
```

Correlation between clans

```{r}
corr_data <- plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  select(date, clan, pop) |> 
  tidyr::pivot_wider(names_from = clan, values_from = pop)

library(corrplot)
corrplot(cor(corr_data |> select(-date)), method = "number", type = "lower", diag = FALSE, bg = "grey95")
```

Separate this into period before and after 2012

```{r}
corrplot(cor(corr_data |> filter(lubridate::year(date) < 2012) |> select(-date)), method = "number", type = "lower", diag = FALSE, bg = "grey95")
```

```{r}
corrplot(cor(corr_data |> filter(lubridate::year(date) >= 2012) |> select(-date)), method = "number", type = "lower", diag = FALSE, bg = "grey95")
```

Plot trends in total pop. Remember, there are totals in a year so they should be lines, not points.

```{r}
plot_data_lines <- plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  select(date, clan, pop, to) |> 
  tidyr::pivot_longer(cols = c(date, to))

end_vals <- plot_data %>%
  filter(lubridate::year(date) != 2022) |> 
    group_by(clan) %>%
    slice(n()) |> 
  ungroup()

ggplot() +
      geom_line(data = plot_data_lines, aes(x = value, y = pop, colour = clan, group = clan)) +
      ## X TICKS
      annotate(geom = "segment",
               x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
               xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
               y = -2, yend = 0,
               lineend = "round", linejoin = "round") +
      annotate(geom = "segment",
               x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
               xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
               y = -4, yend = 0,
               lineend = "round", linejoin = "round") +
      ## Y TICKS
      annotate(geom = "segment",
               x = as.Date("1995-01-01"),
               xend = as.Date("1995-01-01") - 75,
               y = seq(0, 150, 25), yend = seq(0, 150, 25),
               lineend = "round", linejoin = "round") +
      ## LABELS
      geom_text(aes(x = as.Date("2023-06-01"),
                    y = end_vals$pop + c(-0.05, 0.06), colour = end_vals$clan),
                label = end_vals$clan, size = 3,
                hjust = 0.5, lineheight = 0.75) +
      # scale_colour_manual(values = c("red", "grey10")) +
      scale_x_date(breaks = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 years"),
                   date_labels = "%Y") +
      scale_y_continuous(breaks = seq(0, 150, 25),
                         name = "Number of individuals") +
      coord_cartesian(expand = FALSE, clip = "off",
                      ylim = c(0, 150),
                      xlim = c(as.Date("1995-01-01"), as.Date("2025-01-01"))) +
      theme_classic() +
      theme(legend.position = "none",
            axis.title.x = element_blank(),
            axis.text.x = element_text(colour = "black",
                                       margin = margin(t = 10), size = 12),
            axis.ticks = element_blank(),
            axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
            axis.title.y = element_text(colour = "black", size = 17, margin = margin(r = 12)),
            plot.margin = margin(r = 30, t = 10, b = 10))
```

```{r}
plot_data_bars <- plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  select(date, clan, pop, to) |> 
  mutate(year = lubridate::year(date))

end_vals <- plot_data %>%
  filter(lubridate::year(date) != 2022) |> 
    group_by(clan) %>%
    slice(n()) |> 
  ungroup()

ggplot(data = plot_data_bars) +
    geom_col(aes(x = date, y = pop, fill = clan),
             colour = "black", linewidth = 0.25) +
    ## X TICKS
    annotate(geom = "segment",
             x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
             xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
             y = -10, yend = 0,
             lineend = "round", linejoin = "round") +
    annotate(geom = "segment",
             x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
             xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
             y = -20, yend = 0,
             lineend = "round", linejoin = "round") +
    ## Y TICKS
    annotate(geom = "segment",
             x = as.Date("1995-01-01"),
             xend = as.Date("1995-01-01") - 75,
             y = seq(0, 600, 100), yend = seq(0, 600, 100),
             lineend = "round", linejoin = "round") +
    ## LABEL TEXT
    # annotate(geom = "segment",
    #          x = end_vals$date[1] + 225,
    #          xend = end_vals$date[1] + 225,
    #          y = 5, yend = end_vals$pop[2] - 5,
    #          lineend = "round", linejoin = "round", linewidth = 0.75) +
    # annotate(geom = "segment",
    #          x = end_vals$date[1] + 225,
    #          xend = end_vals$date[1] + 225,
    #          y = end_vals$pop[2] + 5, yend = end_vals$pop[2] + end_vals$pop[1] - 5,
    #          lineend = "round", linejoin = "round", linewidth = 0.75) +
    # scale_fill_manual(values = rev(c("grey90", "grey55", "grey20"))) +
    # scale_linewidth_discrete(range = c(0, 0.75)) +
    scale_x_date(breaks = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 years"),
                 date_labels = "%Y") +
    scale_y_continuous(breaks = seq(0, 600, 100),
                       name = "Number of individuals") +
    coord_cartesian(expand = FALSE, clip = "off",
                    ylim = c(0, 600),
                    xlim = c(as.Date("1995-01-01"), as.Date("2025-01-01"))) +
    theme_classic() +
    theme(legend.position = "right",
          axis.title.x = element_blank(),
          axis.text.x = element_text(colour = "black",
                                     margin = margin(t = 10), size = 12),
          axis.ticks = element_blank(),
          axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
          axis.title.y = element_text(colour = "black", size = 17, margin = margin(r = 12)),
          plot.margin = margin(r = 30, t = 10, b = 10))
```

