---
title: "response_to_reviewer"
format: html
---

All these plots are create in response to reviewer comments. In long term, could be worth separating them into individual sections.

## Prepare workspace

```{r}
library(ggplot2)
library(dplyr)
```

## PLOT 1: Clans

Many comments from reviewers focus on clan numbers. We need to show how clan size varies over time, how clan size and trends in clan size differ between clans.

```{r}
### GENERATED IN STEP0_prepare_data/demographic_data.R
plot_data <- readRDS(here::here("./data/NClanplot_data_separate_year.RDS")) |> 
  mutate(pop = lay::lay(pick(young:ad_fem), sum),
         to = date + lubridate::years(1))
```

General stats:

**Max and min**

```{r}
## Max & min clan size
## What's up with Triangle in 2022?! Remove this for now
plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  summarise(across(young:pop, max, .names = "{.col}_max"),
            across(young:pop, min, .names = "{.col}_min")) 
```

```{r}
plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  filter(pop == min(pop))
```


**Difference in clan size**

```{r}
## Range clan size
## What's up with Triangle in 2022?! Remove this for now
plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  mutate(year = lubridate::year(date)) |> 
  group_by(year) |> 
  summarise(across(young:pop, .fns = \(x) abs(diff(range(x))), .names = "{.col}")) |> 
  filter(pop == max(pop))
```

```{r}
plot_data |> 
  filter(lubridate::year(date) == 2017)
```

Correlation between clans

```{r}
corr_data <- plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  select(date, clan, pop) |> 
  tidyr::pivot_wider(names_from = clan, values_from = pop)

library(corrplot)
corrplot(cor(corr_data |> select(-date)), method = "number", type = "lower", diag = FALSE, bg = "grey95")
```

Separate this into period before and after 2012

```{r}
corrplot(cor(corr_data |> filter(lubridate::year(date) < 2012) |> select(-date)), method = "number", type = "lower", diag = FALSE, bg = "grey95")
```

```{r}
corrplot(cor(corr_data |> filter(lubridate::year(date) >= 2012) |> select(-date)), method = "number", type = "lower", diag = FALSE, bg = "grey95")
```

Plot trends in total pop. Remember, there are totals in a year so they should be lines, not points.

```{r}
plot_data_lines <- plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  select(date, clan, pop, to) |> 
  tidyr::pivot_longer(cols = c(date, to))

end_vals <- plot_data %>%
  filter(lubridate::year(date) != 2022) |> 
  group_by(clan) %>%
  slice(n()) |> 
  ungroup()

ggplot() +
  geom_line(data = plot_data_lines, aes(x = value, y = pop, colour = clan, group = clan)) +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
           xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
           y = -2, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
           xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
           y = -4, yend = 0,
           lineend = "round", linejoin = "round") +
  ## Y TICKS
  annotate(geom = "segment",
           x = as.Date("1995-01-01"),
           xend = as.Date("1995-01-01") - 75,
           y = seq(0, 150, 25), yend = seq(0, 150, 25),
           lineend = "round", linejoin = "round") +
  ## LABELS
  geom_text(aes(x = as.Date("2023-06-01"),
                y = end_vals$pop + c(-0.05, 0.06), colour = end_vals$clan),
            label = end_vals$clan, size = 3,
            hjust = 0.5, lineheight = 0.75) +
  # scale_colour_manual(values = c("red", "grey10")) +
  scale_x_date(breaks = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 years"),
               date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0, 150, 25),
                     name = "Number of individuals") +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 150),
                  xlim = c(as.Date("1995-01-01"), as.Date("2025-01-01"))) +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 12),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
        axis.title.y = element_text(colour = "black", size = 17, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10))
```

```{r}
plot_data_bars <- plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  select(date, clan, pop, to) |> 
  mutate(year = lubridate::year(date))

end_vals <- plot_data %>%
  filter(lubridate::year(date) != 2022) |> 
  group_by(clan) %>%
  slice(n()) |> 
  ungroup()

ggplot(data = plot_data_bars) +
  geom_col(aes(x = date, y = pop, fill = clan),
           colour = "black", linewidth = 0.25) +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
           xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
           y = -10, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
           xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
           y = -20, yend = 0,
           lineend = "round", linejoin = "round") +
  ## Y TICKS
  annotate(geom = "segment",
           x = as.Date("1995-01-01"),
           xend = as.Date("1995-01-01") - 75,
           y = seq(0, 600, 100), yend = seq(0, 600, 100),
           lineend = "round", linejoin = "round") +
  ## LABEL TEXT
  # annotate(geom = "segment",
  #          x = end_vals$date[1] + 225,
  #          xend = end_vals$date[1] + 225,
  #          y = 5, yend = end_vals$pop[2] - 5,
  #          lineend = "round", linejoin = "round", linewidth = 0.75) +
  # annotate(geom = "segment",
  #          x = end_vals$date[1] + 225,
  #          xend = end_vals$date[1] + 225,
  #          y = end_vals$pop[2] + 5, yend = end_vals$pop[2] + end_vals$pop[1] - 5,
  #          lineend = "round", linejoin = "round", linewidth = 0.75) +
  # scale_fill_manual(values = rev(c("grey90", "grey55", "grey20"))) +
  # scale_linewidth_discrete(range = c(0, 0.75)) +
  scale_x_date(breaks = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 years"),
               date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0, 600, 100),
                     name = "Number of individuals") +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 600),
                  xlim = c(as.Date("1995-01-01"), as.Date("2025-01-01"))) +
  theme_classic() +
  theme(legend.position = "right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 12),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
        axis.title.y = element_text(colour = "black", size = 17, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10))
```

## PLOT 2: Simulation convergence

```{r}
years <- 1997:2022
facet_data <- purrr::map_df(.x = years, .f = function(sim_year, folder_name){
  
  txt_files <- list.files(here::here(paste0("./STEP1_estimate_K/", sim_year)),
                          pattern = ".txt", full.names = TRUE)
  
  allsims <- purrr::map_df(.x = txt_files,
                           .f = function(filepath){
                             
                             readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) |> 
                               dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=_)[0-9]+(?=.txt)"))
                             
                           })
  
  ## Estimate average (median) monthly pop within each year
  annual_avg <- allsims %>%
    select(sim, date, pop_size) |>
    mutate(year = lubridate::year(date)) |>
    dplyr::group_by(sim, year) |>
    summarise(window = median(pop_size), .groups = "drop")
  
  overall_avg <- annual_avg |> 
    group_by(year) |> 
    summarise(avg = median(window))
  
  output <- ggplot() +
    geom_line(data = annual_avg,
              aes(x = year, y = window, group = sim),
              linewidth = 0.1, colour = "grey10", alpha = 0.75) +
    geom_line(data = overall_avg,
              aes(x = year, y = avg),
              linewidth = 0.5, colour = "grey10") +
    ## X TICKS
    annotate(geom = "segment",
             x = seq(1995, 2100, by = 5),
             xend = seq(1995, 2100, by = 5),
             y = -7, yend = 0,
             lineend = "round", linejoin = "round") +
    annotate(geom = "segment",
             x = seq(2000, 2100, by = 20),
             xend = seq(2000, 2100, by = 20),
             y = -12, yend = 0,
             lineend = "round", linejoin = "round") +
    ## Y TICKS
    annotate(geom = "segment",
             x = 1990,
             xend = 1990 - 1,
             y = seq(0, 1000, 100), yend = seq(0, 1000, 100),
             lineend = "round", linejoin = "round") +
    labs(title = sim_year) +
    scale_x_continuous(breaks = seq(2000, 2100, by = 20)) +
    scale_y_continuous(breaks = seq(0, 1000, 100),
                       name = "Number of individuals (annual average)") +
    coord_cartesian(expand = FALSE, clip = "off",
                    ylim = c(0, 1000),
                    xlim = c(1990, 2100)) +
    theme_classic() +
    theme(legend.position = "right",
          axis.title.x = element_blank(),
          axis.text.x = element_text(colour = "black",
                                     margin = margin(t = 10), size = 12),
          axis.ticks = element_blank(),
          axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
          axis.title.y = element_text(colour = "black", size = 14, margin = margin(r = 12)),
          plot.margin = margin(r = 30, t = 10, b = 10),
          plot.title = element_text(size = 20, colour = "black"))
  
  ggplot2::ggsave(plot = output, here::here(paste0("./plots/sim_outputs/simulation_results_", sim_year, ".png")),
                  height = 8, width = 9, dpi = 300)
  
  output_data <- annual_avg |> 
    tidyr::pivot_wider(names_from = sim, values_from = window) |> 
    left_join(overall_avg, by = "year") |> 
    mutate(sim_year = sim_year)
  
  return(output_data)
  
})
```

Create a facet wrap plot

```{r}
plot_data <- facet_data |> 
  tidyr::pivot_longer(cols = `1`:avg)

sim_value <- plot_data |> 
  filter(name != "avg")

overall_value <- plot_data |> 
  filter(name == "avg")

facet_plot <- ggplot() +
  geom_line(data = sim_value,
            aes(x = year, y = value, group = name),
            linewidth = 0.1, colour = "grey10", alpha = 0.75) +
  geom_line(data = overall_value,
            aes(x = year, y = value),
            linewidth = 0.5, colour = "grey10") +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(1995, 2100, by = 5),
           xend = seq(1995, 2100, by = 5),
           y = -7, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(2000, 2100, by = 20),
           xend = seq(2000, 2100, by = 20),
           y = -12, yend = 0,
           lineend = "round", linejoin = "round") +
  ## Y TICKS
  annotate(geom = "segment",
           x = 1990,
           xend = 1990 - 1,
           y = seq(0, 1000, 100), yend = seq(0, 1000, 100),
           lineend = "round", linejoin = "round") +
  facet_wrap(facets = ~sim_year, ncol = 6) +
  scale_x_continuous(breaks = seq(2000, 2100, by = 20)) +
  scale_y_continuous(breaks = seq(0, 1000, 100),
                     name = "Number of individuals (annual average)") +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 1000),
                  xlim = c(1990, 2100)) +
  theme_classic() +
  theme(legend.position = "right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 12),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
        axis.title.y = element_text(colour = "black", size = 14, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10),
        strip.text = element_text(size = 20, colour = "black"),
        strip.background = element_rect(colour = "grey80"))

ggplot2::ggsave(plot = facet_plot, here::here("./plots/sim_outputs/simulation_results_facet.png"),
                height = 16, width = 18, dpi = 300)

```


## PLOT 3: Quantify simulation stability

How can we estimate and plot population stability? Example from 1997

```{r}
library(dplyr)
library(ggplot2)
```

```{r}
years <- 1997:2022
all_data <- purrr::map_df(.x = years, .f = function(sim_year, folder_name){
  
  txt_files <- list.files(here::here(paste0("./STEP1_estimate_K/", sim_year)),
                          pattern = ".txt", full.names = TRUE)
  
  allsims <- purrr::map_df(.x = txt_files,
                           .f = function(filepath){
                             
                             readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) |> 
                               dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=_)[0-9]+(?=.txt)"))
                             
                           }) |> 
    mutate(sim_year = sim_year)
  
  allsims
  
})

all_data_select <- all_data |> 
  select(sim_year, date, pop_size, sim)
```

### Variance

Remove data until we reach a variance below X (X is arbitrary...)

```{r}
## Try and example for sim 1
burnin_allyrs <- purrr::map_df(.x = 1997:2022, .f = \(focal_year){
  
  allsims <- all_data_select |> 
    filter(sim_year == focal_year)
  
  purrr::map_df(.x = 1:10, \(sim_nr){
    
    simN <- allsims |> 
      filter(sim == sim_nr)
    
    ## Loop through removing 1 month at a time
    simN_var <- purrr::map_dfr(.x = 1:(nrow(simN) - 1), \(x){
      
      data.frame(sim = sim_nr, x = x,
                 var = var(simN$pop_size[x:nrow(simN)]))
      
    }) |> 
      mutate(sim_year = focal_year)
    
    ## Also calculate slope
    simN_var$slope <- c(purrr::map_dbl(.x = 1:(nrow(simN_var) - 1), \(i){
      
      diff(simN_var$var[i:(i+1)])
      
    }), NA)
    
    simN_var$pop_slope <- c(purrr::map_dbl(.x = 1:(nrow(simN_var) - 1), \(i){
      
      diff(simN$pop_size[i:(i+1)])
      
    }), NA)
    
    return(simN_var)
    
  })
  
})
```

```{r}
ggplot() +
  geom_line(data = burnin_allyrs,
            aes(x = x, y = var, group = sim), linewidth = 0.1) +
  facet_wrap(facets = ~sim_year)
```

```{r}
ggplot() +
  geom_line(data = burnin_allyrs,
            aes(x = x, y = slope, group = sim), linewidth = 0.1) +
  facet_wrap(facets = ~sim_year)
```

Our approach:

- In all simulations, population size increased from starting population (equivalent to status in 1997)
- We removed steps from each simulation to reduce variance in population size
- Each simulation was considered 'stable' once removing steps no longer decreased variance AND absolute variance was below 750.

Apply our approach below:

```{r}
stable_sims <- burnin_allyrs |> 
  group_by(sim, sim_year) |> 
  filter(x >= min(which(slope > 0)) & x >= min(which(var <= 750))) |> 
  slice(1) |> 
  ungroup() |> 
  arrange(sim_year, sim)

stable_sims
```

```{r}
range(stable_sims$x)
```

How quickly did sims converge?

```{r}
plot_data <- stable_sims |> 
  mutate(years_converge = x/12)

converge_hist <- ggplot() +
  geom_histogram(data = plot_data,
                 aes(x = years_converge), binwidth = 1,
                 colour = "black", fill = "grey80") +
  geom_vline(xintercept = median(plot_data$years_converge), lty = 2) +
  geom_text(aes(x = median(plot_data$years_converge) + 1,
                y = 55, label = paste0("Median: ", median(plot_data$years_converge), " years")),
            hjust = 0) +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(0, 70, by = 2),
           xend = seq(0, 70, by = 2),
           y = -0.5, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(0, 70, by = 10),
           xend = seq(0, 70, by = 10),
           y = -1, yend = 0,
           lineend = "round", linejoin = "round") +
  scale_x_continuous(breaks = seq(0, 100, 10),
                     name = "Time until equilibrium (years)")  +
  scale_y_continuous(name = "Number of simulations")  +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 60),
                  xlim = c(0, 70)) +
  theme_classic() +
  theme(legend.position = "right",
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 10),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(colour = "black", size = 10, margin = margin(r = 5)),
        axis.title = element_text(colour = "black", size = 12, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10),
        strip.text = element_text(size = 20, colour = "black"),
        strip.background = element_rect(colour = "grey80"))

ggplot2::ggsave(plot = converge_hist, here::here("./plots/sim_outputs/convergence_histogram.png"),
                height = 7, width = 8, dpi = 300)
```

How many years of data does this give us? In all but 3 sims, we end up with >67 years of data. Do we want to run these other sims longer?

```{r}
plot_data <- stable_sims |> 
  mutate(years_data = (1200-x)/12)

ggplot() +
  geom_histogram(data = plot_data,
                 aes(x = years_data), binwidth = 1) +
  scale_x_continuous(breaks = seq(30, 100, 10))
```

What does Kt look like using this method?

```{r}
stable_data <- all_data_select |> 
  group_by(sim, sim_year) |> 
  mutate(x = 1:n(), sim = as.integer(sim)) |> 
  select(sim, sim_year, x, pop_size) |> 
  ungroup() |> 
  left_join(stable_sims |> 
              select(sim, sim_year, burnin = x),
            by = c("sim", "sim_year")) |> 
  filter(x >= burnin)

KtN_calc <- stable_data |> 
  group_by(sim, sim_year) |> 
  summarise(KtN = median(pop_size), .groups = "drop")

Kt_calc <- KtN_calc |> 
  group_by(sim_year) |> 
  summarise(Kt = median(KtN),
            lower = min(KtN), upper = max(KtN))
```

Compare to our previous hard cut-off method

```{r}
## Old data
Kplot_data <- readRDS(here::here("./data/Kplot_data.RDS"))

ggplot() +
  geom_errorbar(data = Kplot_data,
                aes(x = year, ymin = lower, ymax = upper),
                width = 0) +
  geom_point(data = Kplot_data,
             aes(x = year, y = globalK)) +
  geom_errorbar(data = Kt_calc,
                aes(x = sim_year + 0.25, ymin = lower, ymax = upper),
                width = 0, colour = "blue") +
  geom_point(data = Kt_calc,
             aes(x = sim_year + 0.25, y = Kt),
             colour = "blue")
```

When we have defined something as 'at equilibrium' how much do time steps vary from this Kt value?

```{r}
divergence <- stable_data |> 
  left_join(KtN_calc, by = c("sim", "sim_year")) |> 
  mutate(diff = pop_size - KtN,
         abs_diff = abs(diff)) |> 
  ## What % are within 30 individuals?
  summarise(in30 = sum(abs_diff <= 30),
            perc_in30 = in30/n())

divergence
```

How long does a simulation take to return +- 30?

```{r}
months_diverged <- stable_data |> 
  left_join(KtN_calc, by = c("sim", "sim_year")) |> 
  mutate(abs_diff = abs(pop_size - KtN),
         over30 = abs_diff > 30) |> 
  arrange(sim_year, sim)

block_IDs <- c()
block_values <- c()
for (focal_year in years){
  for (focal_sim in 1:10){
    data <- months_diverged |> 
      filter(sim_year == focal_year & sim == focal_sim) |> 
      pull(over30)
    rle_check <- rle(data)
    block_IDs <- append(block_IDs, rep(seq_along(rle_check$lengths), rle_check$lengths))
    block_values <- append(block_values, rep(rle_check$values, rle_check$lengths))
  }
}

months_diverged$group <- block_IDs
months_diverged$over30_block <- block_values

divergence_length <- months_diverged |> 
  filter(over30) |> 
  group_by(sim, sim_year, group) |> 
  summarise(n = n(), .groups = "drop")

median(divergence_length$n)
```

What if we just use our 750 cut-off without considering the change in variance?

```{r}
stable_sims_simple <- burnin_allyrs |> 
  group_by(sim, sim_year) |> 
  filter(x >= min(which(var <= 750))) |> 
  slice(1) |> 
  ungroup() |> 
  arrange(sim_year, sim)

stable_sims_simple
```

No, this is not strict enough.

```{r}
range(stable_sims_simple$x)
```

Could we take the same approach but just for pop size? (i.e. we filter once sim stops growing). NO. Due to demographic stochasticity, we still can see some declines month to month even in 'growth' period at the start of the sim.

```{r}
burnin_allyrs |> 
  group_by(sim, sim_year) |> 
  slice(min(which(pop_slope < 0)))
```

What if we do it based on annual average instead?

```{r}
stable_sims_popsize <- all_data_select |> 
  mutate(step_year = lubridate::year(date)) |> 
  group_by(sim_year, sim, step_year) |> 
  summarise(pop_size_avg = median(pop_size)) |> 
  group_by(sim_year, sim) |> 
  mutate(pop_slope = lead(pop_size_avg) - pop_size_avg) |> 
  slice(min(which(pop_slope <= 0)))

stable_sims_popsize
```

Some cases see first annual decline already in first year!

```{r}
range(stable_sims_popsize$step_year)
```

### Time series stationarity tests

Dickey-Fuller test considers the null hypothesis that the data are non-stationary. Therefore, 'stationary' time series should have a significant value. Majority 

```{r}
purrr::map_dfr(1:10, \(x){
  
  data <- annual_avg |> 
    filter(year >= 2030 & sim == x)
  ## Consider relationship with data in the previous year
  test <- tseries::adf.test(data$window, k = 1)
  data.frame(sim = x, adf = test$p.value)
  
})
```

KPSS test considers the null hypothesis that the data are stationary. Therefore, in 'stationary' time series we would not reject the null hypothesis.

```{r}
purrr::map_dfr(1:10, \(x){
  
  data <- annual_avg |> 
    filter(year >= 2030 & sim == x)
  ## Consider relationship with data in the same month in the previous year
  test <- tseries::kpss.test(data$window, lshort = TRUE)
  data.frame(sim = x, kpss = test$p.value)
  
})
```

Phillips-Peron test, similar to Dickey-Fuller but specifically tests for different possible non-stationary functions.

```{r}
purrr::map_dfr(1:10, \(x){
  
  data <- annual_avg |> 
    filter(year >= 2030 & sim == x)
  test <- aTSA::pp.test(data$window, lag.short = TRUE)
  ## Type 2 test considers just random drift (i.e. values will increase by a certain amount each time step)
  ## Type 3 tests for an explicit linear trend relationship with t
  data.frame(sim = x, pp_type2 = test[2, 3], pp_type3 = test[3, 3])
  
})
```
Just manually fit a GLM that tests for a year effect!

```{r}
purrr::map_dfr(1:10, \(x){
  
  data <- annual_avg |> 
    filter(year >= 2030 & sim == x)
  test <- lm(window ~ year, data = data)
  test2 <- summary(test)
  ## Type 2 test considers just random drift (i.e. values will increase by a certain amount each time step)
  ## Type 3 tests for an explicit linear trend relationship with t
  data.frame(sim = x, year_pval = test2$coefficients[2, 4])
  
})
```

### Gelman-Rubin stat

I'm not convinced this is useful (or appropriate) because even if we run for Inf time, we still expect some level of variation due to demographic stochasticity (that is what our model is DESIGNED to do). I think it's more appropriate to look whether each INDIVIDUAL run has stabilised or is still trending.

```{r}
## Convert into matrix of chains for Bolstad2 package
## Just an example package to test the idea
theta <- annual_avg |>
  select(sim, window) |>
  tidyr::pivot_wider(names_from = sim, values_from = window) |>
  tidyr::unnest(cols = 1:max(burnin$sim)) |>
  as.matrix()
```
```{r}
## We get values very close or above 1.1, which is usually too high
## Looking at the sims, there is still a lot of variation...however, it's not
## clear that leaving to run for longer would lead to convergence (or whether
## "convergence" is even possible with a stochastic simulated pop)

## Gelman-Rubin compares variance between chains to variance within chains
## We would expect value <1.1 at a minimum to suggest convergence
Bolstad2::GelmanRubin(theta)
```

Included two new runs that go for even longer....

```{r}
txt_files <- list.files(here::here(paste0("./STEP1_estimate_K")),
                        pattern = ".txt", full.names = TRUE)

allsims_long <- purrr::map_df(.x = txt_files,
                              .f = function(filepath){
                                
                                readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) |> 
                                  dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=_)[0-9]+(?=.txt)"))
                                
                              })

## Estimate average (median) monthly pop within each year
annual_avg_long <- allsims %>%
  select(sim, date, pop_size) |>
  mutate(year = lubridate::year(date)) |>
  dplyr::group_by(sim, year) |>
  summarise(window = median(pop_size), .groups = "drop")

overall_avg_long <- annual_avg_long |> 
  group_by(year) |> 
  summarise(avg = median(window))
```

```{r}
## Plot absolute values
ggplot() +
  geom_line(data = annual_avg_long,
            aes(x = year, y = window, group = sim),
            linewidth = 0.1, colour = "grey10", alpha = 0.75) +
  geom_line(data = overall_avg_long,
            aes(x = year, y = avg),
            linewidth = 0.5, colour = "grey10") +
  geom_vline(xintercept = 2100, lty = 2) +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(2000, 2400, by = 10),
           xend = seq(2000, 2400, by = 10),
           y = -10, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(2000, 2400, by = 50),
           xend = seq(2000, 2400, by = 50),
           y = -20, yend = 0,
           lineend = "round", linejoin = "round") +
  ## Y TICKS
  annotate(geom = "segment",
           x = 1990,
           xend = 1990 - 1,
           y = seq(0, 600, 100), yend = seq(0, 600, 100),
           lineend = "round", linejoin = "round") +
  scale_x_continuous(breaks = seq(2000, 2400, by = 50)) +
  scale_y_continuous(breaks = seq(0, 600, 100),
                     name = "Number of individuals (annual average)") +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 600),
                  xlim = c(1990, 2400)) +
  theme_classic() +
  theme(legend.position = "right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 12),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
        axis.title.y = element_text(colour = "black", size = 14, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10))
```

### Gewkes convergence diagnostic

```{r}
## Try Gewkes convergence diagnostic
## This is just a Z-score to compare start and end of a chain
## If |Z-score| is >1.96 it suggests non-stationarity (i.e. end and start are different!)
## Use LaplacesDemon
## All but a few are considered 'non-stationary' with this method
LaplacesDemon::Geweke.Diagnostic(theta)
```

### Heidelberger-Welch Test

```{r}
## Maybe statistics from time series analysis?
## Augmeted Dicky-Fuller tests for stationarity (H0 = series is NOT stationary)
## Only 1 series considered non-stationary
apply(theta, MARGIN = 2, FUN = \(x){
  
  tseries::adf.test(x)$p.value
  
})
```

### Longer runs

Would we expect results to be any better if we run simulations for longer?

```{r}
year <- 1997
txt_files <- list.files(here::here(paste0("./STEP1_estimate_K")),
                        pattern = ".txt", full.names = TRUE)

allsims_long <- purrr::map_df(.x = txt_files,
                              .f = function(filepath){
                                
                                readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) |> 
                                  dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=_)[0-9]+(?=.txt)"))
                                
                              })

## Estimate average (median) monthly pop within each year
annual_avg_long <- allsims_long %>%
  select(sim, date, pop_size) |>
  mutate(year = lubridate::year(date)) |>
  dplyr::group_by(sim, year) |>
  summarise(window = median(pop_size), .groups = "drop")

overall_avg_long <- annual_avg_long |> 
  group_by(year) |> 
  summarise(avg = median(window))
```

```{r}
## Plot absolute values
ggplot() +
  geom_line(data = annual_avg_long,
            aes(x = year, y = window, group = sim),
            linewidth = 0.1, colour = "grey10", alpha = 0.75) +
  geom_line(data = overall_avg_long,
            aes(x = year, y = avg),
            linewidth = 0.5, colour = "grey10") +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(2000, 2400, by = 25),
           xend = seq(2000, 2400, by = 25),
           y = -10, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(2000, 2400, by = 50),
           xend = seq(2000, 2400, by = 50),
           y = -20, yend = 0,
           lineend = "round", linejoin = "round") +
  ## Y TICKS
  annotate(geom = "segment",
           x = 1990,
           xend = 1990 - 1,
           y = seq(0, 600, 100), yend = seq(0, 600, 100),
           lineend = "round", linejoin = "round") +
  scale_x_continuous(breaks = seq(2000, 2400, by = 50)) +
  scale_y_continuous(breaks = seq(0, 600, 100),
                     name = "Number of individuals (annual average)") +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 600),
                  xlim = c(1990, 2400)) +
  theme_classic() +
  theme(legend.position = "right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 12),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
        axis.title.y = element_text(colour = "black", size = 14, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10))
```

Apply all these stats to data until 2100 and then data until the end of the time series!

Dickey-Fuller test considers the null hypothesis that the data are non-stationary. Therefore, 'stationary' time series should have a significant value. Majority 

```{r}
purrr::map_dfr(1:2, \(x){
  
  data <- annual_avg_long |> 
    filter(year >= 2030 & year <= 2100 & sim == x)
  ## Consider relationship with data in the previous year
  test_short <- tseries::adf.test(data$window, k = 1)
  
  data2 <- annual_avg_long |> 
    filter(year >= 2030 & sim == x)
  ## Consider relationship with data in the previous year
  test_long <- tseries::adf.test(data2$window, k = 1)
  
  data.frame(sim = x, adf_short = test_short$p.value, adf_long = test_long$p.value)
  
})
```

KPSS test considers the null hypothesis that the data are stationary. Therefore, in 'stationary' time series we would not reject the null hypothesis.

```{r}
purrr::map_dfr(1:2, \(x){
  
  data <- annual_avg_long |> 
    filter(year >= 2030 & year <= 2100 & sim == x)
  ## Consider relationship with data in the same month in the previous year
  test <- tseries::kpss.test(data$window, lshort = TRUE)
  
  data2 <- annual_avg_long |> 
    filter(year >= 2030 & sim == x)
  ## Consider relationship with data in the same month in the previous year
  test_long <- tseries::kpss.test(data2$window, lshort = TRUE)
  
  data.frame(sim = x, kpss = test$p.value, kpss_long = test_long$p.value)
  
})
```

Phillips-Peron test, similar to Dickey-Fuller but specifically tests for different possible non-stationary functions.

```{r}
purrr::map_dfr(1:2, \(x){
  
  data <- annual_avg_long |> 
    filter(year >= 2030 & year <= 2100 & sim == x)
  test <- aTSA::pp.test(data$window, lag.short = TRUE)
  
  data2 <- annual_avg_long |> 
    filter(year >= 2030 & sim == x)
  test_long <- aTSA::pp.test(data2$window, lag.short = TRUE)
  ## Type 2 test considers just random drift (i.e. values will increase by a certain amount each time step)
  ## Type 3 tests for an explicit linear trend relationship with t
  data.frame(sim = x,
             pp_type2 = test[2, 3], pp_type3 = test[3, 3],
             pp_type2_long = test_long[2, 3], pp_type3_long = test_long[3, 3])
  
})
```

Just manually fit a GLM that tests for a year effect!

```{r}
purrr::map_dfr(1:2, \(x){
  
  data <- annual_avg_long |> 
    filter(year >= 2030 & year <= 2100 & sim == x)
  test <- lm(window ~ year, data = data)
  test2 <- summary(test)
  
  data2 <- annual_avg_long |> 
    filter(year >= 2030 & sim == x)
  test_long <- lm(window ~ year, data = data2)
  test2_long <- summary(test_long)
  ## Type 2 test considers just random drift (i.e. values will increase by a certain amount each time step)
  ## Type 3 tests for an explicit linear trend relationship with t
  data.frame(sim = x,
             year_pval = test2$coefficients[2, 4],
             year_pval_long = test2_long$coefficients[2, 4])
  
})
```

### Gelman-Rubin stat

I'm not convinced this is useful (or appropriate) because even if we run for Inf time, we still expect some level of variation due to demographic stochasticity (that is what our model is DESIGNED to do). I think it's more appropriate to look whether each INDIVIDUAL run has stabilised or is still trending.

```{r}
## Convert into matrix of chains for Bolstad2 package
## Just an example package to test the idea
theta <- annual_avg_long |>
  filter(year >= 2020 & year <= 2100) |> 
  select(sim, window) |>
  tidyr::pivot_wider(names_from = sim, values_from = window) |>
  tidyr::unnest(cols = 1:max(annual_avg_long$sim)) |>
  as.matrix()

Bolstad2::GelmanRubin(theta)
```

```{r}
## Convert into matrix of chains for Bolstad2 package
## Just an example package to test the idea
theta <- annual_avg_long |>
  filter(year >= 2030) |> 
  select(sim, window) |>
  tidyr::pivot_wider(names_from = sim, values_from = window) |>
  tidyr::unnest(cols = 1:max(annual_avg_long$sim)) |>
  as.matrix()

Bolstad2::GelmanRubin(theta)
```

