---
title: "response_to_reviewer"
format: html
---

All these plots are create in response to reviewer comments. In long term, could be worth separating them into individual sections.

## Prepare workspace

```{r}
library(ggplot2)
library(dplyr)
```

## PLOT 1: Clans

Many comments from reviewers focus on clan numbers. We need to show how clan size varies over time, how clan size and trends in clan size differ between clans.

```{r}
### GENERATED IN STEP0_prepare_data/demographic_data.R
plot_data <- readRDS(here::here("./data/NClanplot_data_separate_year.RDS")) |> 
  mutate(pop = lay::lay(pick(young:ad_fem), sum),
         to = date + lubridate::years(1))
```

General stats:

**Max and min**

```{r}
## Max & min clan size
## What's up with Triangle in 2022?! Remove this for now
plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  summarise(across(young:pop, max, .names = "{.col}_max"),
            across(young:pop, min, .names = "{.col}_min")) 
```

```{r}
plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  filter(pop == min(pop))
```


**Difference in clan size**

```{r}
## Range clan size
## What's up with Triangle in 2022?! Remove this for now
plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  mutate(year = lubridate::year(date)) |> 
  group_by(year) |> 
  summarise(across(young:pop, .fns = \(x) abs(diff(range(x))), .names = "{.col}")) |> 
  filter(pop == max(pop))
```

```{r}
plot_data |> 
  filter(lubridate::year(date) == 2017)
```

Correlation between clans

```{r}
corr_data <- plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  select(date, clan, pop) |> 
  tidyr::pivot_wider(names_from = clan, values_from = pop)

library(corrplot)
corrplot(cor(corr_data |> select(-date)), method = "number", type = "lower", diag = FALSE, bg = "grey95")
```

Separate this into period before and after 2012

```{r}
corrplot(cor(corr_data |> filter(lubridate::year(date) < 2012) |> select(-date)), method = "number", type = "lower", diag = FALSE, bg = "grey95")
```

```{r}
corrplot(cor(corr_data |> filter(lubridate::year(date) >= 2012) |> select(-date)), method = "number", type = "lower", diag = FALSE, bg = "grey95")
```

Plot trends in total pop. Remember, there are totals in a year so they should be lines, not points.

```{r}
plot_data_lines <- plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  select(date, clan, pop, to) |> 
  tidyr::pivot_longer(cols = c(date, to))

end_vals <- plot_data %>%
  filter(lubridate::year(date) != 2022) |> 
  group_by(clan) %>%
  slice(n()) |> 
  ungroup()

ggplot() +
  geom_line(data = plot_data_lines, aes(x = value, y = pop, colour = clan, group = clan)) +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
           xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
           y = -2, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
           xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
           y = -4, yend = 0,
           lineend = "round", linejoin = "round") +
  ## Y TICKS
  annotate(geom = "segment",
           x = as.Date("1995-01-01"),
           xend = as.Date("1995-01-01") - 75,
           y = seq(0, 150, 25), yend = seq(0, 150, 25),
           lineend = "round", linejoin = "round") +
  ## LABELS
  geom_text(aes(x = as.Date("2023-06-01"),
                y = end_vals$pop + c(-0.05, 0.06), colour = end_vals$clan),
            label = end_vals$clan, size = 3,
            hjust = 0.5, lineheight = 0.75) +
  # scale_colour_manual(values = c("red", "grey10")) +
  scale_x_date(breaks = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 years"),
               date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0, 150, 25),
                     name = "Number of individuals") +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 150),
                  xlim = c(as.Date("1995-01-01"), as.Date("2025-01-01"))) +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 12),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
        axis.title.y = element_text(colour = "black", size = 17, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10))
```

```{r}
plot_data_bars <- plot_data |> 
  filter(lubridate::year(date) != 2022) |> 
  select(date, clan, pop, to) |> 
  mutate(year = lubridate::year(date))

end_vals <- plot_data %>%
  filter(lubridate::year(date) != 2022) |> 
  group_by(clan) %>%
  slice(n()) |> 
  ungroup()

ggplot(data = plot_data_bars) +
  geom_col(aes(x = date, y = pop, fill = clan),
           colour = "black", linewidth = 0.25) +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
           xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "1 year"),
           y = -10, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
           xend = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 year"),
           y = -20, yend = 0,
           lineend = "round", linejoin = "round") +
  ## Y TICKS
  annotate(geom = "segment",
           x = as.Date("1995-01-01"),
           xend = as.Date("1995-01-01") - 75,
           y = seq(0, 600, 100), yend = seq(0, 600, 100),
           lineend = "round", linejoin = "round") +
  ## LABEL TEXT
  # annotate(geom = "segment",
  #          x = end_vals$date[1] + 225,
  #          xend = end_vals$date[1] + 225,
  #          y = 5, yend = end_vals$pop[2] - 5,
  #          lineend = "round", linejoin = "round", linewidth = 0.75) +
  # annotate(geom = "segment",
  #          x = end_vals$date[1] + 225,
  #          xend = end_vals$date[1] + 225,
  #          y = end_vals$pop[2] + 5, yend = end_vals$pop[2] + end_vals$pop[1] - 5,
  #          lineend = "round", linejoin = "round", linewidth = 0.75) +
  # scale_fill_manual(values = rev(c("grey90", "grey55", "grey20"))) +
  # scale_linewidth_discrete(range = c(0, 0.75)) +
  scale_x_date(breaks = seq(as.Date("1995-01-01"), as.Date("2025-01-01"), by = "5 years"),
               date_labels = "%Y") +
  scale_y_continuous(breaks = seq(0, 600, 100),
                     name = "Number of individuals") +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 600),
                  xlim = c(as.Date("1995-01-01"), as.Date("2025-01-01"))) +
  theme_classic() +
  theme(legend.position = "right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 12),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
        axis.title.y = element_text(colour = "black", size = 17, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10))
```

## PLOT 2: Stability of simulations

How can we estimate and plot population stability? Example from 1997

```{r}
library(dplyr)
library(ggplot2)
```


```{r}
year <- 1997
txt_files <- list.files(here::here(paste0("./STEP1_estimate_K/", year)),
                        pattern = ".txt", full.names = TRUE)

allsims <- purrr::map_df(.x = txt_files,
                         .f = function(filepath){
                           
                           readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) |> 
                             dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=_)[0-9]+(?=.txt)"))
                           
                         })

## Estimate average (median) monthly pop within each year
annual_avg <- allsims %>%
  select(sim, date, pop_size) |>
  mutate(year = lubridate::year(date)) |>
  dplyr::group_by(sim, year) |>
  summarise(window = median(pop_size), .groups = "drop")

overall_avg <- annual_avg |> 
  group_by(year) |> 
  summarise(avg = median(window))
```

```{r}
## Plot absolute values
ggplot() +
  geom_line(data = annual_avg,
            aes(x = year, y = window, group = sim),
            linewidth = 0.1, colour = "grey10", alpha = 0.75) +
  geom_line(data = overall_avg,
            aes(x = year, y = avg),
            linewidth = 0.5, colour = "grey10") +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(1995, 2100, by = 5),
           xend = seq(1995, 2100, by = 5),
           y = -10, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(2000, 2100, by = 20),
           xend = seq(2000, 2100, by = 20),
           y = -20, yend = 0,
           lineend = "round", linejoin = "round") +
  ## Y TICKS
  annotate(geom = "segment",
           x = 1990,
           xend = 1990 - 1,
           y = seq(0, 600, 100), yend = seq(0, 600, 100),
           lineend = "round", linejoin = "round") +
  scale_x_continuous(breaks = seq(2000, 2100, by = 20)) +
  scale_y_continuous(breaks = seq(0, 600, 100),
                     name = "Number of individuals (annual average)") +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 600),
                  xlim = c(1990, 2100)) +
  theme_classic() +
  theme(legend.position = "right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 12),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
        axis.title.y = element_text(colour = "black", size = 14, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10))
```

### Gelman-Rubin stat

I'm not convinced this is useful (or appropriate) because even if we run for Inf time, we still expect some level of variation due to demographic stochasticity (that is what our model is DESIGNED to do). I think it's more appropriate to look whether each INDIVIDUAL run has stabilised or is still trending.

```{r}
## Convert into matrix of chains for Bolstad2 package
## Just an example package to test the idea
theta <- annual_avg |>
  select(sim, window) |>
  tidyr::pivot_wider(names_from = sim, values_from = window) |>
  tidyr::unnest(cols = 1:max(burnin$sim)) |>
  as.matrix()
```
```{r}
## We get values very close or above 1.1, which is usually too high
## Looking at the sims, there is still a lot of variation...however, it's not
## clear that leaving to run for longer would lead to convergence (or whether
## "convergence" is even possible with a stochastic simulated pop)

## Gelman-Rubin compares variance between chains to variance within chains
## We would expect value <1.1 at a minimum to suggest convergence
Bolstad2::GelmanRubin(theta)
```

Included two new runs that go for even longer....

```{r}
txt_files <- list.files(here::here(paste0("./STEP1_estimate_K")),
                        pattern = ".txt", full.names = TRUE)

allsims_long <- purrr::map_df(.x = txt_files,
                              .f = function(filepath){
                                
                                readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) |> 
                                  dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=_)[0-9]+(?=.txt)"))
                                
                              })

## Estimate average (median) monthly pop within each year
annual_avg_long <- allsims %>%
  select(sim, date, pop_size) |>
  mutate(year = lubridate::year(date)) |>
  dplyr::group_by(sim, year) |>
  summarise(window = median(pop_size), .groups = "drop")

overall_avg_long <- annual_avg_long |> 
  group_by(year) |> 
  summarise(avg = median(window))
```

```{r}
## Plot absolute values
ggplot() +
  geom_line(data = annual_avg_long,
            aes(x = year, y = window, group = sim),
            linewidth = 0.1, colour = "grey10", alpha = 0.75) +
  geom_line(data = overall_avg_long,
            aes(x = year, y = avg),
            linewidth = 0.5, colour = "grey10") +
  geom_vline(xintercept = 2100, lty = 2) +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(2000, 2400, by = 10),
           xend = seq(2000, 2400, by = 10),
           y = -10, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(2000, 2400, by = 50),
           xend = seq(2000, 2400, by = 50),
           y = -20, yend = 0,
           lineend = "round", linejoin = "round") +
  ## Y TICKS
  annotate(geom = "segment",
           x = 1990,
           xend = 1990 - 1,
           y = seq(0, 600, 100), yend = seq(0, 600, 100),
           lineend = "round", linejoin = "round") +
  scale_x_continuous(breaks = seq(2000, 2400, by = 50)) +
  scale_y_continuous(breaks = seq(0, 600, 100),
                     name = "Number of individuals (annual average)") +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 600),
                  xlim = c(1990, 2400)) +
  theme_classic() +
  theme(legend.position = "right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 12),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
        axis.title.y = element_text(colour = "black", size = 14, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10))
```

### Gewkes convergence diagnostic

```{r}
## Try Gewkes convergence diagnostic
## This is just a Z-score to compare start and end of a chain
## If |Z-score| is >1.96 it suggests non-stationarity (i.e. end and start are different!)
## Use LaplacesDemon
## All but a few are considered 'non-stationary' with this method
LaplacesDemon::Geweke.Diagnostic(theta)
```

### Heidelberger-Welch Test

```{r}
## Maybe statistics from time series analysis?
## Augmeted Dicky-Fuller tests for stationarity (H0 = series is NOT stationary)
## Only 1 series considered non-stationary
apply(theta, MARGIN = 2, FUN = \(x){
  
  tseries::adf.test(x)$p.value
  
})
```

```{r}
## Heidelberger-Welch Test: More aimed at discarding 'unconverged' parts
## Autocorrelation Analysis (IAT fn in LaplacesDemon).
## Testing for low auto-correlation seems meaningless because we KNOW our data are auto-correlated.
```

What if we do the same thing using some larger sliding window (e.g. 10 years)

```{r}
## Estimate average (median) monthly pop within each year
annual_avg_10y <- purrr::map_dfr(.x = seq(min(annual_avg$year),
                                          max(annual_avg$year)-10, 1), .f = \(x){
  allsims %>%
    select(sim, date, pop_size) |>
    mutate(year = lubridate::year(date)) |> 
    filter(year %in% seq(x, x+9, 1)) |> 
    group_by(sim) |> 
    summarise(window = median(pop_size)) |> 
    mutate(year = x+5)
})

overall_avg_10y <- annual_avg_10y |> 
  group_by(year) |> 
  summarise(avg = median(window))
```

```{r}
## Plot absolute values
ggplot() +
  geom_line(data = annual_avg_10y,
            aes(x = year, y = window, group = sim),
            linewidth = 0.1, colour = "grey10", alpha = 0.75) +
  geom_line(data = overall_avg_10y,
            aes(x = year, y = avg),
            linewidth = 0.5, colour = "grey10") +
  ## X TICKS
  annotate(geom = "segment",
           x = seq(1995, 2100, by = 5),
           xend = seq(1995, 2100, by = 5),
           y = -10, yend = 0,
           lineend = "round", linejoin = "round") +
  annotate(geom = "segment",
           x = seq(2000, 2100, by = 20),
           xend = seq(2000, 2100, by = 20),
           y = -20, yend = 0,
           lineend = "round", linejoin = "round") +
  ## Y TICKS
  annotate(geom = "segment",
           x = 1990,
           xend = 1990 - 1,
           y = seq(0, 600, 100), yend = seq(0, 600, 100),
           lineend = "round", linejoin = "round") +
  scale_x_continuous(breaks = seq(2000, 2100, by = 20)) +
  scale_y_continuous(breaks = seq(0, 600, 100),
                     name = "Number of individuals (annual average)") +
  coord_cartesian(expand = FALSE, clip = "off",
                  ylim = c(0, 600),
                  xlim = c(1990, 2100)) +
  theme_classic() +
  theme(legend.position = "right",
        axis.title.x = element_blank(),
        axis.text.x = element_text(colour = "black",
                                   margin = margin(t = 10), size = 12),
        axis.ticks = element_blank(),
        axis.text.y = element_text(colour = "black", size = 12, margin = margin(r = 5)),
        axis.title.y = element_text(colour = "black", size = 14, margin = margin(r = 12)),
        plot.margin = margin(r = 30, t = 10, b = 10))
```

```{r}
## Convert into matrix of chains for Bolstad2 package
## Just an example package to test the idea
theta <- annual_avg_10y |>
  select(sim, window) |>
  tidyr::pivot_wider(names_from = sim, values_from = window) |>
  tidyr::unnest(cols = 1:max(burnin$sim)) |>
  as.matrix()
```

```{r}
## Try Gewkes convergence diagnostic
## This is just a Z-score to compare start and end of a chain
## If |Z-score| is >1.96 it suggests non-stationarity (i.e. end and start are different!)
## Use LaplacesDemon
## All but a few are considered 'non-stationary' with this method
LaplacesDemon::Geweke.Diagnostic(theta)
```
