---
title: "Temporal_trend"
output: html_document
date: '2022-10-19'
---

This document includes analysis of all temporal trends in the data. This includes:
- Absolute population abundance
- Carrying capacity
- Sex ratio
- Age ratio

# Prepare workspace

Load required packages

```{r pkg}
library(ggplot2)
library(hyenaR)
library(dplyr)
library(here)
library(spaMM)
spaMM.options(nb_cores=10) ## CHECK WITH htop BEFORE USING TOO MANY
library(doSNOW)
library(DHARMa)
library(lubridate)
```

Define which simulation type we're using

```{r params}
start_year  <- 1997
end_year    <- 2022
growth_period_until <- 2011
scale <- "year"
```

# Extract data

Extract estimated K

```{r k_data}
## Time-varying carrying capacity (Kt) 
if (!file.exists(here::here("./data/Kplot_data.RDS"))) {
  ## EXTRACT ESTIMATED K
  years <- start_year:end_year
  
  pb_yr <- progress::progress_bar$new(total = length(years))
  
  Kplot_data <- purrr::map_df(.x = years,
                              .f = function(year){
                                
                                pb_yr$tick()
                                
                                txt_files <- list.files(here(paste0("./STEP1_estimate_K/", year)),
                                                        pattern = ".txt", full.names = TRUE)
                                
                                allsims <- purrr::map_df(.x = txt_files,
                                                         .f = function(filepath){
                                                           
                                                           readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) %>%
                                                             dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=_)[0-9]+(?=.txt)"))
                                                           
                                                         })
                                
                                estK <- allsims %>% 
                                  dplyr::group_by(.data$sim) %>% 
                                  dplyr::mutate(start_pop = first(pop_size)) %>% 
                                  dplyr::slice(ceiling(dplyr::n()/2):dplyr::n()) %>% 
                                  dplyr::summarise(K = median(.data$pop_size),
                                                   start_size = first(start_pop))
                                
                                plot_data <- estK %>% 
                                  dplyr::summarise(year = year,
                                                   globalK = median(.data$K),
                                                   lower = min(.data$K),
                                                   upper = max(.data$K),
                                                   points = list(data.frame(pop_size = .data$K,
                                                                            start_pop = .data$start_size)))
                                
                                return(plot_data)
                                
                              })
  
  saveRDS(Kplot_data, here::here("./data/Kplot_data.RDS"))
} else {
  Kplot_data <- readRDS(here::here("./data/Kplot_data.RDS"))
}

```

Extract real pop data over time at 1 month and 6mo intervals.

```{r N_data}
### GENERATED IN STEP0_prepare_data/demographic_data.R
if (scale == "year"){
  real_pop <- readRDS(here::here("./data/Nplot_data_year.RDS"))
  real_pop_separate <- readRDS(here::here("./data/Nplot_data_separate_year.RDS"))
} else if (scale == "month"){
  real_pop <- readRDS(here::here("./data/Nplot_data_month.RDS")) 
  real_pop_separate <- readRDS(here::here("./data/Nplot_data_separate_1month.RDS"))
}
```

Prepare sex and age ratio data

```{r N_data_separate}
### Calculate sex ratio (male/all females)
ratios <- real_pop_separate %>% 
  mutate(sex_ratio = ad_male/(ad_male + ad_fem),
         age_ratio = young/(young + ad_male + ad_fem)) %>% 
  tidyr::pivot_longer(cols = sex_ratio:age_ratio)
```


# Population abundance (N)

## Describe growth period

When were adult numbers highest in first growth period?

```{r growthN}
real_pop_separate %>%
  mutate(total_ad = ad_male+ad_fem) %>%
  filter(year(date) < 2015) %>%
  filter(total_ad == max(total_ad))
```

## Trend in whole period

```{r}
real_pop_growth <- real_pop |> 
  filter(lubridate::year(date) <= end_year) |> 
  mutate(year = lubridate::year(date),
         n = 1:n())

N_model <- fitme(pop_size ~ year + AR1(1|n), data = real_pop_growth, family = "gaussian")
N_model_null <- fitme(pop_size ~ 1 + AR1(1|n), data = real_pop_growth, family = "gaussian")

summary(N_model)
```

```{r}
LRT(N_model, N_model_null)
```

```{r}
confint(N_model, parm = "year")
```

## Trend during growth period

```{r}
real_pop_growth <- real_pop |> 
  filter(lubridate::year(date) <= growth_period_until) |> 
  mutate(year = lubridate::year(date),
         n = 1:n())

N_model <- fitme(pop_size ~ year + AR1(1|n), data = real_pop_growth, family = "gaussian")
N_model_null <- fitme(pop_size ~ 1 + AR1(1|n), data = real_pop_growth, family = "gaussian")

summary(N_model)
```

```{r}
LRT(N_model, N_model_null)
```

```{r}
confint(N_model, parm = "year")
```

## Trend after growth period

```{r}
real_pop_growth <- real_pop |> 
  filter(lubridate::year(date) > growth_period_until) |> 
  mutate(year = lubridate::year(date),
         n = 1:n())

N_model <- fitme(pop_size ~ year + AR1(1|n), data = real_pop_growth, family = "gaussian")
N_model_null <- fitme(pop_size ~ 1 + AR1(1|n), data = real_pop_growth, family = "gaussian")

summary(N_model)
```

```{r}
LRT(N_model, N_model_null)
```

```{r}
confint(N_model, parm = "year")
```

## Fluctuation in N following growth

How can we describe the period after growth period?

```{r}
postgrowth_data <- real_pop %>% 
  ## Use 1st May b/c we calculated over whole months
  ## Numbers are similar.
  filter(lubridate::year(date) > growth_period_until)

median(postgrowth_data$pop_size)

range(postgrowth_data$pop_size)
```

# Carrying capacity (K)

## Years of decline

When did K show sharp declines (we define here as <= 80% of previous value)

```{r}
Kplot_data %>% 
  filter(year <= end_year) %>% 
  reframe(prop_change = lead(globalK)/globalK,
          year = year) %>% 
  filter(!is.na(prop_change) & prop_change <= 0.8)
```

## Descriptive stats

Range and SD of K

```{r}
range(Kplot_data$globalK)

sd(Kplot_data$globalK)
```

## Kt in full period

Estimate over the full period (because we're not just focusing in growth anymore)

```{r}
Kplot_data_sub <- Kplot_data %>% 
  filter(year <= end_year) |> 
  mutate(n = 1:n())

poisson_data <- Kplot_data_sub %>% 
  mutate(globalK = as.integer(globalK))
```

#### Model 1: Poisson

```{r}
K_model1 <- fitme(globalK ~ year + AR1(1|n), data = poisson_data, family = "poisson")
```

```{r}
K_model1_resid <- simulateResiduals(K_model1, n = 1000, seed = 123)

plot(K_model1_resid)
```

QQ-plot is bad.

```{r}
DHARMa::testDispersion(K_model1_resid)
```

Major over-dispersion.

```{r}
acf(residuals(K_model1))
```
Temporal auto-correlation not too serious. For parsimony maybe easier to accept this and no need to fit AR1 term (which causes problems)

#### Model 2: Gaussian

Could we achieve the same thing just using Gaussian model?

```{r}
## Use the same Poisson data for AIC are comparable
K_model2 <- fitme(globalK ~ year + AR1(1|n), data = poisson_data, family = "gaussian")
```

```{r}
K_model2_resid <- simulateResiduals(K_model2, n = 1000, seed = 123)

plot(K_model2_resid)
```

Uniformity better, quantiles still a bit messy.

```{r}
DHARMa::testDispersion(K_model2_resid)
```

Dispersion issue fixed...

```{r}
acf(residuals(K_model2))
```

Temporal auto-correlation seems ok.

#### Model 3: Negative-binomial

```{r}
K_model3 <- fitme(globalK ~ year + AR1(1|n), data = poisson_data, family = spaMM::negbin2())
```

```{r}
K_model3_resid <- simulateResiduals(K_model3, n = 1000, seed = 123)

plot(K_model3_resid)
```

Uniformity better, quantiles still a bit messy.

```{r}
DHARMa::testDispersion(K_model3_resid)
```

Dispersion issue fixed...

```{r}
acf(residuals(K_model3))
```
Temporal auto-correlation seems not too bad.

#### Compare possible models

```{r}
do.call(dplyr::bind_rows, purrr::map(.x = list(K_model1, K_model2, K_model3),
                                     .f = spaMM::AIC.HLfit)) %>% 
  mutate(model = seq(1:n())) %>% 
  select(model, everything()) %>% 
  janitor::clean_names() %>% 
  arrange(marginal_aic)
```

Gaussian model is best (slightly better than negbin). We will look at both to see if results are comparable. Gaussian is preferable because it's easier to interpret/present and gives us results that can be compared to different model outcomes for other variables.

#### Model results and CI

##### Gaussian model

LRT to compare model to null

```{r}
global_mod <- fitme(globalK ~ year, data = poisson_data, family = "gaussian")
null_mod   <- fitme(globalK ~ 1, data = poisson_data, family = "gaussian")

summary(global_mod)
```
```{r}
## #Asymptotic pvalue for consistency
LRT(global_mod, null_mod)
# LRT_result_gaussian <- LRT(global_mod, null_mod, boot.repl = 999, nb_cores = 10, seed = 123)
# data.frame(basic = LRT_result_gaussian$basicLRT$p_value, bartlett = LRT_result_gaussian$BartBootLRT$p_value, bootstrap = LRT_result_gaussian$rawBootLRT$p_value)
```

Summary of full model

```{r}
summary(global_mod)
```

CI of year term

```{r}
spaMM::confint.HLfit(global_mod, parm = "year", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

Fixef term

```{r}
fixef(global_mod)[2]
```

## Ktc in full period

```{r ktc_data}
if (file.exists(here::here("./data/Kplot_clan_data.RDS"))) {
  Kplot_data_byclan <- readRDS(here::here("./data/Kplot_clan_data.RDS"))
} else {
  
  ## EXTRACT ESTIMATED
  years <- start_year:end_year
  
  pb_yr <- progress::progress_bar$new(total = length(years))
  
  Kplot_data <- purrr::map_df(.x = years,
                              .f = function(year, folder_name){
                                
                                pb_yr$tick()
                                
                                txt_files <- list.files(here(paste0("~/data/simulation_results/analysis/STEP1_estimate_K/", year)),
                                                        pattern = ".txt", full.names = TRUE)
                                
                                allsims <- purrr::map_df(.x = txt_files,
                                                         .f = function(filepath){
                                                           
                                                           readr::read_delim(filepath, show_col_types = FALSE, lazy = FALSE) %>%
                                                             dplyr::mutate(sim = stringr::str_extract(filepath, "(?<=_)[0-9]+(?=.txt)"))
                                                           
                                                         })
                                
                                #Remove deaths, mothers, father
                                allsims_sub <- allsims %>% 
                                  select(-contains("dead"), -contains("father"), -contains("mother")) %>% 
                                  tidyr::pivot_longer(cols = A_cubfem:T_dispmale) %>% 
                                  tidyr::separate(col = name, sep = "_", into = c("clan", "group")) %>% 
                                  group_by(clan, date, sim) %>% 
                                  summarise(pop_size = first(pop_size),
                                            clan_size = sum(value), .groups = "drop") %>% 
                                  tidyr::pivot_wider(names_from = clan, values_from = clan_size)
                                
                                estK <- allsims_sub %>% 
                                  dplyr::group_by(.data$sim) %>% 
                                  dplyr::mutate(start_pop = first(pop_size)) %>%
                                  dplyr::slice(ceiling(dplyr::n()/2):dplyr::n()) %>% 
                                  dplyr::summarise(across(.cols = pop_size:T, .fns = function(N) replace(median(N, na.rm = TRUE),
                                                                                                         is.na(median(N, na.rm = TRUE)), 0)),
                                                   start_size = first(start_pop),
                                                   year = year)
                                
                                return(estK)
                                
                              }, folder_name = folder_name)
  
  saveRDS(Kplot_data, file = here("./data/Kplot_clan_data.RDS"))
}

```

```{r Ktc_plot}
plot_data <- Kplot_data_byclan %>% 
  select(sim, A:T, year) %>% 
  tidyr::pivot_longer(A:T) %>% 
  group_by(name, year) %>% 
  summarise(median = as.integer(median(value)),
            min = min(value),
            max = max(value)) %>% 
  arrange(name, year) %>% 
  mutate(n = 1:n())

ggplot(data = plot_data) +
  geom_line(aes(x =year, y = median)) +
  geom_point(aes(x =year, y = median)) +
  facet_wrap(facets = ~name)
```

```{r Ktc_gaussian}
## Fit gaussian models for comparison
## Gaussian is easiest fit and can be compared with other mods.
K_model_perclan_gaussian <- fitme(median ~ year:name + name + AR1(1|n), data = plot_data, family = "gaussian")

```

```{r DHARMaKtc}
K_model_perclan_gaussian_resid <- simulateResiduals(K_model_perclan_gaussian, n = 1000, seed = 123)

plot(K_model_perclan_gaussian_resid)
```

Uniformity better, quantiles still a bit messy.

```{r}
DHARMa::testDispersion(K_model_perclan_gaussian_resid)
```

Dispersion issue fixed...

```{r}
acf(residuals(K_model_perclan_gaussian_resid))
```

```{r}
summary(K_model_perclan_gaussian)
```

```{r LRT_Ktc}
global_mod <- fitme(median ~ year:name + name + AR1(1|n), data = plot_data, family = "gaussian")
null_mod   <- fitme(median ~ name + AR1(1|n), data = plot_data, family = "gaussian")
summary(global_mod)
```
```{r}
## Need to bootstrap this, it takes some time
LRT(global_mod, null_mod)
# data.frame(basic = LRT_result_gaussian$basicLRT$p_value, bartlett = LRT_result_gaussian$BartBootLRT$p_value, bootstrap = LRT_result_gaussian$rawBootLRT$p_value)
```

CI of year term

```{r}
spaMM::confint.HLfit(global_mod, parm = "year:nameA", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(global_mod, parm = "year:nameE", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(global_mod, parm = "year:nameF", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(global_mod, parm = "year:nameL", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(global_mod, parm = "year:nameM", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(global_mod, parm = "year:nameN", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(global_mod, parm = "year:nameS", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(global_mod, parm = "year:nameT", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

## Kt in growth period

```{r}
K_model_growthperiod <- fitme(globalK ~ year + AR1(1|n), data = poisson_data %>% filter(year <= growth_period_until), family = "gaussian")
null_mod <- fitme(globalK ~ 1 + AR1(1|n), data = poisson_data %>% filter(year <= growth_period_until), family = "gaussian")
summary(K_model_growthperiod)
```
```{r}
## Asympototic for consistency
LRT(K_model_growthperiod, null_mod)
# LRT(K_model_growthperiod, null_mod, boot.repl = 999, nb_cores = 10, seed = 123)
```

```{r}
summary(K_model_growthperiod)
```

```{r}
confint(K_model_growthperiod, parm = "year", boot_args = list(nsim = 999, nb_cores = 10, seed = 123))
```

## Ktc in growth period

```{r}
K_model_perclan_growthperiod <- fitme(median ~ year:name + name + AR1(1|n),
                                      data = plot_data %>% filter(year <= growth_period_until), family = "gaussian")

null_mod <- fitme(median ~ name + AR1(1|n),
                  data = plot_data %>% filter(year <= growth_period_until), family = "gaussian")
summary(K_model_perclan_growthperiod)
```
```{r}
## Asympototic for consistency
LRT(K_model_perclan_growthperiod, null_mod)
# LRT(K_model_perclan_growthperiod, null_mod, boot.repl = 999, nb_cores = 10, seed = 123)
```

```{r}
summary(K_model_perclan_growthperiod)
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameA", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameE", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameF", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameL", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameM", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameN", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameS", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameT", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

## Kt in growth period

```{r}
K_model_growthperiod <- fitme(globalK ~ year + AR1(1|n), data = poisson_data %>% filter(year > growth_period_until), family = "gaussian")
null_mod <- fitme(globalK ~ 1 + AR1(1|n), data = poisson_data %>% filter(year > growth_period_until), family = "gaussian")
summary(K_model_growthperiod)
```
```{r}
## Asympototic for consistency
LRT(K_model_growthperiod, null_mod)
# LRT(K_model_growthperiod, null_mod, boot.repl = 999, nb_cores = 10, seed = 123)
```

```{r}
summary(K_model_growthperiod)
```

```{r}
confint(K_model_growthperiod, parm = "year", boot_args = list(nsim = 999, nb_cores = 10, seed = 123))
```

## Ktc after growth period

```{r}
K_model_perclan_growthperiod <- fitme(median ~ year:name + name + AR1(1|n),
                                      data = plot_data %>% filter(year > growth_period_until), family = "gaussian")

null_mod <- fitme(median ~ name + AR1(1|n),
                  data = plot_data %>% filter(year > growth_period_until), family = "gaussian")
summary(K_model_perclan_growthperiod)
```
```{r}
## Asympototic for consistency
LRT(K_model_perclan_growthperiod, null_mod)
# LRT(K_model_perclan_growthperiod, null_mod, boot.repl = 999, nb_cores = 10, seed = 123)
```

```{r}
summary(K_model_perclan_growthperiod)
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameA", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameE", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameF", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameL", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameM", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameN", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameS", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

```{r}
spaMM::confint.HLfit(K_model_perclan_growthperiod, parm = "year:nameT", boot_args = list(nsim = 999, nb.cores = 10, seed = 123))
```

## Sex ratio

Descriptive stats

```{r}
real_pop_separate %>% 
  mutate(sexratio = ad_male/(ad_male + ad_fem)) %>% 
  filter(lubridate::year(date) <= end_year) |> 
  summarise(median = median(sexratio),
            min = min(sexratio),
            max = max(sexratio))
```

### Sex ratio mod (binomial)


```{r}
ratio_data <- real_pop_separate %>% 
  filter(lubridate::year(date) <= end_year) |> 
  filter(lubridate::month(date) %in% c(1, 7)) %>% 
  mutate(n = 1:n())
sexratio_mod <- fitme(cbind(ad_male, ad_fem) ~ n, data = ratio_data, family = "binomial")
```

```{r}
sexratio_residuals <- DHARMa::simulateResiduals(sexratio_mod, n = 1000, seed = 123)
plot(sexratio_residuals)
```

```{r}
testTemporalAutocorrelation(sexratio_residuals, time = 1:nrow(ratio_data))
```

### Sex ratio mod AR1 (binomial)

Do this at every 6 months to be comparable

```{r}
sexratio_mod2 <- fitme(cbind(ad_male, ad_fem) ~ n + AR1(1|n), data = ratio_data, family = "binomial")
summary(sexratio_mod2)
```

```{r}
sexratio2_residuals <- DHARMa::simulateResiduals(sexratio_mod2, n = 1000, seed = 123)
## Residual quantiles not great, but residuals ok w/ uniformity test
## Not sure there's much to do here when using model with so few points!
plot(sexratio2_residuals)
```


```{r}
acf(residuals(sexratio_mod2))
```

```{r}
global_mod <- fitme(cbind(ad_male, ad_fem) ~ n + AR1(1|n), data = ratio_data, family = "binomial")
null_mod   <- fitme(cbind(ad_male, ad_fem) ~ 1 + AR1(1|n), data = ratio_data, family = "binomial")

summary(global_mod)
```
```{r}
## Fails with bootstrap...is it because we're using cbind?!
LRT(global_mod, null_mod)
```

```{r}
confint(global_mod, parm = "n")
```

## Age ratio

Descriptive stats

```{r}
real_pop_separate %>% 
  mutate(sexratio = young/(young + ad_male + ad_fem)) %>% 
  filter(lubridate::year(date) <= end_year) |> 
  summarise(median = median(sexratio),
            min = min(sexratio),
            max = max(sexratio))
```

### Age ratio mod (binomial)

Do this at every 6 months to be comparable

```{r}
ageratio_mod <- fitme(cbind(young, ad_male + ad_fem) ~ n, data = ratio_data, family = "binomial")
```

```{r}
ageratio_residuals <- DHARMa::simulateResiduals(ageratio_mod, n = 1000, seed = 123)
plot(ageratio_residuals)
```


```{r}
testTemporalAutocorrelation(ageratio_residuals, time = 1:nrow(ratio_data))
```

### Age ratio mod AR1 (binomial)

Do this at every 6 months to be comparable

```{r}
ageratio_mod2 <- fitme(cbind(young, ad_male + ad_fem) ~ n + AR1(1|n), data = ratio_data, family = "binomial")
summary(ageratio_mod2)
```

```{r}
ageratio2_residuals <- DHARMa::simulateResiduals(ageratio_mod2, n = 1000, seed = 123)
## AGE RATIO MODEL IS MUCH BETTER FIT
plot(ageratio2_residuals)
```

```{r}
acf(residuals(ageratio_mod2))
```

```{r}
global_mod <- fitme(cbind(young, ad_male + ad_fem) ~ n + AR1(1|n), data = ratio_data, family = "binomial")
null_mod   <- fitme(cbind(young, ad_male + ad_fem) ~ 1 + AR1(1|n), data = ratio_data, family = "binomial")

summary(global_mod)
```
```{r}
## Fails with bootstrap, because we're using cbind?
LRT(global_mod, null_mod)
```

```{r}
confint(global_mod, parm = "n")
```


