---
title: "POM_approach"
output: html_document
date: "2023-03-13"
---

# Create simulated and real dataset

## Simulated outcome

```{r}
library(SHIM)
library(dplyr)
library(hyenaR)
library(ggplot2)
library(spaMM)

## GENERATED IN STEP0_prepare_data/model_fit.Rmd
model_data <- readRDS(here::here("./analysis/data/model_data.RDS"))

## GENERATED IN STEP1_estimate_K/estimateK.R
modlist <- readRDS(here::here("./analysis/data/model_list.RDS"))
```

```{r}
## Run simulation for 313 timesteps (i.e. from 1996 - 2021)
POM_sim <- simulation_fitrun(number_steps = 320, models = modlist,
                             return = TRUE, name = "POM",
                             save_dir = "~/data/simulation_results/analysis/STEP3_supplementary_analysis/SX_pattern_oriented_modelling/data",
                             predictors = list(start_clan = \(ID) ID$clan_name,
                                               post_dispersal_status = \(ID) if (ID$birth_date == ID$first_date) "philo" else "disp",
                                               ## If we want a more refined estimate of rank
                                               rank_category2 = \(ID){
                                                 natals <- ID$clan_ID$inhabitants_tbl$ID[ID$clan_ID$inhabitants_tbl$natal]
                                                 ## Will extract for all individuals (even disperser males) so can be NA
                                                 if (!ID$ID %in% natals) return(NA_character_)
                                                 std_rank <- seq(1, -1, length.out = length(natals))[which(natals == ID$ID)]
                                                 if (std_rank >= 1/3) "top" else if (std_rank <= -1/3) "bottom" else "middle"
                                               }
                             ),
                             step_size = 1,
                             seed = 123)
```

# Extract demographic info to compare

We do this once for simulated data and once for real data so that we don't have to rebuilt the lifehistory table every time.

## Simulated data

To use the rank functions we need to save a database object (which can be build from .csv files)

```{r}
all_tbls <- ls(POM_sim)[grepl(ls(POM_sim), pattern = "Sighting|Hyenas|Clans|Rankchanges|Snapshots|Selections")]

for (file in all_tbls){
  
  focal_tbl <- POM_sim[[file]]
  
  save_name <- tolower(stringr::str_remove(file, pattern = "_tbl"))
  
  if (save_name == "sightings") {
    focal_tbl <- focal_tbl %>% 
      rename(date = date_time) %>% 
      mutate(time = "00:00")
  }
  
  if ("sex" %in% colnames(focal_tbl)) {
    focal_tbl <- focal_tbl %>% 
      mutate(across(sex, .fns = \(x){
        case_when(x == "female" ~ 2,
                  x == "male" ~ 1,
                  TRUE ~ NA_real_)
      })) 
  }
  
  write.csv(focal_tbl,
            file = paste0("~/data/simulation_results/analysis/STEP3_supplementary_analysis/SX_pattern_oriented_modelling/data/", save_name, ".csv"), row.names = FALSE)
  
}

build_package_database.full(db.name = "POM_sim",
                            input.folder = "~/data/simulation_results/analysis/STEP3_supplementary_analysis/SX_pattern_oriented_modelling/data")
```

```{r}
# load_package_database.sim(POM_sim)
load_package_database.full("~/data/simulation_results/analysis/STEP3_supplementary_analysis/SX_pattern_oriented_modelling/data/POM_sim.sqlite")

```

```{r}
### LIFESPAN
lifespan_data_sim <- create_id_starting.table(sex = c("female", "male"),
                                              from = find_pop_date.observation.first(),
                                              to = find_pop_date.observation.last(),
                                              lifestage = "cub", lifestage.overlap = "start") %>%
  mutate(lifespan = fetch_id_duration.lifespan(ID),
         sex = fetch_id_sex(ID),
         source = "sim",
         rank = fetch_id_rank.birth.std(ID)) %>%
  # Remove NAs for lifespan = IDs still not dead = right-censored IDs
  filter(!is.na(lifespan))

### FEMALE LRS
LRS_data_sim <- create_id_starting.table(sex = "female", lifestage = "adult",
                                         ## We observed their full adult life
                                         lifestage.overlap = "within",
                                         from = find_pop_date.observation.first(),
                                         to = find_pop_date.observation.last()) %>%
  mutate(RS = fetch_id_number.offspring(ID = .data$ID, filiation = c("mother_genetic", "mother_social_genetic"), age.mature = 6, unit = "month"),
         sex = fetch_id_sex(ID),
         source = "sim",
         rank = fetch_id_rank.native.std(ID, at = fetch_id_date.at.age(ID, age = 2, unit = "year")))

### FEMALE AGE AT FIRST REPRO
firstrepro_data_sim <- create_id_offspring.table() %>% 
  ## Find non-left censored individuals
  filter(fetch_id_date.birth(parentID) >= find_pop_date.observation.first()) %>% 
  filter(filiation %in% c("mother_social_genetic", "mother_genetic")) %>% 
  mutate(cublifespan = fetch_id_duration.lifespan(offspringID, unit = "month"),
         cubage_lastdate = fetch_id_age(offspringID, at = find_pop_date.observation.last(), unit = "month")) %>% 
  filter((!is.na(cublifespan) & cublifespan >= 6)|(is.na(cublifespan) & cubage_lastdate >= 6)) %>% 
  group_by(parentID) %>% 
  summarise(first_repro = min(birthdate), .groups = "drop") %>% 
  mutate(age_first_repro = fetch_id_age(parentID, at = first_repro),
         source = "sim")

### FEMALE IBI
IBI_data_sim <- create_id_offspring.table() %>% 
  ## Find non-left censored litters
  filter(birthdate >= find_pop_date.observation.first()) %>% 
  filter(filiation %in% c("mother_social_genetic", "mother_genetic")) %>% 
  mutate(cublifespan = fetch_id_duration.lifespan(offspringID, unit = "month"),
         cubage_lastdate = fetch_id_age(offspringID, at = find_pop_date.observation.last(), unit = "month")) %>% 
  filter((!is.na(cublifespan) & cublifespan >= 6)|(is.na(cublifespan) & cubage_lastdate >= 6)) |> 
  group_by(parentID, birthdate) |> 
  summarise() %>% 
  mutate(IBI = as.numeric(lead(birthdate) - birthdate),
         ## Assume an average month of 31 days
         IBI_mo = IBI/31,
         source = "sim") |> 
  ungroup() |> 
  filter(!is.na(IBI))
```

## Real data

```{r}
load_package_database.full(db.path)
```

```{r}
### LIFESPAN
lifespan_data_real <- create_id_starting.table(sex = c("female", "male"),
                                               from = find_pop_date.observation.first(),
                                               to = find_pop_date.observation.last(),
                                               lifestage = "cub", lifestage.overlap = "start") %>%
  mutate(lifespan = fetch_id_duration.lifespan(ID),
         sex = fetch_id_sex(ID),
         source = "real") %>%
  # Remove NAs for lifespan = IDs still not dead = right-censored IDs
  filter(!is.na(lifespan) & lifespan > 0.5)

### FEMALE LRS
LRS_data_real <- create_id_starting.table(sex = "female", lifestage = "adult",
                                          ## We observed their full adult life
                                          lifestage.overlap = "within",
                                          from = find_pop_date.observation.first(),
                                          to = find_pop_date.observation.last()) %>%
  mutate(RS = fetch_id_number.offspring(ID = .data$ID, filiation = c("mother_genetic", "mother_social_genetic"), age.mature = 6, unit = "month"),
         sex = fetch_id_sex(ID),
         source = "real",
         rank = fetch_id_rank.native.std(ID, at = fetch_id_date.at.age(ID, age = 2, unit = "year")))

### FEMALE AGE AT FIRST REPRO
firstrepro_data_real <- create_id_offspring.table() %>% 
  ## Find non-left censored individuals
  filter(fetch_id_date.birth(parentID) >= find_pop_date.observation.first()) %>% 
  filter(filiation %in% c("mother_social_genetic", "mother_genetic")) %>% 
  mutate(cublifespan = fetch_id_duration.lifespan(offspringID, unit = "month"),
         cubage_lastdate = fetch_id_age(offspringID, at = find_pop_date.observation.last(), unit = "month")) %>% 
  filter((!is.na(cublifespan) & cublifespan >= 6)|(is.na(cublifespan) & cubage_lastdate >= 6)) %>% 
  group_by(parentID) %>% 
  summarise(first_repro = min(birthdate), .groups = "drop") %>% 
  mutate(age_first_repro = fetch_id_age(parentID, at = first_repro),
         source = "real") %>% 
  ## A-260 died before first birth...is this a known bug in data? Yes, GH issue #615
  filter(!is.na(age_first_repro))

### FEMALE IBI
IBI_data_real <- create_id_offspring.table() %>% 
  ## Now we only need to consider non left-censored LITTERS
  filter(birthdate >= find_pop_date.observation.first()) %>% 
  filter(filiation %in% c("mother_social_genetic", "mother_genetic")) %>% 
  mutate(cublifespan = fetch_id_duration.lifespan(offspringID, unit = "month"),
         cubage_lastdate = fetch_id_age(offspringID, at = find_pop_date.observation.last(), unit = "month")) %>% 
  filter((!is.na(cublifespan) & cublifespan >= 6)|(is.na(cublifespan) & cubage_lastdate >= 6)) |> 
  group_by(parentID, birthdate) |> 
  summarise() %>% 
  mutate(IBI = as.numeric(lead(birthdate) - birthdate),
         IBI_mo = IBI/31,
         source = "real") |> 
  ungroup() |> 
  filter(!is.na(IBI))
```

# Plot data

### Lifespan

```{r}
lifespan_data_sim %>% 
  group_by(sex) %>% 
  summarise(mean = mean(lifespan),
            median = median(lifespan),
            max = max(lifespan),
            se = sd(lifespan)/sqrt(n()))
```
```{r}
lifespan_data_real %>% 
  group_by(sex) %>% 
  summarise(mean = mean(lifespan),
            median = median(lifespan),
            max = max(lifespan),
            se = sd(lifespan)/sqrt(n()))
```

```{r}
ggplot() +
  geom_histogram(data = lifespan_data_sim, aes(x = lifespan, y = ..count../sum(..count..)), fill = "red", colour = "black", alpha = 0.75,
                 linewidth = 1, binwidth = 0.5) +
  geom_histogram(data = lifespan_data_real, aes(x = lifespan, y = ..count../sum(..count..)), fill = "white", colour = "black", alpha = 0.5,
                 linewidth = 1, binwidth = 0.5) +
  facet_wrap(facets = ~sex) +
  labs(x = "Lifespan (years)",
       y = "Proportion of individuals") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black"))

ggsave(filename = "~/data/simulation_results/analysis/STEP3_supplementary_analysis/SX_pattern_oriented_modelling/plots/lifespan.png",
       width = 9, heigh = 5)
```

### LRS

```{r}
LRS_data_sim %>% 
  summarise(mean = mean(RS),
            median = median(RS),
            max = max(RS),
            se = sd(RS)/sqrt(n()))
```
```{r}
LRS_data_real %>% 
  summarise(mean = mean(RS),
            median = median(RS),
            max = max(RS),
            se = sd(RS)/sqrt(n()))
```

```{r}
ggplot() +
  geom_histogram(data = LRS_data_sim, aes(x = RS, y = ..count../sum(..count..)), fill = "red", colour = "black", alpha = 0.75,
                 linewidth = 1, binwidth = 1) +
  geom_histogram(data = LRS_data_real, aes(x = RS, y = ..count../sum(..count..)), fill = "white", colour = "black", alpha = 0.5,
                 linewidth = 1, binwidth = 1) +
  labs(x = "Lifetime reproductive success (number offspring >6mo)",
       y = "Proportion of individuals") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black"))

ggsave(filename = "~/data/simulation_results/analysis/STEP3_supplementary_analysis/SX_pattern_oriented_modelling/plots/LRS.png",
       width = 9, heigh = 5)
```

### First repro

```{r}
firstrepro_data_sim %>% 
  summarise(mean = mean(age_first_repro),
            median = median(age_first_repro),
            max = max(age_first_repro),
            se = sd(age_first_repro)/sqrt(n()))
```
```{r}
firstrepro_data_real %>% 
  summarise(mean = mean(age_first_repro),
            median = median(age_first_repro),
            max = max(age_first_repro),
            se = sd(age_first_repro)/sqrt(n()))
```

```{r}
ggplot() +
  geom_histogram(data = firstrepro_data_sim, aes(x = age_first_repro, y = ..count../sum(..count..)), fill = "red", colour = "black", alpha = 0.75,
                 linewidth = 1, binwidth = 0.5) +
  geom_histogram(data = firstrepro_data_real, aes(x = age_first_repro, y = ..count../sum(..count..)), fill = "white", colour = "black", alpha = 0.5,
                 linewidth = 1, binwidth = 0.5) +
  scale_x_continuous(limits = c(0, NA),
                     breaks = seq(0, 10, 1)) +
  labs(x = "Age at first reproduction (years)",
       y = "Proportion of individuals") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black"))

ggsave(filename = "~/data/simulation_results/analysis/STEP3_supplementary_analysis/SX_pattern_oriented_modelling/plots/age_at_first_repro.png",
       width = 9, heigh = 5)
```

### IBI

```{r}
IBI_data_sim %>% 
  mutate(IBI = IBI_mo) |> 
  summarise(mean = mean(IBI),
            median = median(IBI),
            max = max(IBI),
            se = sd(IBI)/sqrt(n()))
```
```{r}
IBI_data_real %>% 
  mutate(IBI = IBI_mo) |> 
  summarise(mean = mean(IBI),
            median = median(IBI),
            max = max(IBI),
            se = sd(IBI)/sqrt(n()))
```

```{r}
ggplot() +
  geom_histogram(data = IBI_data_sim, aes(x = IBI_mo, y = ..count../sum(..count..)), fill = "red", colour = "black", alpha = 0.75,
                 linewidth = 1, binwidth = 1) +
  geom_histogram(data = IBI_data_real, aes(x = IBI_mo, y = ..count../sum(..count..)), fill = "white", colour = "black", alpha = 0.5,
                 linewidth = 1, binwidth = 1) +
  labs(x = "Inter-birth interval (months)",
       y = "Proportion of individuals") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black"))

ggsave(filename = "~/data/simulation_results/analysis/STEP3_supplementary_analysis/SX_pattern_oriented_modelling/plots/IBI.png",
       width = 9, heigh = 5)
```

## Effects of rank

```{r}
LRS_rank_sim <- LRS_data_sim  %>% 
  filter(!is.na(rank)) %>% 
  mutate(rank_cat = case_when(rank >= 1/3 ~ "1. top",
                              rank < 1/3 & rank >= -1/3 ~ "2. middle",
                              TRUE ~ "3. bottom")) %>% 
  group_by(rank_cat) %>% 
  summarise(meanLRS = mean(RS),
            SE = sqrt(mean(RS)/n()),
            source = "sim")

LRS_rank_real <- LRS_data_real  %>% 
  filter(!is.na(rank)) %>% 
  mutate(rank_cat = case_when(rank >= 1/3 ~ "1. top",
                              rank < 1/3 & rank >= -1/3 ~ "2. middle",
                              TRUE ~ "3. bottom")) %>% 
  group_by(rank_cat) %>% 
  summarise(meanLRS = mean(RS),
            SE = sqrt(mean(RS)/n()),
            source = "real")

(plot_data <- dplyr::bind_rows(LRS_rank_sim, LRS_rank_real))
```

```{r}
ggplot() +
  geom_col(data = plot_data,
           aes(x = rank_cat, y = meanLRS, fill = source,
               alpha = source), position = position_dodge(width = 0.6),
           colour = "black") +
  geom_errorbar(data = plot_data,
                aes(x = rank_cat,
                    ymin = meanLRS - SE,
                    ymax = meanLRS + SE, group = source), position = position_dodge(width = 0.6),
                colour = "black", width = 0) +
  scale_fill_manual(values = c("white", "red")) +
  scale_alpha_manual(values = c(0.5, 0.75)) +
  labs(x = "Rank category",
       y = "Lifetime reproductive success (offspring >6mo)") +
  theme_classic() +
  theme(axis.text = element_text(colour = "black"),
        legend.position = "none")

ggsave(filename = "~/data/simulation_results/analysis/STEP3_supplementary_analysis/SX_pattern_oriented_modelling/plots/rank_effect.png",
       width = 9, heigh = 5)
```

## Population size

```{r}
sim_pop_ad <- POM_sim$Rawdata_tbl %>% 
  filter(age >= 24) %>% 
  group_by(current_date) %>% 
  summarise(n = n())

filter(sim_pop_ad, n == max(n))
```


```{r}
sim_pop_cub <- POM_sim$Rawdata_tbl %>% 
  filter(age < 24) %>% 
  group_by(current_date) %>% 
  summarise(n = n())

filter(sim_pop_cub, n == max(n))
```

```{r}
### GENERATED IN STEP0_prepare_data/demographic_data.R
real_pop <- readRDS(here::here("./analysis/data/Nplot_data_separate_1month.RDS"))
real_pop <- real_pop %>% 
  mutate(ad_total = ad_male + ad_fem)
```

```{r}
ggplot() +
  geom_line(data = real_pop, aes(x = date, y = ad_total), colour = "blue") +
  geom_line(data = sim_pop_ad, aes(x = current_date, y = n), colour = "red")
```

```{r}
ggplot() +
  geom_line(data = real_pop, aes(x = date, y = young), colour = "blue") +
  geom_line(data = sim_pop_cub, aes(x = current_date, y = n), colour = "red")
```
